### 2024-08-24 README.qmd
Added Quarto markdown file for generating README.

---
title: "quicR"
format: gfm
editor: source
---

# Description
quicR is a package made for the analysis of real-time quaking-induced conversion (RT-QuIC) assays.

Much of the functionality is designed to be integrated with the Excel output files generated by the BMG analysis software, MARS.
For best results, in the MARS software select:

```{mermaid}
flowchart TB
excel(Excel Export)

subgraph A[Select the following export options]
  direction LR
  micro(Microplate View)
  table(Table View)
  trans(Transpose Table)
  test(Add test run \n information)
end

export(Export report to Excel)

excel --> A
micro --> table --> trans --> test
A --> export
```

Having both the microplate view and the table view helps with integrating plate layouts and the real-time data.

For many of the functions, it is important to have a table labelled "Sample IDs" on the microplate view sheet of the Excel file.

### 2024-08-24 README.qmd
Update README

@@
 
-# Description
+## Description
 quicR is a package made for the analysis of real-time quaking-induced conversion (RT-QuIC) assays.
@@
 For many of the functions, it is important to have a table labelled "Sample IDs" on the microplate view sheet of the Excel file.
+
+## Examples
+
+### Plate IDs for BMG Import
+
+Use BMG_format.R script to format a .CSV file with a Sample IDs in a plate view into a format importable into the BMG control software.
+
+For example .CSV file, see:
+```
+tests -> testthat -> BMG_formatting -> plate_layout.csv
+```
+The file, "formatted.txt" in the same folder, is how the export should look to be imported into the BMG software.
+
+### Plate View
+
+Use plate_view_export.R to export a plate view of the real-time data from an Excel file made in MARS.
+
+For example .CSV files, see:
+```
+tests -> testthat -> input_files
+```
+
+### Calculations
+
+The program, calculate_metrics.R, will calculate relevant metrics such as maxpoint ratio, max slope, time-to-threshold, and rate of amyloid formation.
+
+An Excel file will also be created with the full data and summarized data. A plot of the summarized data will also be created.
+
+For example .CSV files, see:
+```
+tests -> testthat -> input_files
+```
+
+## Author
+
+Gage Rowden

### 2024-08-25 README.qmd
\n lol

@@
   direction LR
+
   micro(Microplate View)

### 2024-08-25 calculate_metrics.R
Designated which functions are from quicR and prettified the code a bit.

@@ -1,11 +1,7 @@
 library(slider)
 library(ggpubr)
 library(agricolae)
-
-
-
-# Users will need to adjust for their own file directory.
-source("~/RTQ_analysis/functions/functions.R")
+library(quicR)
 
 
 
@@ -36,7 +32,7 @@ while (file == "") {
 
 
 # Get the real-time data from the BMG export file.
-df <- get_real(file, ordered=FALSE)
+df <- quicR::get_real(file, ordered=FALSE)
 
 # Ask the user which real-time data set they want to use.
 df_id <- as.integer(
@@ -49,7 +45,7 @@ df_id <- as.integer(
     )
   )
 
-# Ask the user for the run-time in hours.
+# Ask the user for the threshold.
 threshold <- as.integer(
   readline(
     "Please enter the desired threshold for RAF calculation: "
@@ -66,7 +62,8 @@ df <- df[[df_id]]
 
 
 # Export the tables in the first sheet of the file.
-dic <- organize_tables(file)
+dic <- quicR::organize_tables(file)
+
 column_names <- c("Time")
 for (i in t(dic[["Sample IDs"]])) {
   for (j in i) {
@@ -75,6 +72,7 @@ for (i in t(dic[["Sample IDs"]])) {
     }
   }
 }
+
 # Apply the column names.
 colnames(df) <- column_names
 
@@ -88,7 +86,7 @@ dilution_bool <- "Dilutions" %in% names(dic)
 
 
 # Calculate the normalized real-time data.
-df_norm <- normalize_RFU(df)
+df_norm <- quicR::normalize_RFU(df)
 
 # Add dilution factors if applicable.
 if (dilution_bool) {
@@ -113,22 +111,25 @@ hours <- as.numeric(colnames(df_norm)[ncol(df_norm)])
 
 # Initialized the dataframe with the calculated metrics.
 df_analyzed <- data.frame(`Sample_ID` = df_norm$`Sample ID`) %>%
+
   mutate(
     # Add dilutions if applicable.
     Dilutions = if (dilution_bool) -log10(as.numeric(dilutions)),
     # Maxpoint Ratio
-    MPR = calculate_MPR(df_norm, start_col=3, data_is_norm=TRUE),
+    MPR = quicR::calculate_MPR(df_norm, start_col=3, data_is_norm=TRUE),
     # Max Slope
-    MS  = calculate_MS(df_norm, start_col=3),
[…]

### 2024-08-25 plate_view_export.R
Designated which functions are coming from quicR and prettified the code a bit.

@@ -1,8 +1,6 @@
 library(readxl)
-library(tidyverse)
-library(ggpubr)
+library(dplyr)
 library(ggplot2)
-library(gridExtra)
 library(quicR)
 
 
@@ -30,8 +28,8 @@ while (plate == "") {
 
 # Define the layout using the first sheet in the excel file.
 # The sheet should be formatted so that each ID in the "layout" table is unique.
-# "organize_tables" is sourced from plate_view_function.R.
-df_dic <- organize_tables(file, plate = plate)
+df_dic <- quicR::organize_tables(file, plate = plate)
+
 IDs <- t(df_dic[["Sample IDs"]])
 ID_list <- list()
 for (i in IDs) {
@@ -60,7 +58,7 @@ if (dilution_bool) {
 # Read in the real-time data.
 # "get_real" will return a list of dataframes depending on how many real-time
 # measurements the user exported from MARS.
-df_list <- get_real(file, ordered=FALSE)
+df_list <- quicR::get_real(file, ordered=FALSE)
 
 df_id <- as.integer(
   readline(
@@ -72,8 +70,7 @@ df_id <- as.integer(
   )
 )
 
-df <- data.frame(df_list[[df_id]])
-# df_meta <- get_meta(file)
+df <- as.data.frame(df_list[[df_id]])
 
 # Specify the time column.
 time_col <- df[, 1]
@@ -85,16 +82,17 @@ df <- df[, -1]
 rownames(df) <- time_col
 
 # Get the wells used in the run.
-wells <- get_wells(file)
+wells <- quicR::get_wells(file)
 
 # Take the metadata and apply it into a dataframe for the plate_view function.
-sample_locations <- na.omit(do.call(rbind, Map(data.frame, A=wells, B=ID_list)))
+sample_locations <- do.call(rbind, Map(data.frame, A = wells, B = ID_list)) %>%
+  na.omit()
 
 # Add the dilutions if applicable.
 if (dilution_bool) {
   sample_locations <- sample_locations %>%
     mutate(Dilutions = -log10(as.numeric(dilutions))) %>%
-    unite(B, B:Dilutions, sep="\n")
+    unite(B, B:Dilutions, sep = "\n")
 }
 
 # Run plate_view function which produces a plate view figure.

### 2025-01-02 manuscript.qmd
Added manuscript files

---
title: "quicR: An R Package for the Analysis of Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
author:
    - name: 
        given: Gage
        family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
          name: University of Minnesota
          city: Saint Paul
          state: MN
      corresponding: true
abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards have yet to be established. 'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis.
keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
bibliography:
    references.bib
bibliographystyle: 
    apa
---

# Introduction

# Methods
This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stats, stringr, tidyr. Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx and readxl, were fundamental to performing downstream handling. The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization. The janitor package has useful functions for performing quick data cleaning

## Development
The quicR package was developed to address the need for efficient data conversion and analysis of RT-QuIC data. The functions were designed with usability and reproducibility in mind, ensuring compatibility between multiple labs. Currently, the package accepts data exported from the MARS software as an Excel workbook.

The two types of functionality in this package revolve around data curation and metric calculations.

# Implementation

# Usage

# Validation & Performance

# Discussion

# Conclusion

# Acknowledgments

# References
::: {#refs}
:::

### 2025-01-02 .example_scripts/plate_view_export.R
Added a new function, get_sample_locations.

@@ -1,4 +1,4 @@
-require(readxl)
+# require(readxl)
 require(tidyverse)
 require(quicR)
 
@@ -38,18 +38,8 @@ while (plate == "") {
 # The sheet should be formatted so that each ID in the "layout" table is unique.
 df_dic <- quicR::organize_tables(file, plate = plate)
 
-IDs <- quicR::convert_tables(df_dic)[["Sample IDs"]] |>
-  na.omit()
-
 # Determine if there is a dilutions table.
 dilution_bool <- "Dilutions" %in% names(df_dic)
-
-# Add dilution factors if applicable.
-if (dilution_bool) {
-  dilutions <- quicR::convert_tables(df_dic)$Dilutions |>
-    as.numeric() |>
-    log10() * -1
-}
 
 # Read in the real-time data.
 # get_real will return a list of dataframes depending on how many real-time
@@ -70,31 +60,11 @@ df_id <- ifelse(
   1
 )
 
-df <- as.data.frame(df_list[[df_id]])
+df <- df_list[[df_id]] %>%
+  as.data.frame %>%
+  column_to_rownames("Time")
 
-# Set the time column as the df index.
-rownames(df) <- df[, 1]
-
-# Remove the time column and ID row.
-df <- df[, -1]
-
-# Get the wells used in the run.
-wells <- quicR::get_wells(file)
-
-# Take the metadata and apply it into a dataframe for the plate_view function.
-sample_locations <- cbind(wells, IDs) |>
-  na.omit()
-
-# Add the dilutions if applicable.
-if (dilution_bool) {
-  sample_locations <- sample_locations |>
-    dplyr::mutate(Dilutions = dilutions |> na.omit()) |>
-    dplyr::mutate(IDs = as.character(IDs)) |>
-    tidyr::unite(IDs, IDs:Dilutions, sep = "\n")
-}
-
-sample_locations <- sample_locations |>
-  mutate(IDs = ifelse(stringr::str_length(IDs) > 12, gsub(" ", "\n", IDs), IDs))
+sample_locations <- get_sample_locations(file, "Sample IDs", dilution_bool)
 
 
 

### 2025-01-02 R/get_sample_locations.R

@@ -1,0 +1,61 @@
+#' Get the well locations of the samples used in the RT-QuIC run.
+#'
+#' Returns a dataframe with the sample IDs and well IDs used in the plate.
+#'
+#' @param file Excel file exported from MARS
+#' @param tab_name Table name containing the sample IDs.
+#' @param dilution_bool Logical; is there a table containing dilution factors? If so, will add a newline and the log of the dilution factor to the ID column.
+#' @param plate Integer; either 96 or 384 to denote microplate type.
+#'
+#' @return A vector containing well IDs.
+#'
+#' @importFrom dplyr mutate
+#' @importFrom dplyr %>%
+#' @importFrom stats na.omit
+#' @importFrom stringr str_length
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_sample_locations(file, "Sample IDs", TRUE, 96)
+#'
+#' @export
+get_sample_locations <- function(file, tab_name, dilution_bool = FALSE, plate = 96) {
+
+  return(
+    data.frame(
+      wells = get_wells(file) %>%
+        suppressMessages(),
+      IDs = (
+        organize_tables(file, plate = plate) %>%
+          convert_tables() %>%
+          suppressMessages()
+      )[[tab_name]] %>%
+        na.omit()
+    ) %>%
+      mutate(
+        "IDs" = ifelse(
+          str_length(.[["IDs"]]) > 12,
+          gsub(" ", "\n", .[["IDs"]]),
+          .[["IDs"]]
+        ),
+        "IDs" = if (dilution_bool) {
+          paste(
+            as.character(.[["IDs"]]),
+            "\n",
+            (organize_tables(file) %>%
+               convert_tables() %>%
+               suppressMessages())[["Dilutions"]] %>%
+              as.numeric() %>%
+              log10() * -1 %>%
+              na.omit()
+          )
+        } else {
+          .[["IDs"]]
+        }
+    )
+  )
+}

### 2025-01-02 R/get_wells.R
Fixed typo in get_wells

@@ -35,7 +35,7 @@ get_wells <- function(file) {
       break
     }
   }
-  wells <- wells[-(1:2)] |>
+  wells[-(1:2)] |>
     as.data.frame() |>
     t() |>
     as.data.frame()

### 2025-01-03 manuscript.qmd
Update manuscript files

@@
 ---
+```{r, echo=FALSE, message=FALSE}
+library(quicR)
+library(dplyr)
+library(kableExtra)
+library(readxl)
+library(readr)
+
+file <- "inst/extdata/input_files/test3.xlsx"
+sample_file <- "inst/extdata/BMG_formatting/plate_layout.csv"
+```
 
 # Introduction
+Real-time quaking induced conversion is a diagnostic assay that converts recombinant protein substrate into a misfolded aggregate in the presence of a misfolded seed [@Atarashi2011].
+
+While standard metrics for determining a diagnosis have not been universally established, there are certain metrics that many research groups have found useful.
+These include time-to-threshold (TtT)[@Orru2015], rate of amyloid formation (RAF)[@Gallups2022], maxpoint ratio (MPR)[@Rowden2023], and maximum slope (MS)[@Henderson2015].
+All together, these metrics provide insight into the general kinetics of an RT-QuIC reaction, and can be used together to draw a more robust diagnostic decision.
 
@@
 
-The two types of functionality in this package revolve around data curation and metric calculations.
+The functionality in this package revolves around data curation, metric calculations, and visualization.
 
 # Implementation
+
+## Input of Sample IDs into MARS
+
+MARS allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+This file is uniquely formatted, and not easily reproduced manually.
+The function "BMG_format" allows for input of a CSV file containing the plate layout, and exports the formatted TXT file.
+
+### Example Plate Layout
+
+```{r, echo=FALSE, message=FALSE}
+read_csv(sample_file, name_repair = "minimal") %>% kable()
+```
+
+### Formatted Plate Layout for MARS Input
+
+"BMG_format" includes the logical argument "write_file". If this argument is true, it will write a TXT file to the "save_path" as "save_name".
+
+```{r}
+BMG_format(sample_file, write_file = FALSE)[1:18]
+```
+
+## Data Cleaning and Transformation
+
+The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
+Typically, the first sheet in the workbook will include microplate views of data.
+The two tables that are most relevant on this sheet are the "Sample IDs" table and the "Dilutions" table (if included).
+For much of the downstream analysis, it is crucial the the "Sample IDs" table was exported.
+If there is no table, the user can simply add it manually.
+
+### Retrieving Metadata
+
+The metadata is defined as either sample-dependent or -independent.
+Sample-dependent metadata includes information such as sample IDs and dilution factors, whereas sample-independent metadata includes the date, time, reaction ID, etc.
+
+#### Sample-Dependent Metadata
+
+The dependent metadata can be retrieved using the "organize_tables" and "convert_tables" functions.
+The former returns a list of tables, and the ladder converts each table into a column in a single data frame.
+
+```{r, message=FALSE}
+tabs <- organize_tables(file)[-1]
+tabs
+
+tabs <- convert_tables(tabs)
+tabs %>% 
+  head(15)
+```
+
+#### Sample-Independent Metadata
+The independent metadata can be retrieved using the "get_meta" function. This data is included in the header of the excel workbook.
+
+```{r, message=FALSE}
+get_meta(file) %>% as.data.frame()
+```
+
+### Retrieving and Manipulating Raw Data
+
+The raw data is typically found on the second sheet of the Excel workbook.
+The raw real-time data can be retrieved using the "get_real" function.
+The logical argument, "ordered", indicates whether the user would prefer the columns to be ordered by well or by sample ID.
+By default, it is FALSE which will order the data by well.
+This should almost always be the case for easier integration with other downstream functions.
+Additionally, since there can be more than one instance of real-time data (depending on if the user added some calculations in MARS), "get_real" returns a list of dataframes.
+Therefore, the output should be indexed to access the data frame of interest.
+
+#### Retrieve Raw Data
+
+```{r}
+df_ <- get_real(file, ordered = FALSE)[[1]] %>% as.data.frame()
+
+df_[1:15, 1:6]
+```
+
+#### Transpose Raw Data
+
+This data is structured such that each sample is its own column as well as the time points.
+This format can be non-ideal, and should be transposed for downstream manipulation using the function, "transpose_real".
+After transposition, each time point has its own column, and there is a single column for every sample ID.
+
+```{r}
+transpose_real(df_)[1:15, 1:13]
+```
+
+#### Normalize Raw Data
+
+The function "normalize_RFU" will convert the raw data into a background normalized data set.
+The function includes two additional arguments, "bg_cycle" (the cycle which will be used as the background fluorescence value) and "transposed" (if FALSE, will make a call to the "transpose_real" function).
+
+```{r}
+df_norm <- normalize_RFU(df_, bg_cycle = 4, transposed = FALSE)
+
+df_norm[1:15, 1:12] %>%
+  mutate_at(2:ncol(.), ~round(as.numeric(.), 2))
+```
+
+The reader will notice that the fourth time column is all "1's" since this was designated the background cycle.
+
+## Calculations
+There are three analytical metrics with dedicated functions: time-to-threshold, maxpoint ratio, and maximum slope.
+The rate of amyloid formation does not have a designated function since it is simply the inverse of the time-to-threshold.
+Each function below accepts input from the "transpose_real" or the "normalize_RFU" functions.
+
+### Time-to-threshold
+Time-to-threshold is calculated using the "calculate_TtT" function.
+
+### Maxpoint Ratio
+
+### Maximum Slope
+
+```{r}
+samples <- tabs$`Sample IDs` %>% na.omit()
+
+# Define the number of hours that the rxn ran for.
+hours <- as.numeric(colnames(df_norm)[ncol(df_norm)])
+
+data.frame("Sample IDs" = samples) %>%
+  mutate(
+    # Maxpoint Ratio
+    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
+    # Max Slope
+    MS = calculate_MS(df_norm, data_is_norm = TRUE),
+    # Time to Threshold
+    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
+    # Rate of Amyloid Formation
+    RAF = ifelse(TtT == hours, 0, 1 / TtT),
+    # Crossed threshold?
+    crossed = TtT != hours
+  ) %>%
+  head(15)
+```
+
+## Visualization
 

### 2025-01-03 R/calculate_MS.R
Formatted calculate_MS

@@ -4,7 +4,7 @@
 #'
 #' @param data A dataframe containing real-time reads. It is recommended to use a dataframe made from normalize_RFU.
 #' @param window Integer designating how wide you want the sliding window to be for calculating the moving average slope.
-#' @param data_is_norm Logical, if the data has not been normalized, will make a call to normalize_RFU.
+#' @param data_is_norm Logical; if FALSE, will make a call to normalize_RFU.
 #'
 #' @return A dataframe containing the real-time slope values.
 #'
@@ -31,9 +31,7 @@
 calculate_MS <- function(data, window = 3, data_is_norm = TRUE) {
   curate <- function(x) {
     x %>%
-      {
-        if (data_is_norm) . else normalize_RFU(.)
-      } %>%
+      {if (data_is_norm) . else normalize_RFU(.)} %>%
       t() %>%
       as.data.frame() %>%
       mutate_all(~ as.numeric(as.character(.))) %>%

### 2025-01-03 R/get_sample_locations.R
Added default option for tab_name arg

@@ -23,7 +23,7 @@
 #' get_sample_locations(file, "Sample IDs", TRUE, 96)
 #'
 #' @export
-get_sample_locations <- function(file, tab_name, dilution_bool = FALSE, plate = 96) {
+get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = FALSE, plate = 96) {
 
   return(
     data.frame(

### 2025-01-03 man/manuscript/manuscript.qmd
Moved the manuscript files to the man directory.

--- 2025-01-03 manuscript.qmd
@@
 ---
-title: "quicR: An R Package for the Analysis of Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
+title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
 author:
@@
         state: MN
+      roles:
+        Conceptualization
+        Methodology
+        Software
+        Validation
+        Formal analysis
+        Investigation
+        Resources
+        Data curation
+        Writing--original draft preparation
+        Writing--review and editing
+        Visualization
+        Supervision
+        Prject administration
       corresponding: true
@@
 keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
-bibliography:
-    references.bib
-bibliographystyle: 
-    apa
+format: pdf
+mainfont: Calibri
+bibliography: references.bib
+bibliographystyle: apa
 ---
@@
 
-file <- "inst/extdata/input_files/test3.xlsx"
-sample_file <- "inst/extdata/BMG_formatting/plate_layout.csv"
+file <- "../../inst/extdata/input_files/test3.xlsx"
+sample_file <- "../../inst/extdata/BMG_formatting/plate_layout.csv"
 ```
@@
 
-## Development
+# Development
 The quicR package was developed to address the need for efficient data conversion and analysis of RT-QuIC data.
@@
 
-```{r, echo=FALSE, message=FALSE}
-read_csv(sample_file, name_repair = "minimal") %>% kable()
-```
+\begin{table}[ht]
+\centering
+\begin{tabular}{c|cccccccccccc}
+   & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
+  \hline
+  A & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  B & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  C & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  D & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  E & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
+  F & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
+  G & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
+  H & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+\newpage
 
@@
 
-"BMG_format" includes the logical argument "write_file". If this argument is true, it will write a TXT file to the "save_path" as "save_name".
+The function, "BMG_format", includes the logical argument "write_file".
+If true, it will create a TXT file.
+The path can be given to the "save_path" argument, and the file name can be supplied to the "save_name" argument.
 
-```{r}
-BMG_format(sample_file, write_file = FALSE)[1:18]
+```{r, message=FALSE}
+BMG_format(sample_file, write_file = FALSE)[1:18] %>% 
+  as.data.frame()
 ```
@@
 tabs <- convert_tables(tabs)
-tabs %>% 
-  head(15)
+tabs %>% head(15) %>% kable(row.names = FALSE)
 ```
@@
 
-df_[1:15, 1:6]
+df_[1:15, 1:6] %>% kable(row.names = FALSE)
 ```
@@
 ```{r}
-transpose_real(df_)[1:15, 1:13]
+transpose_real(df_)[1:15, 1:13] %>% kable(row.names = FALSE)
 ```
@@
 df_norm[1:15, 1:12] %>%
-  mutate_at(2:ncol(.), ~round(as.numeric(.), 2))
+  mutate_at(2:ncol(.), ~round(as.numeric(.), 2)) %>%
+  kable(row.names = FALSE)
 ```
@@
 Time-to-threshold is calculated using the "calculate_TtT" function.
+The function must be supplied a threshold; default value is 2 (i.e.
+twice the background fluorescence if the data is normalized).
+A starting column should also be given as an integer; default value is 3.
+This is essentially asking how many columns of metadata are included before the fluorescence reads begin.
+
+Time-to-threshold is calculated by iterating through each row and checking if a value is greater than the threshold.
+If the value is greater, the slope of the previous timepoint to the current timepoint is calculated, and the time intersection of the current read is returned.
 
 ### Maxpoint Ratio
+Maxpoint ratios (MPR) are calculated by the "calculate_MPR" function.
+Data must be normalized in order to derive this metric.
+In a normalized data set, the MPR is simply the maximum value achieved during the run.
 
 ### Maximum Slope
+The Maximum Slope (MS) is calculated by the "calculate_MS" function.
+The data can be either raw or normalized.
+The function iterates through each row using a rolling window which can be adjusted (default value is 3).
+Given the window size, a linear model is developed on those data points, and the slope of the model is recorded.
+The MS is simply the largest slope value recorded.
 
@@
   ) %>%
-  head(15)
+  head(15) %>%
+  kable(row.names = FALSE)
 ```

### 2025-01-03 R/calculate_MS.R
Converted the slope function to a vectorized function, and instead of using lm(), the function looks at differences within the moving window.

@@ -6,14 +6,15 @@
 #' @param window Integer designating how wide you want the sliding window to be for calculating the moving average slope.
 #' @param data_is_norm Logical; if FALSE, will make a call to normalize_RFU.
 #'
-#' @return A dataframe containing the real-time slope values.
+#' @return A dataframe containing the real-time slope values as ΔRFU/sec.
 #'
-#' @importFrom slider slide
-#' @importFrom dplyr slice
+#' @importFrom slider slide_dbl
+#' @importFrom purrr map_dbl
 #' @importFrom dplyr mutate_all
+#' @importFrom dplyr mutate
+#' @importFrom dplyr relocate
 #' @importFrom dplyr %>%
-#' @importFrom dplyr select_at
-#' @importFrom stats as.formula
+#' @importFrom dplyr select
 #'
 #' @examples
 #' # This test takes >5 sec
@@ -37,31 +38,25 @@ calculate_MS <- function(data, window = 3, data_is_norm = TRUE) {
       mutate_all(~ as.numeric(as.character(.))) %>%
       suppressWarnings() %>%
       na.omit() %>%
-      mutate(Time = rownames(.))
+      mutate(Time = as.numeric(rownames(.))) %>%
+      relocate("Time", .before = 1)
   }
 
   slope <- function(x) {
-    max_slopes <- c()
-
-    for (i in colnames(x)[-ncol(x)]) {
-      max_slopes <- max_slopes %>%
-        rbind(
-          x %>%
-            slide(
-              ~ lm(
-                as.formula(paste0("`", i, "`", " ~ Time")),
-                data = .x
-              )[[1]][[2]] / 3600,
-              .before = window,
-              .complete = TRUE
-            ) %>%
-            replace(. == "NULL", NA) %>%
-            as.numeric() %>%
-            max(na.rm = TRUE)
-        )
-    }
-
-    return(max_slopes)
+    x %>%
+      select(-"Time") %>%
+      map_dbl(~ {
+        slide_dbl(
+          .x = seq_along(.x),
+          .f = function(idx) {
+            if (length(idx) < 2) return(NA)
+            diff(range(.x[idx])) / diff(range(x[["Time"]][idx]))
+          },
+          .before = window,
+          .complete = TRUE
+        ) %>%
+          max(na.rm = TRUE)
+      })
   }
 
   return(slope(curate(data)))

### 2025-01-03 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 ---
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 library(quicR)

### 2025-01-03 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 \centering
-\begin{tabular}{c|cccccccccccc}
+\begin{tabular}{|c|cccccccccccc|}
+  \hline
    & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
@@
 The function iterates through each row using a rolling window which can be adjusted (default value is 3).
-Given the window size, a linear model is developed on those data points, and the slope of the model is recorded.
+Given the window size, the slope is calcualated based on the range of the window.
 The MS is simply the largest slope value recorded.
@@
 samples <- tabs$`Sample IDs` %>% na.omit()
+dilutions <- tabs$Dilutions %>% na.omit() %>% as.numeric()
 
@@
   mutate(
+    Dilutions = -log10(dilutions),
     # Maxpoint Ratio

### 2025-01-03 R/plate_view.R
Fixed a bug where the plate view would not render properly if the plate was not completely full.

@@ -14,6 +14,7 @@
 #' @importFrom tidyr replace_na
 #' @importFrom tidyr separate
 #' @importFrom stringr str_length
+#' @importFrom reshape2 melt
 #'
 #' @examples
 #' # This test takes >5 sec
@@ -62,7 +63,7 @@ plate_view <- function(df, meta, plate = 96) {
   # Ensures that the input is a dataframe.
   df <- data.frame(df)
 
-  colnames(df) <- paste(meta[, 1], meta[, 2], sep = ".")
+  colnames(df) <- c("Time", paste(meta[[1]], meta[[2]], sep = "."))
 
   # Create a template of all possible columns
   template_columns <- expand.grid(
@@ -82,13 +83,13 @@ plate_view <- function(df, meta, plate = 96) {
 
   # Add columns with NAs if they do not exist.
   for (col in template_columns) {
-    if (!(col %in% meta[, 1])) {
-      df[[col]] <- NA
+    if (!(col %in% meta[[1]])) {
+      df[col] <- NA
     }
   }
 
   # Add a "Time" column. This is important for the melt function.
-  df <- cbind("Time" = rownames(df), df)
+  # df <- cbind("Time" = rownames(df), df)
 
   # Combine the template_columns and sample_locations.
   template_columns <- as.data.frame(template_columns)
@@ -97,7 +98,8 @@ plate_view <- function(df, meta, plate = 96) {
   # Create a data.frame with all the wells and IDs, even if some are missing.
   full <- meta |>
     full_join(as.data.frame(template_columns)) |>
-    arrange_at(1)
+    arrange_at(1) %>%
+    suppressMessages()
 
   # Create the labeller function for the facet plot.
   ID_labeller <- function(variable, value) {
@@ -119,7 +121,7 @@ plate_view <- function(df, meta, plate = 96) {
     ) |>
     mutate(ID = replace_na(.data[["ID"]], "none")) |>
     # Create the facet plot.
-    ggplot(aes(x = .data[["Time"]], y = .data[["value"]])) +
+    ggplot(aes(x = Time, y = value)) +
     geom_line() +
     labs(
       y = "RFU",
@@ -132,7 +134,7 @@ plate_view <- function(df, meta, plate = 96) {
       axis.text.x = element_blank(),
       axis.text.y = element_blank()
     ) +
-    facet_wrap(vars(.data[["Well"]]),
+    facet_wrap(vars(Well),
[…]

### 2025-01-03 R/get_sample_locations.R
Fixed the get_sample_locations example.

@@ -5,6 +5,7 @@
 #' @param file Excel file exported from MARS
 #' @param tab_name Table name containing the sample IDs.
 #' @param dilution_bool Logical; is there a table containing dilution factors? If so, will add a newline and the log of the dilution factor to the ID column.
+#' @param dilution_fun A function for transforming the dilution factor.
 #' @param plate Integer; either 96 or 384 to denote microplate type.
 #'
 #' @return A vector containing well IDs.
@@ -20,42 +21,41 @@
 #'   file = "test.xlsx",
 #'   package = "quicR"
 #' )
-#' get_sample_locations(file, "Sample IDs", TRUE, 96)
+#' get_sample_locations(file)
 #'
 #' @export
-get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = FALSE, plate = 96) {
+get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = FALSE, dilution_fun = function(x) 1*x, plate = 96) {
 
-  return(
-    data.frame(
-      wells = get_wells(file) %>%
-        suppressMessages(),
-      IDs = (
-        organize_tables(file, plate = plate) %>%
-          convert_tables() %>%
-          suppressMessages()
-      )[[tab_name]] %>%
+  data.frame(
+    wells = get_wells(file),
+    IDs = (
+      organize_tables(file, plate = plate) %>%
+        convert_tables() %>%
+        suppressMessages() %>%
         na.omit()
-    ) %>%
-      mutate(
-        "IDs" = ifelse(
-          str_length(.[["IDs"]]) > 12,
-          gsub(" ", "\n", .[["IDs"]]),
-          .[["IDs"]]
-        ),
-        "IDs" = if (dilution_bool) {
-          paste(
-            as.character(.[["IDs"]]),
-            "\n",
-            (organize_tables(file) %>%
-               convert_tables() %>%
-               suppressMessages())[["Dilutions"]] %>%
-              as.numeric() %>%
-              log10() * -1 %>%
-              na.omit()
-          )
-        } else {
-          .[["IDs"]]
-        }
-    )
+    )[[tab_name]],
+    row.names = NULL
+  ) %>%
+    na.omit() %>%
+    mutate(
+      "IDs" = ifelse(
+        str_length(.[["IDs"]]) > 12,
+        gsub(" ", "\n", .[["IDs"]]),
+        .[["IDs"]]
+      ),
+      "IDs" = if (dilution_bool) {
[…]

### 2025-01-03 R/plate_view.R
Fixed the plate_view example.

@@ -25,33 +25,17 @@
 #'   package = "quicR"
 #' )
 #'
-#' tab <- organize_tables(file)
-#' IDs <- quicR::convert_tables(tab)[["Sample IDs"]] |>
-#'   na.omit()
-#'
 #' # Get the real-time data.
 #' df_ <- get_real(file, ordered = FALSE)[[1]] |>
 #'   as.data.frame()
 #'
-#' # Set the time column as the df index.
-#' rownames(df_) <- df_[, 1]
+#' sample_locations <- get_sample_locations(
+#'   file,
+#'   dilution_bool = TRUE,
+#'   dilution_fun = function(x) -log10(x)
+#' )
 #'
-#' # Remove the time column and ID row.
-#' df_ <- df_[, -1]
-#'
-#' # Get the wells used in the run.
-#' wells <- get_wells(file)
-#'
-#' # Take the metadata and apply it into a dataframe for the plate_view function.
-#' sample_locations <- cbind(wells, IDs) |>
-#'   stats::na.omit()
-#'
-#' # Wrap the text if it is too long.
-#' sample_locations <- sample_locations |>
-#'   dplyr::mutate(IDs = ifelse(stringr::str_length(IDs) > 12, gsub(" ", "\n", IDs), IDs))
-#'
-#' # Make the plate view figure.
-#' plate_view(df_, sample_locations, plate = 96)
+#' plate_view(df_, sample_locations)
 #' }
 #'
 #' @export

### 2025-01-03 R/get_wells.R
Suppressing messages from get_wells.

@@ -17,7 +17,8 @@
 #' @export
 get_wells <- function(file) {
   if (is.character(file)) {
-    df <- read_excel(file, sheet = 2, col_names = FALSE)
+    df <- read_excel(file, sheet = 2, col_names = FALSE) %>%
+      suppressMessages()
   } else if (is.data.frame(file)) {
     df <- file
   } else {

### 2025-01-03 man/manuscript/manuscript.qmd
Update manuscript.

@@
       corresponding: true
+    - name:
+        given: Peter
+        family: Larsen
+        id: PL
+        orcid: 0000-0000-0000-0000
+        email: plarsen@umn.edu
+        affiliation:
+          name: University of Minnesota
+          city: Saint Paul
+          state: MN
+        roles:
+          Supervision
+          Project administration
+          Funding
+
 abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
@@
 library(readr)
+library(ggplot2)
+library(reshape2)
 
@@
 
-data.frame("Sample IDs" = samples) %>%
+df_analyzed <- data.frame("Sample IDs" = samples, check.names = FALSE) %>%
   mutate(
@@
     # Rate of Amyloid Formation
-    RAF = ifelse(TtT == hours, 0, 1 / TtT),
-    # Crossed threshold?
-    crossed = TtT != hours
-  ) %>%
+    RAF = ifelse(TtT == hours, 0, 1 / TtT)
+  )
+
+df_analyzed%>%
   head(15) %>%
@@
 
+\newpage
+
 ## Visualization
+
+### Plate View
+```{r, warning=FALSE}
+#| fig-width: 8
+#| fig-height: 7
+sample_locations <- get_sample_locations(
+  file, 
+  dilution_bool = TRUE,
+  dilution_fun = function(x) -log10(x)
+)
+
+plate_view(df_, sample_locations)
+```
+
+### Summary Plots
+```{r, warning=FALSE, message=FALSE}
+#| fig-width: 6
+#| fig-height: 5
+df_analyzed %>%
+  melt(id.vars = c("Sample IDs", "Dilutions")) %>%
+  mutate_at("Dilutions", as.factor) %>%
+
+  ggplot(aes(`Sample IDs`, value, fill = Dilutions)) +
+    geom_boxplot() +
+    facet_wrap(~variable, scales = "free")
+```
 

### 2025-01-05 R/get_sample_locations.R
Added a sep argument to get_sample_locations.

@@ -6,6 +6,7 @@
 #' @param tab_name Table name containing the sample IDs.
 #' @param dilution_bool Logical; is there a table containing dilution factors? If so, will add a newline and the log of the dilution factor to the ID column.
 #' @param dilution_fun A function for transforming the dilution factor.
+#' @param sep A string used to separate the sample ID and dilution factor.
 #' @param plate Integer; either 96 or 384 to denote microplate type.
 #'
 #' @return A vector containing well IDs.
@@ -24,7 +25,7 @@
 #' get_sample_locations(file)
 #'
 #' @export
-get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = FALSE, dilution_fun = function(x) 1*x, plate = 96) {
+get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = FALSE, dilution_fun = function(x) 1*x, sep = "\n", plate = 96) {
 
   data.frame(
     wells = get_wells(file),
@@ -46,7 +47,7 @@ get_sample_locations <- function(file, tab_name = "Sample IDs", dilution_bool = 
       "IDs" = if (dilution_bool) {
         paste(
           as.character(.[["IDs"]]),
-          "\n",
+          sep,
           (organize_tables(file) %>%
              convert_tables() %>%
              suppressMessages())[["Dilutions"]] %>%

### 2025-01-05 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
-format: pdf
+format: 
+  pdf:
+    papersize: letter
+    documentclass: article
+    fontsize: 12pt
+    geometry:
+      - top=30mm
+      - right=30mm
+      - bottom=30mm
+      - left=30mm
 mainfont: Calibri
@@
 
-file <- "../../inst/extdata/input_files/test3.xlsx"
+file <- "../../inst/extdata/input_files/test2.xlsx"
+file_384 <- "../../inst/extdata/input_files/test384.xlsx"
 sample_file <- "../../inst/extdata/BMG_formatting/plate_layout.csv"
@@
 This file is uniquely formatted, and not easily reproduced manually.
-The function "BMG_format" allows for input of a CSV file containing the plate layout, and exports the formatted TXT file.
+The function, "BMG_format", allows for input of a CSV file containing the plate layout, and exports the formatted TXT file.
 
-### Example Plate Layout
+### Example CSV File Plate Layout
 
@@
   \hline
-  A & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
-  B & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
-  C & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
-  D & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
-  E & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
-  F & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
-  G & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
-  H & P & S12 & S13 & S14 & S15 & S16 & S17 & S18 & S19 & S20 & S21 & S22 \\ 
+  A & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  B & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  C & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  D & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  E & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  F & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  G & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+  H & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
   \hline
@@
 ```{r, message=FALSE}
-BMG_format(sample_file, write_file = FALSE)[1:18] %>% 
+BMG_format(sample_file, write_file = FALSE)[1:12] %>%
   as.data.frame()
@@
 ```{r, message=FALSE}
-tabs <- organize_tables(file)[-1]
-tabs
+tabs <- organize_tables(file)[-2]
+```
 
+#### Sample IDs
+```{r, echo=FALSE, as.is=TRUE}
+rename <- function(x) {
+  names(x) <- 1:12
+  rownames(x) <- LETTERS[1:8]
+  return(x)
+}
+
+tabs$`Sample IDs` %>%
+  as.data.frame() %>%
+  rename() %>%
+  kable(align = rep("c", 12))
+```
+
+#### Dilutions
+```{r, echo=FALSE, as.is=TRUE}
+tabs$Dilutions %>%
+  as.data.frame() %>%
+  rename() %>%
+  kable(align = rep("c", 12))
+```
+```{r, message=FALSE}
 tabs <- convert_tables(tabs)
-tabs %>% head(15) %>% kable(row.names = FALSE)
+tabs %>% head(12) %>% kable(row.names = FALSE)
+```
+
+#### Sample Locations
+Samples locations can be extracted based on their well ID.
+The "get_sample_locations" function accepts additional arguments if dilution factors were exported from MARS.
+The "dilution_fun" argument will supply a function for transforming the dilution factors (e.g.
+if the user would want to perform a log transformation).
+```{r, eval=FALSE}
+get_sample_locations(
+  file, dilution_bool = TRUE, dilution_fun = function(x) -log10(x), sep = " "
+)
+```
+```{r, echo=FALSE}
+get_sample_locations(
+  file, dilution_bool = TRUE, dilution_fun = function(x) -log10(x), sep = " "
+) %>%
+  head(12) %>%
+  kable(row.names = FALSE, align = c("c", "c"), escape = TRUE)
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
+get_real(file)[[1]]
+```
+```{r, echo=FALSE}
+columns <- 8
 df_ <- get_real(file, ordered = FALSE)[[1]] %>% as.data.frame()
-
-df_[1:15, 1:6] %>% kable(row.names = FALSE)
+df_[1:11, 1:columns] %>% kable(row.names = FALSE, align = rep("c", columns))
 ```
@@
 
-```{r}
-transpose_real(df_)[1:15, 1:13] %>% kable(row.names = FALSE)
+```{r, eval=FALSE}
+get_real(file)[[1]] %>% transpose_real()
+```
+```{r, echo=FALSE}
+columns <- 12
+transpose_real(df_)[1:7, 1:columns] %>% 
+  kable(row.names = FALSE, align = rep("c", columns))
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
+get_real(file)[[1]] %>% normalize_RFU(transposed = FALSE)
+```
+```{r, echo=FALSE, message=FALSE}
 df_norm <- normalize_RFU(df_, bg_cycle = 4, transposed = FALSE)
 
-df_norm[1:15, 1:12] %>%
+df_norm[1:7, 1:columns] %>%
   mutate_at(2:ncol(.), ~round(as.numeric(.), 2)) %>%
-  kable(row.names = FALSE)
+  kable(row.names = FALSE, align = rep("c", columns))
+
+df_norm <- df_norm %>%
+  mutate(`Sample IDs` = tabs$`Sample IDs`)
 ```
@@
 ## Calculations
-There are three analytical metrics with dedicated functions: time-to-threshold, maxpoint ratio, and maximum slope.
+There are three analytical metrics with dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
 The rate of amyloid formation does not have a designated function since it is simply the inverse of the time-to-threshold.
@@
 ### Time-to-threshold
-Time-to-threshold is calculated using the "calculate_TtT" function.
+TtT is calculated using the "calculate_TtT" function.
 The function must be supplied a threshold; default value is 2 (i.e.
@@
 
-Time-to-threshold is calculated by iterating through each row and checking if a value is greater than the threshold.
-If the value is greater, the slope of the previous timepoint to the current timepoint is calculated, and the time intersection of the current read is returned.
+TtT is calculated by iterating through each row and checking if a value is greater than the threshold.
+If the value is greater, the slope of the previous time-point to the current time-point is calculated, and the time intersection of the current read is returned.
 
 ### Maxpoint Ratio
-Maxpoint ratios (MPR) are calculated by the "calculate_MPR" function.
+MPR is calculated by the "calculate_MPR" function.
 Data must be normalized in order to derive this metric.
 In a normalized data set, the MPR is simply the maximum value achieved during the run.
+Raw data can be passed to this function, but the argument, "data_is_norm", must be set to TRUE.
+This will pass the raw data to "normalize_RFU" before calculating the MPR values.
 
 ### Maximum Slope
-The Maximum Slope (MS) is calculated by the "calculate_MS" function.
-The data can be either raw or normalized.
+MS is calculated by the "calculate_MS" function.
 The function iterates through each row using a rolling window which can be adjusted (default value is 3).
@@
 
-```{r}
-samples <- tabs$`Sample IDs` %>% na.omit()
+```{r, eval=FALSE}
+samples <- tabs$`Sample IDs`
+dilutions <- tabs$Dilutions
+
+df_norm <- get_real(file) %>% normalize_RFU()
+
+data.frame("Sample IDs" = samples, check.names = FALSE) %>%
+  mutate(
+    Dilutions = -log10(dilutions),
+    # Maxpoint Ratio
+    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
+    # Max Slope
+    MS = calculate_MS(df_norm, data_is_norm = TRUE),
+    # Time to Threshold
+    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
+    # Rate of Amyloid Formation
+    RAF = 1 / TtT
+  )
+```
+
+```{r, echo=FALSE}
+samples <- tabs$`Sample IDs`
 dilutions <- tabs$Dilutions %>% na.omit() %>% as.numeric()
-
-# Define the number of hours that the rxn ran for.
-hours <- as.numeric(colnames(df_norm)[ncol(df_norm)])
 
@@
     # Rate of Amyloid Formation
-    RAF = ifelse(TtT == hours, 0, 1 / TtT)
+    RAF = 1 / TtT
   )
@@
 df_analyzed%>%
-  head(15) %>%
-  kable(row.names = FALSE)
+  head(12) %>%
+  kable(row.names = FALSE, align = rep("c", ncol(df_analyzed)))
 ```
@@
 ### Plate View
+The "plate_view" function requires *un-transposed* data and sample locations as arguments. It also has an argument for plate type which will either be 96 or 384.
 ```{r, warning=FALSE}
-#| fig-width: 8
-#| fig-height: 7
+#| fig-width: 12
+#| fig-height: 8
 sample_locations <- get_sample_locations(
@@
     geom_boxplot() +
-    facet_wrap(~variable, scales = "free")
+    facet_wrap(~variable, scales = "free") +
+    theme(
+      legend.position = "bottom",
+      strip.text = element_text(face = "bold"),
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
+    )
 ```
@@
 # Usage
+
+## Installation
+```{r, eval=FALSE}
+# Latest CRAN release
+install.packages("quicR")
+
+# Development version
+install.packages("devtools")
+library(devtools)
+
+install_github("gage1145/quicR")
+```
 

### 2025-01-06 R/BMG_format.R
Fixed bug where BMG_format wouldn't write a TXT file.

@@ -27,7 +27,7 @@
 #' BMG_format(layout_file)
 #'
 #' @export
-BMG_format <- function(file, save_path = "./", save_name = "formatted.txt", write_file = FALSE) {
+BMG_format <- function(file, save_path = "", save_name = "formatted.txt", write_file = FALSE) {
   df_ <- read.csv(file, header = F)
   colnames(df_) <- c("col", df_[1, -1])
   df_ <- df_[-1, ]
@@ -88,8 +88,8 @@ BMG_format <- function(file, save_path = "./", save_name = "formatted.txt", writ
     apply(1, format_row) |>
     na.omit()
   if (write_file == TRUE) {
-    writeLines(paste(save_path, save_name))
-  } else {
-    return(formatted)
+    writeLines(formatted, paste0(save_path, save_name))
+
   }
+  return(formatted)
 }

### 2025-01-06 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 Given that the technology is still relatively new, academic and industry standards have yet to be established.
-'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis.
+'quicR' was developed to fill this lack of standardization by providing functions for data curation, analysis, and vizualiztion.
 keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
@@
 sample_file <- "../../inst/extdata/BMG_formatting/plate_layout.csv"
+path <- "../../inst/extdata/BMG_formatting"
 ```
@@
 Real-time quaking induced conversion is a diagnostic assay that converts recombinant protein substrate into a misfolded aggregate in the presence of a misfolded seed [@Atarashi2011].
+Given the recent development and novelty of the assay, academic and industry standards for analysis have yet to be established.
+'quicR' is an attempt to provide an open-source library dedicated to RT-QuIC assays.
 
@@
 All together, these metrics provide insight into the general kinetics of an RT-QuIC reaction, and can be used together to draw a more robust diagnostic decision.
+
+quicR also provides visualization options using ggplot2 [@ggplot2016] on the backend. Figures generated by quicR functions can be manipulated using the ggplot2 "+" syntax.
 
@@
 ## Input of Sample IDs into MARS
-
 MARS allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
@@
 ### Example CSV File Plate Layout
-
 \begin{table}[ht]
@@
 ### Formatted Plate Layout for MARS Input
+The function, "BMG_format", includes the logical argument "write_file".
+If TRUE, it will create a TXT file.
+The path can be given to the "save_path" argument, and the file name can be supplied to the "save_name" argument.
+The text file will be formatted as follows, and can be imported into MARS.
 
-The function, "BMG_format", includes the logical argument "write_file".
-If true, it will create a TXT file.
-The path can be given to the "save_path" argument, and the file name can be supplied to the "save_name" argument.
-
-```{r, message=FALSE}
-BMG_format(sample_file, write_file = FALSE)[1:12] %>%
-  as.data.frame()
+```{r, eval=FALSE, message=FALSE}
+BMG_format(sample_file, write_file = TRUE)
+```
+```
+A1  P      P
+B1  P      P
+C1  P      P
+D1  P      P
+E1  N      N
+F1  N      N
+G1  N      N
+H1  N      N
+A2  X1     S01
+B2  X1     S01
+C2  X1     S01
+D2  X1     S01
+E2  X1     S01
+F2  X1     S01
+G2  X1     S01
+H2  X1     S01
 ```
@@
 ## Data Cleaning and Transformation
-
 The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
-Typically, the first sheet in the workbook will include microplate views of data.
-The two tables that are most relevant on this sheet are the "Sample IDs" table and the "Dilutions" table (if included).
+Typically, the first sheet in the workbook will include microplate views of both raw data and metadata.
+The two tables that are most relevant on this sheet are the "Sample IDs" and the "Dilutions" tables (if included).
 For much of the downstream analysis, it is crucial the the "Sample IDs" table was exported.
@@
 ### Retrieving Metadata
-
 The metadata is defined as either sample-dependent or -independent.
 Sample-dependent metadata includes information such as sample IDs and dilution factors, whereas sample-independent metadata includes the date, time, reaction ID, etc.
-
-#### Sample-Dependent Metadata
 
@@
 ```
+
 ```{r, message=FALSE}
@@
 get_sample_locations(
-  file, dilution_bool = TRUE, dilution_fun = function(x) -log10(x), sep = " "
+  file, 
+  dilution_bool = TRUE, 
+  dilution_fun = function(x) 
+    -log10(x), 
+  sep = " "
 )
@@
   head(12) %>%
-  kable(row.names = FALSE, align = c("c", "c"), escape = TRUE)
+  kable(row.names = FALSE, align = c("c", "c"))
 ```
+
+\newpage
 
@@
 
-```{r, message=FALSE}
-get_meta(file) %>% as.data.frame()
+```{r, eval=FALSE}
+get_meta(file)
+```
+```{r, echo=FALSE, message=FALSE}
+get_meta(file) %>%
+  mutate_at("Meta_info", ~gsub("\\\\", "/", .)) %>%
+  kable(row.names = FALSE)
 ```
@@
 ### Retrieving and Manipulating Raw Data
-
 The raw data is typically found on the second sheet of the Excel workbook.
@@
 
+\newpage
+
 #### Retrieve Raw Data
-
 ```{r, eval=FALSE}
@@
 #### Transpose Raw Data
-
-This data is structured such that each sample is its own column as well as the time points.
-This format can be non-ideal, and should be transposed for downstream manipulation using the function, "transpose_real".
-After transposition, each time point has its own column, and there is a single column for every sample ID.
+This data is structured such that each sample is its own column (variable) and each row (observation) is a time point.
+While this format is technically correct, a transposed format is more ideal for some downstream manipulation.
+This operation is performed using the function, "transpose_real".
+After transposition, each time point is an individual column (variable), and each sample is an individual row (observation).
 
@@
 
+\newpage
+
 #### Normalize Raw Data
-
 The function "normalize_RFU" will convert the raw data into a background normalized data set.
 The function includes two additional arguments, "bg_cycle" (the cycle which will be used as the background fluorescence value) and "transposed" (if FALSE, will make a call to the "transpose_real" function).
+Note that the fourth time point is all "1's" since this was designated the background cycle.
 
@@
 ```
-
-The reader will notice that the fourth time column is all "1's" since this was designated the background cycle.
 
@@
 
+\newpage
+
 ### Summary Plots
 ```{r, warning=FALSE, message=FALSE}
-#| fig-width: 6
-#| fig-height: 5
+#| fig-width: 8
+#| fig-height: 6.5
 df_analyzed %>%
@@
       strip.text = element_text(face = "bold"),
-      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+      axis.title = element_blank()
     )
 ```
+
+\newpage
 
@@
 # Development version
-install.packages("devtools")
-library(devtools)
-
-install_github("gage1145/quicR")
+devtools::install_github("gage1145/quicR")
 ```
@@
 # Conclusion
+quicR provides improved and standardized methods for analyzing RT-QuIC data.
 

### 2025-01-09 man/manuscript/manuscript.qmd
Fixed table issues.

@@
       - left=30mm
+    include-in-header: 
+      - text: \usepackage{tabularray}
+      - text: \usepackage{float}
+      - text: \floatplacement{table}{H}
 mainfont: Calibri
@@
 # Methods
-This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stats, stringr, tidyr.
+This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stats, stringr, and tidyr.
 Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx and readxl, were fundamental to performing downstream handling.
 The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization.
-The janitor package has useful functions for performing quick data cleaning
+The janitor package has useful functions for performing quick data cleaning.
 
@@
 The functions were designed with usability and reproducibility in mind, ensuring compatibility between multiple labs.
-Currently, the package accepts data exported from the MARS software as an Excel workbook.
+Currently, the package accepts data exported from the proprietary MARS software (BMG Labtech, Ortenberg, Germany) as an Excel workbook.
 
@@
 This file is uniquely formatted, and not easily reproduced manually.
-The function, "BMG_format", allows for input of a CSV file containing the plate layout, and exports the formatted TXT file.
+The function, "BMG_format", allows for input of a CSV file containing the plate layout (see @tbl-layout for proper formatting), and exports the formatted TXT file.
 
-### Example CSV File Plate Layout
-\begin{table}[ht]
-\centering
-\begin{tabular}{|c|cccccccccccc|}
+<!-- ### Example CSV File Plate Layout -->
+:::{#tbl-layout tbl-pos="ht" tbl-cap-location="bottom"}
+```{=latex}
+\begin{tblr}{
+  colspec = {|c|cccccccccccc|}, 
+  row{1} = {font=\bfseries}, 
+  column{1} = {font=\bfseries}, 
+  rowhead = 1
+}
   \hline
@@
   \hline
-\end{tabular}
-\end{table}
+\end{tblr}
+```
+Example CSV file plate layout for input into the "BMG_format" function.
+The top left corner should be cell "A1" in the file.
+The top numbered row and the left-most lettered column should never be altered.
+:::
 
@@
 The dependent metadata can be retrieved using the "organize_tables" and "convert_tables" functions.
-The former returns a list of tables, and the ladder converts each table into a column in a single data frame.
+The former returns a list of tables, and the latter converts each table into a column in a single data frame.
+See @tbl-sampleids and @tbl-dilutions for example outputs of organize_tables and
 
@@
 
-#### Sample IDs
 ```{r, echo=FALSE, as.is=TRUE}
+#| label: tbl-sampleids
+#| tbl-cap: Sample IDs
 rename <- function(x) {
@@
   rename() %>%
-  kable(align = rep("c", 12))
+  kable(
+    format = "latex",
+    booktabs = TRUE,
+    linesep = "",
+    align = rep("c", 12)
+  ) %>%
+  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) %>%
+  column_spec(13, border_right = TRUE) %>%
+  row_spec(0, bold = TRUE)
+  # kable_styling(latex_options = c("HOLD_position"))
 ```
 
-#### Dilutions
 ```{r, echo=FALSE, as.is=TRUE}
+#| label: tbl-dilutions
+#| tbl-cap: Dilutions
 tabs$Dilutions %>%
@@
   rename() %>%
-  kable(align = rep("c", 12))
+  kable(
+    format = "latex",
+    booktabs = TRUE,
+    linesep = "",
+    align = rep("c", 12)
+  ) %>%
+  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) %>%
+  column_spec(13, border_right = TRUE) %>%
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(latex_options = c("scale_down"))
 ```

### 2025-01-09 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 The former returns a list of tables, and the latter converts each table into a column in a single data frame.
-See @tbl-sampleids and @tbl-dilutions for example outputs of organize_tables and
+See @tbl-tables for example outputs of organize_tables.
 
-```{r, message=FALSE}
+```{r, echo=FALSE, message=FALSE}
 tabs <- organize_tables(file)[-2]
+```
+```{r, eval=FALSE}
+organize_tables(file)
 ```
@@
 ```{r, echo=FALSE, as.is=TRUE}
-#| label: tbl-sampleids
-#| tbl-cap: Sample IDs
+#| label: tbl-tables
+#| tbl-cap: Sample IDs and Dilution Factors
 rename <- function(x) {
@@
   column_spec(13, border_right = TRUE) %>%
-  row_spec(0, bold = TRUE)
-  # kable_styling(latex_options = c("HOLD_position"))
-```
+  row_spec(0, bold = TRUE) %>%
+  kable_styling(full_width = TRUE, font_size = 10)
 
-```{r, echo=FALSE, as.is=TRUE}
-#| label: tbl-dilutions
-#| tbl-cap: Dilutions
 tabs$Dilutions %>%
@@
   row_spec(0, bold = TRUE) %>%
-  kable_styling(latex_options = c("scale_down"))
+  kable_styling(full_width = TRUE, font_size = 10)
 ```
 
-```{r, message=FALSE}
+```{r, eval=FALSE}
+organize_tables(file) %>% convert_tables()
+```
+```{r, echo=FALSE, message=FALSE}
 tabs <- convert_tables(tabs)
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ### Retrieving and Manipulating Raw Data
@@
 Therefore, the output should be indexed to access the data frame of interest.
-
-\newpage
 
@@
 ```
-
-\newpage
 
@@
 Each function below accepts input from the "transpose_real" or the "normalize_RFU" functions.
+See @tbl-metrics for an example of the output of these functions.
 
@@
 The function iterates through each row using a rolling window which can be adjusted (default value is 3).
-Given the window size, the slope is calcualated based on the range of the window.
+Given the window size, the slope is calcualated based on change in fluorescence divided by the range of the window.
 The MS is simply the largest slope value recorded.
+The units are typically reported as $\Delta$RFU/s.
+
+\newpage
 
 ```{r, eval=FALSE}
+#| label: tbl-metrics
+#| tbl-cap: Calculated metrics
+#| tbl-cap-location: bottom
+
 samples <- tabs$`Sample IDs`

### 2025-01-10 man/manuscript/manuscript.qmd
Added a function for calculating thresholds.

@@
 
+### Thresholds
+Many publications have different methods of determining thresholds.
+By and large, the most popular method is to take the average background fluorescence of the entire plate and add some multiple of standard deviations.
+The quicR package provides the "calculate_threshold" function for this purpose.
+A value can be provided as the optional argument, "multiplier", which will be applied to the standard deviation.
+```{r, eval=FALSE}
+get_real(file)[[1]] %>% calculate_threshold(multiplier = 10)
+```
+```{r, echo=FALSE}
+calculate_threshold(df_, multiplier = 10)
+```
+
 ### Time-to-threshold

### 2025-01-10 R/calculate_threshold.R

@@ -1,0 +1,43 @@
+#' Calculate a Threshold for Rate Determination
+#'
+#' Calculates a threshold for determining time-to-threshold and rate of amyloid formation.
+#'
+#' @param data A dataframe output from get_real.
+#' @param background_cycle Integer; the cycle used for background fluorescence.
+#' @param method Method for determining threshold; default is "stdev".
+#' @param multiplier For some methods, will add a multiplier for more conservative thresholds.
+#'
+#' @importFrom dplyr select
+#'
+#' @return A float value.
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test2.xlsx",
+#'   package = "quicR"
+#' )
+#' threshold <- get_real(file)[[1]] |>
+#'   calculate_threshold(multiplier = 10)
+#'
+#' @export
+calculate_threshold <- function(data, background_cycle = 2, method = list("stdev", "none"), multiplier = 1) {
+
+  if (is.list(method)) method <- method[[which(method == "stdev")]]
+  if (method == "none") return(NA)
+
+  curate <- function() {
+    data |>
+      select(-"Time") |>
+      lapply(as.numeric) |>
+      as.data.frame()
+  }
+
+  if (method == "stdev") {
+    get_row <- function() curate()[background_cycle, ]
+    avg <- function() apply(get_row(), 1, mean, na.rm = TRUE)[[1]]
+    std <- function() apply(get_row(), 1, sd, na.rm = TRUE)[[1]] * multiplier
+    return(avg() + std())
+  }
+
+}

### 2025-01-10 man/manuscript/plots.R
Added a new script for standalone plots.

@@ -1,0 +1,143 @@
+library(tidyverse)
+library(quicR)
+library(slider)
+library(ggpubr)
+library(ggrepel)
+
+
+data_is_norm <- FALSE
+file <- "../../inst/extdata/input_files/test2.xlsx"
+window <- 4
+
+curate <- function(x) {
+  x %>%
+    {if (data_is_norm) . else normalize_RFU(.)} %>%
+    t() %>%
+    as.data.frame() %>%
+    mutate_all(~ as.numeric(as.character(.))) %>%
+    suppressWarnings() %>%
+    na.omit() %>%
+    mutate(Time = as.numeric(rownames(.))) %>%
+    relocate("Time", .before = 1)
+}
+
+
+df_1 <- get_real(file, ordered = FALSE)[[1]][1:2] %>%
+  curate()
+
+
+slope <- slide(
+  df_1,
+  ~lm(`2` ~ Time, data = .x)[[1]][[2]],
+  .before = window,
+  .complete = TRUE
+) %>%
+  unlist() %>%
+  as.data.frame()
+
+slope <- rbind(NA, NA, slope, NA, NA)
+
+df_2 <- cbind(df_1, slope) %>%
+  na.omit() %>%
+  mutate_all(as.numeric)
+colnames(df_2) <- c("Time", "Raw", "Slope")
+
+ms <- max(df_2$Slope)
+ms_time <- df_2[[which(df_2$Slope == max(df_2$Slope)), "Time"]]
+
+mpr <- max(df_2$Raw)
+mpr_time <- df_2[[which(df_2$Raw == max(df_2$Raw)), "Time"]]
+threshold <- 1.2
+ttt <- min(df_2[which(df_2$Raw > threshold),][["Time"]])
+
+ggplot(df_2, aes(Time)) +
+  geom_line(aes(y = Slope), color = "blue", size = 1.2) +
+  geom_line(aes(y = Raw - 1), color = "red", size = 1.2) +
+  # geom_smooth(aes(y = Slope), color = "blue", span = 0.1, se = F, size = 1.2) +
+  # geom_smooth(aes(y = Raw - 1), color = "red", span = 0.1, se = F, size = 1.2) +
+
+  geom_hline(yintercept = ms, color = "darkblue", size = 1.2, linetype = "dashed") +
+  # geom_vline(xintercept = ms_time, color = "darkblue", size = 1.2, linetype = "dashed") +
+  geom_hline(yintercept = mpr - 1, color = "darkred", size = 1.2, linetype = "dashed") +
[…]

### 2025-01-10 man/manuscript/manuscript.qmd
Updated the manuscript.

@@
       - left=30mm
+    fig-pos: "H"
     include-in-header: 
@@
 library(dplyr)
+library(tidyr)
 library(kableExtra)
@@
 # Introduction
-Real-time quaking induced conversion is a diagnostic assay that converts recombinant protein substrate into a misfolded aggregate in the presence of a misfolded seed [@Atarashi2011].
-Given the recent development and novelty of the assay, academic and industry standards for analysis have yet to be established.
-'quicR' is an attempt to provide an open-source library dedicated to RT-QuIC assays.
+Real-time quaking induced conversion is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates.
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Atarashi2011].
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies.
+However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation.
 
-While standard metrics for determining a diagnosis have not been universally established, there are certain metrics that many research groups have found useful.
-These include time-to-threshold (TtT)[@Orru2015], rate of amyloid formation (RAF)[@Gallups2022], maxpoint ratio (MPR)[@Rowden2023], and maximum slope (MS)[@Henderson2015].
-All together, these metrics provide insight into the general kinetics of an RT-QuIC reaction, and can be used together to draw a more robust diagnostic decision.
+To address this gap, we introduce quicR, an open-source R library dedicated to the manipulation, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field.
+quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
 
-quicR also provides visualization options using ggplot2 [@ggplot2016] on the backend. Figures generated by quicR functions can be manipulated using the ggplot2 "+" syntax.
+While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results. These include:
+
+-   Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold, indicating amyloid formation [@Orru2015].
+-   Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into relative misfolded seed quantity [@Gallups2022].
+-   Maxpoint ratio (MPR): A ratio-based metric for comparing peak normalized fluorescence intensities [@Rowden2023].
+-   Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation [@Henderson2015].
+
+Together, these metrics enable researchers to characterize the kinetics of RT-QuIC reactions comprehensively, enhancing the rigor and reliability of diagnostic decisions.
+
+In addition to analytical tools, quicR provides flexible and customizable visualization capabilities.
+Leveraging the powerful ggplot2 library [@ggplot2016], quicR enables users to generate high-quality, publication-ready figures.
+These visualizations can be further customized using the intuitive + syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
+
+By combining standardized metrics, advanced visualization tools, and a commitment to open science, quicR serves as a foundational resource for the growing RT-QuIC community.
+Its goal is to empower researchers to analyze and present their data with clarity, consistency, and confidence.
 
 # Methods
-This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stats, stringr, and tidyr.
-Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx and readxl, were fundamental to performing downstream handling.
-The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization.
-The janitor package has useful functions for performing quick data cleaning.
+
+## Dependencies
+This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stringr, and tidyr.
+Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing downstream handling.
+The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization [@tidyverse2019].
+The janitor package [@janitor2024] has data cleaning functions which were useful when importing data from Excel.
+The slider package provides tools which apply some function to a moving window which was crucial for determining the approximate derivative of raw data [@slider2024].
+
+## Input Data Formatting
+MARS exports data into Excel workbooks.
+For many of the quicR functions to work together, the workbooks must be formatted correctly.
+In MARS, select "Excel Report", and a pop-up window will appear (see [@fig-mars]).
+The following options must be checked for proper output: "Microplate View", "Table view", "Transpose table", and "Add test run information".
+After clicking "Export report to Excel", an Excel workbook is created such as in [@fig-marsoutput].
+
+![Excel export settings in MARS](images/MARS_settings.png){#fig-mars height=50%}
+
+:::{#fig-marsoutput layout-nrow=2}
+![Microplate view Excel spreadsheet.
+This is the first spreadsheet in the workbook and contains the plate layouts of any data the user exported from MARS.
+Typically, there is a header containing metadata followed by a number of named matrices.](images/sheet1.png){#fig-sheet1 height=50%}
+
+![Table view Excel spreadsheet.
+This is the second spreadsheet in the workboook and contains columns of each well and time points.
+Each cell is a raw fluorescent value.
+This spreadsheet will also contain a header, but was excluded from this figure.](images/sheet2.png){#fig-sheet2 height=50%}
+
+Excel spreadsheet exported from MARS.  
+:::
+
+## Key Metrics and Calculations
+quicR has functions for calculating TtT, MPR, and MS.
+A graphical representation of these can be found in [@fig-metrics].
+There is no dedicated function for RAF since it can simply be expressed as the inverse of TtT, and can therefore be calculated separately as in [@tbl-metrics].
+
+TtT is calculated by iterating through each sample until a value is greater than the supplied threshold.
+It then determines the intersection between the previous and current read times and the threshold.
+If no value was found larger than the threshold, the total reaction run-time is returned.
+
+MPR is defined as the maximum fluorescence divided by the background fluorescence.
+Thus, in order to calculate, the raw data must first be normalized against the background.
+This is done by choosing a cycle for background determination, and then dividing each read by that value.
+Once this is done, the MPR is taken as the max value.
+
+Finally, MS is determined by approximating the maximum of the derivative of the raw data and is typically reported in units of $\Delta$RFU/h (i.e.
+the change in relative fluorescent units per hour).
+Originally, this was accomplished by applying a linear regression to a sliding window; however, this proved to be very computationally expensive.
+Now, the slopes are calculated using differences between two data points within the range of the sliding window.
+While this slightly reduces the accuracy of the approximation, it was decided that the improvement in computation time was worth the loss in accuracy.
+
+![Example graphs highlighting the different calculated metrics.
+The red curve represents a raw data curve that has been normalized against background.
+MPR is calculated as the maximum fluorescent value achieved in the normalized raw data.
+TtT is determined as the time required to cross a given threshold (in this example, the threshold is 0.2).
+The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.](images/metric_example.png){#fig-metrics}
 
 # Development
-The quicR package was developed to address the need for efficient data conversion and analysis of RT-QuIC data.
+![Workflow hierarchy of the quicR package.
+Blue nodes indicate steps where BMG software is needed.
+Purple nodes indicate functions dedicated to handling metadata.
+Red nodes are functions that acquire and manipulate raw data.
+Orange nodes are functions which calculate some metric.
+Finally, yellow nodes represent endpoints in the data analysis.](images/workflow.png){#fig-workflow}
+
+quicR was developed to address the need for efficient data conversion and analysis of RT-QuIC data.
 The functions were designed with usability and reproducibility in mind, ensuring compatibility between multiple labs.
 Currently, the package accepts data exported from the proprietary MARS software (BMG Labtech, Ortenberg, Germany) as an Excel workbook.
+
+This project was devloped using Git version control.
+GitHub workflows were utilized to ensure that the package is able to be installed on current operating systems.
+Additionally, tests were performed on each function using the testthat package [@testthat2011].
 
@@
 # Implementation
+The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of real-time fluorescence data.
+This section provides a comprehensive guide to utilizing the package's key functionalities, detailing how to:
+
+1.  Format and input sample data into MARS.
+2.  Extract, clean, and organize metadata and raw fluorescence data.
+3.  Apply transformations and normalization to raw data for downstream analysis.
+4.  Calculate critical analytical metrics, such as time-to-threshold (TtT), rate of amyloid formation (RAF), maxpoint ratio (MPR), and maximum slope (MS).
+
+These steps are designed to enhance reproducibility, minimize manual data handling, and enable seamless integration with the MARS software workflow.
+Through practical examples, this section illustrates how each function operates, along with expected input and output formats, ensuring clarity and ease of use for researchers.
 
 ## Input of Sample IDs into MARS
-MARS allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
 This file is uniquely formatted, and not easily reproduced manually.
 The function, "BMG_format", allows for input of a CSV file containing the plate layout (see @tbl-layout for proper formatting), and exports the formatted TXT file.
+The file can then be imported into the control software before running.
 
-<!-- ### Example CSV File Plate Layout -->
-:::{#tbl-layout tbl-pos="ht" tbl-cap-location="bottom"}
+:::{#tbl-layout tbl-pos="ht"}
 ```{=latex}
@@
 Example CSV file plate layout for input into the "BMG_format" function.
-The top left corner should be cell "A1" in the file.
+The top left corner should be cell "A1" in the CSV file.
 The top numbered row and the left-most lettered column should never be altered.
 :::
-
-\newpage
 
@@
 The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
-Typically, the first sheet in the workbook will include microplate views of both raw data and metadata.
-The two tables that are most relevant on this sheet are the "Sample IDs" and the "Dilutions" tables (if included).
+Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what will be most useful.
+Those tables are the "Sample IDs" and the "Dilutions" tables (if dilutions were included in the export).
 For much of the downstream analysis, it is crucial the the "Sample IDs" table was exported.
-If there is no table, the user can simply add it manually.
+If there is no table, the user can simply add it manually (see [@fig-sheet1] for proper formatting).
 
@@
 The former returns a list of tables, and the latter converts each table into a column in a single data frame.
-See @tbl-tables for example outputs of organize_tables.
+See @tbl-tables and @tbl-converted for example outputs of these functions.
 
@@
 ```{r, echo=FALSE, message=FALSE}
+#| label: tbl-converted
+#| tbl-cap: The tables extracted from the "organize_tables" function are converted into columns in a dataframe. This format is much more compatible with downstream analysis.
 tabs <- convert_tables(tabs)
@@
 
-\newpage
-
-#### Sample Locations
+### Sample Locations
 Samples locations can be extracted based on their well ID.
@@
 if the user would want to perform a log transformation).
+This output of this function is critical as an argument in "plate_view" function which is further explained in the visualization section.
+
 ```{r, eval=FALSE}
@@
 
-\newpage
-
-#### Sample-Independent Metadata
+### Sample-Independent Metadata
 The independent metadata can be retrieved using the "get_meta" function. This data is included in the header of the excel workbook.
@@
 
-\newpage
+### Retrieving and Manipulating Raw Data
+The raw, real-time data is typically found on the second sheet of the Excel workbook. There are three functions dedicated to the retrieval and cleaning of raw data.
+1.  get_real: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
+2.  transpose_real: Swaps the rows and columns which makes some downstream analyses easier.
+3.  normalize_RFU: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
 
-### Retrieving and Manipulating Raw Data
-The raw data is typically found on the second sheet of the Excel workbook.
-The raw real-time data can be retrieved using the "get_real" function.
+### Retrieve Raw Data
+Raw data can be retrieved using the "get_real" function.
 The logical argument, "ordered", indicates whether the user would prefer the columns to be ordered by well or by sample ID.
@@
 Therefore, the output should be indexed to access the data frame of interest.
-
-#### Retrieve Raw Data
 ```{r, eval=FALSE}
@@
 
-\newpage
-
-#### Transpose Raw Data
+### Transpose Raw Data
 This data is structured such that each sample is its own column (variable) and each row (observation) is a time point.
@@
 
-#### Normalize Raw Data
+### Normalize Raw Data
 The function "normalize_RFU" will convert the raw data into a background normalized data set.
@@
 ```{r, eval=FALSE}
-get_real(file)[[1]] %>% calculate_threshold(multiplier = 10)
+get_real(file)[[1]] %>% 
+  calculate_threshold(method = "stdev", multiplier = 10)
 ```
 ```{r, echo=FALSE}
-calculate_threshold(df_, multiplier = 10)
+calculate_threshold(df_, method = "stdev", multiplier = 10)
 ```
 
-### Time-to-threshold
+### Time-to-threshold & Rate of Amyloid Formation
 TtT is calculated using the "calculate_TtT" function.
@@
 The function iterates through each row using a rolling window which can be adjusted (default value is 3).
-Given the window size, the slope is calcualated based on change in fluorescence divided by the range of the window.
+Given the window size, the slope is calculated based on change in fluorescence divided by the range of the window.
 The MS is simply the largest slope value recorded.
-The units are typically reported as $\Delta$RFU/s.
-
-\newpage
+The units are typically reported as $\Delta$RFU/h.
 
 ```{r, eval=FALSE}
-#| label: tbl-metrics
-#| tbl-cap: Calculated metrics
-#| tbl-cap-location: bottom
-
-samples <- tabs$`Sample IDs`
-dilutions <- tabs$Dilutions
-
 df_norm <- get_real(file) %>% normalize_RFU()
 
-data.frame("Sample IDs" = samples, check.names = FALSE) %>%
+data.frame("Sample IDs" = tabs$`Sample IDs`) %>%
   mutate(
-    Dilutions = -log10(dilutions),
-    # Maxpoint Ratio
+    Dilutions = -log10(tabs$dilutions),
     MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
-    # Max Slope
     MS  = calculate_MS(df_norm, data_is_norm = TRUE),
-    # Time to Threshold
     TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
-    # Rate of Amyloid Formation
     RAF = 1 / TtT
@@
 ```{r, echo=FALSE}
-samples <- tabs$`Sample IDs`
-dilutions <- tabs$Dilutions %>% na.omit() %>% as.numeric()
-
-df_analyzed <- data.frame("Sample IDs" = samples, check.names = FALSE) %>%
+#| label: tbl-metrics
+#| tbl-cap: Calculated metrics
+#| tbl-cap-location: top
+df_analyzed <- data.frame("Sample IDs" = tabs$`Sample IDs`, check.names = FALSE) %>%
   mutate(
-    Dilutions = -log10(dilutions),
-    # Maxpoint Ratio
-    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE),
-    # Max Slope
-    MS = calculate_MS(df_norm, data_is_norm = TRUE),
-    # Time to Threshold
-    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3),
-    # Rate of Amyloid Formation
-    RAF = 1 / TtT
+    Dilutions = -log10(tabs$Dilutions %>% na.omit() %>% as.numeric()),
+    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE) %>% round(2),
+    MS = calculate_MS(df_norm, data_is_norm = TRUE) %>% round(3),
+    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3) %>% round(2),
+    RAF = (1 / TtT) %>% round(4)
   )
-
 df_analyzed%>%

### 2025-01-11 man/manuscript/manuscript.qmd
Updated manuscript plots and workflow diagram

@@
 ---
-title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
+title: "quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays"
 author:
@@
 'quicR' was developed to fill this lack of standardization by providing functions for data curation, analysis, and vizualiztion.
-keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
+keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
 format: 
@@
     geometry:
-      - top=30mm
-      - right=30mm
-      - bottom=30mm
-      - left=30mm
+      - top=20mm
+      - right=20mm
+      - bottom=20mm
+      - left=20mm
     fig-pos: "H"
@@
 # Introduction
-Real-time quaking induced conversion is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates.
+Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates.
 The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Atarashi2011].
@@
 ## Dependencies
-This package requires the following dependencies: dplyr, ggplot2, janitor, openxlsx, readxl, reshape2, slider, stringr, and tidyr.
+This package requires the following dependencies: dplyr, ggplot2, stringr, tidyr, janitor, openxlsx, readxl, reshape2, and slider.
 Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing downstream handling.
@@
 
-## Input Data Formatting
+\newpage
+
+## Input Formatting
 MARS exports data into Excel workbooks.
@@
 Orange nodes are functions which calculate some metric.
-Finally, yellow nodes represent endpoints in the data analysis.](images/workflow.png){#fig-workflow}
+Finally, yellow nodes represent endpoints in the data analysis.](images/workflow2.png){#fig-workflow}
 
@@
 
-1.  Format and input sample data into MARS.
+1.  Format and input sample data into Omega control software (BMG Labtech, Ortenberg, Germany).
 2.  Extract, clean, and organize metadata and raw fluorescence data.
@@
 
-## Input of Sample IDs into MARS
+## Input of Sample IDs into Omega Control Software
 The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
@@
 :::
+
+\newpage
 
@@
 See @tbl-tables and @tbl-converted for example outputs of these functions.
-
+\newpage
 ```{r, echo=FALSE, message=FALSE}
@@
 #| label: tbl-tables
-#| tbl-cap: Sample IDs and Dilution Factors
+#| tbl-cap: Sample IDs and Dilution Factors. Note that these are the same tables shown in [@fig-sheet1].
 rename <- function(x) {
@@
 tabs <- convert_tables(tabs)
-tabs %>% head(12) %>% kable(row.names = FALSE)
+tabs %>% head(12) %>% kable(row.names = FALSE, align = c("c", "c"))
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ### Transpose Raw Data
@@
 
+\newpage
+
 ```{r, eval=FALSE}
@@
 
+\newpage
+
 ## Visualization

### 2025-01-11 man/manuscript/plots.R

@@ -5,139 +5,70 @@ library(ggpubr)
 library(ggrepel)
 
 
-data_is_norm <- FALSE
-file <- "../../inst/extdata/input_files/test2.xlsx"
-window <- 4
 
-curate <- function(x) {
-  x %>%
-    {if (data_is_norm) . else normalize_RFU(.)} %>%
-    t() %>%
-    as.data.frame() %>%
-    mutate_all(~ as.numeric(as.character(.))) %>%
-    suppressWarnings() %>%
-    na.omit() %>%
-    mutate(Time = as.numeric(rownames(.))) %>%
-    relocate("Time", .before = 1)
+# Smoothed Functions ------------------------------------------------------
+
+
+
+S <- 5.13534
+a <- 314730
+b <- -1.61059
+E <- -1.43142
+c <- 78.01494
+d <- -0.304958
+
+raw_func <- function(x) {
+  ratio1 <- S/(1 + a * exp(b * x))
+  ratio2 <- E/(1 + c * exp(d * x))
+  return(ratio1 + ratio2)
 }
 
+deriv_func <- function(x) {
+  ratio1 <- -S * a * b * exp(b * x) / (a * exp(b * x) + 1)^2
+  ratio2 <- -E * c * d * exp(d * x) / (c * exp(d * x) + 1)^2
+  ratio1 + ratio2
+}
 
-df_1 <- get_real(file, ordered = FALSE)[[1]][1:2] %>%
-  curate()
+df_ <- data.frame(x = seq(0, 48, 0.1)) %>%
+  mutate(raw = raw_func(x), der = deriv_func(x))
 
+threshold <- 0.2
+ttt <- min(df_[which(df_$raw > threshold), "x"])
+mpr <- max(df_$raw)
+mpr_time <- df_[which(df_$raw == max(df_$raw)), "x"]
+ms <- max(df_$der)
+ms_time <- df_[which(df_$der == max(df_$der)), "x"]
 
-slope <- slide(
-  df_1,
-  ~lm(`2` ~ Time, data = .x)[[1]][[2]],
-  .before = window,
-  .complete = TRUE
-) %>%
-  unlist() %>%
-  as.data.frame()
+ggplot(df_, aes(x)) +
+  geom_line(aes(y = raw), color = "darkred", size = 1.2) +
+  geom_line(aes(y = der), color = "darkblue", size = 1.2) +
 
-slope <- rbind(NA, NA, slope, NA, NA)
[…]

### 2025-01-11 man/manuscript/manuscript.qmd
Added more references

@@
 abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
-Given that the technology is still relatively new, academic and industry standards have yet to be established.
-'quicR' was developed to fill this lack of standardization by providing functions for data curation, analysis, and vizualiztion.
+Given that the technology is still relatively new, academic and industry standards for cleaning data and analyzing results have yet to be fully established.
+The open source R library, quicR, was developed to fill this lack of standardization.
+This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualiztion.
 keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
@@
 # Introduction
-Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates.
-The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Atarashi2011].
-The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies.
-However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation.
+Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates [@Atarashi2011].
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Wilham2010; @Orru2012; @Bongianni2019; @Orru2017; @Orru2015; @Dassanayake2016; @Hwang2018; @Groveman2018; @Metrick2020].
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies [@Fiorini2020; @Franceschini2017; @Picasso-Risso2022, @Holz2021].
+However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation [@Rowden2023].
 
-To address this gap, we introduce quicR, an open-source R library dedicated to the manipulation, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field.
+To address this gap, we introduce quicR, an open-source library, developed in R [@R2024], dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of seeded amplification assays.
 quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
 
-While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results. These include:
+While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics. These include:
 
--   Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold, indicating amyloid formation [@Orru2015].
--   Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into relative misfolded seed quantity [@Gallups2022].
--   Maxpoint ratio (MPR): A ratio-based metric for comparing peak normalized fluorescence intensities [@Rowden2023].
+-   Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold [@Orru2015].
+-   Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed [@Gallups2022].
+-   Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities [@Rowden2023].
 -   Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation [@Henderson2015].
@@
 Leveraging the powerful ggplot2 library [@ggplot2016], quicR enables users to generate high-quality, publication-ready figures.
-These visualizations can be further customized using the intuitive + syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
+These visualizations can be further customized using the intuitive '+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
 
-By combining standardized metrics, advanced visualization tools, and a commitment to open science, quicR serves as a foundational resource for the growing RT-QuIC community.
-Its goal is to empower researchers to analyze and present their data with clarity, consistency, and confidence.
+By combining standardized metrics, advanced visualization tools, and a commitment to open source science, quicR serves as a foundational resource for the growing RT-QuIC community.
+Its goal is to empower researchers to analyze and present their data with clarity, consistency, and cohesion.
 
@@
 
-### Retrieving and Manipulating Raw Data
+## Retrieving and Manipulating Raw Data
 The raw, real-time data is typically found on the second sheet of the Excel workbook. There are three functions dedicated to the retrieval and cleaning of raw data.

### 2025-01-13 man/manuscript/manuscript.qmd
Update manuscript

@@
 title: "quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays"
-author:
-    - name: 
-        given: Gage
-        family: Rowden
-        id: GR
+authors:
+    - id: GR
+      name: Gage Rowden
       orcid: 0000-0002-7517-0480
       email: rowde002@umn.edu
-        affiliation:
-          name: University of Minnesota
+      affiliations:
+        - name: University of Minnesota
+          city: Saint Paul
+          state: MN
+        - name: Priogen Corp.
           city: Saint Paul
@@
       corresponding: true
-    - name:
-        given: Peter
-        family: Larsen
-        id: PL
-        orcid: 0000-0000-0000-0000
+    - id: PL
+      name: Peter Larsen
+      orcid: 0000-0002-3634-3625
       email: plarsen@umn.edu
-        affiliation:
-          name: University of Minnesota
+      affiliations:
+        - name: University of Minnesota
+          city: Saint Paul
+          state: MN
+        - name: Priogen Corp.
           city: Saint Paul
@@
       - text: \floatplacement{table}{H}
+    html: default
 mainfont: Calibri

### 2025-01-14 man/manuscript/manuscript.qmd
Updated manuscript

--- 2025-01-11 man/manuscript/manuscript.qmd
@@
 title: "quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays"
-author:
-    - name: 
-        given: Gage
-        family: Rowden
-        id: GR
+authors:
+    - id: GR
+      name: Gage Rowden
       orcid: 0000-0002-7517-0480
       email: rowde002@umn.edu
-        affiliation:
-          name: University of Minnesota
-          city: Saint Paul
-          state: MN
+      affil-id: 1,2,3
       roles:
@@
           Supervision
-          Prject administration
+          Project administration
       corresponding: true
-    - name:
-        given: Peter
-        family: Larsen
-        id: PL
-        orcid: 0000-0000-0000-0000
+    - id: PL
+      name: Peter Larsen
+      orcid: 0000-0002-3634-3625
       email: plarsen@umn.edu
-        affiliation:
-          name: University of Minnesota
-          city: Saint Paul
-          state: MN
+      affil-id: 1,2,3
       roles:
@@
           Funding
+affiliations:
+  - id: 1
+    name: Department of Veterinary and Biomedical Sciences, University of Minnesota, St. Paul, MN 55108, USA.
+  - id: 2
+    name: Minnesota Center for Prion Research and Outreach, University of Minnesota, St. Paul, MN 55108, USA.
+  - id: 3
+    name: Priogen Corp., St. Paul, MN 55114, USA.
 
@@
 The open source R library, quicR, was developed to fill this lack of standardization.
-This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualiztion.
+This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
 keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
@@
     fig-pos: "H"
+    keep-tex: true
+    template-partials: 
+      - title.tex
     include-in-header: 
@@
       - text: \floatplacement{table}{H}
+      - text: \usepackage[noblocks]{authblk}
+      - text: \renewcommand*{\Authsep}{, }
+      - text: \renewcommand*{\Authand}{, }
+      - text: \renewcommand*{\Authands}{, }
+      - text: \renewcommand\Affilfont{\small}
+    html: default
 mainfont: Calibri
@@
 
-file <- "../../inst/extdata/input_files/test2.xlsx"
+file <- "../../inst/extdata/input_files/test4.xlsx"
 file_384 <- "../../inst/extdata/input_files/test384.xlsx"
@@
 
+\newpage
+
 # Implementation
@@
 ```{r, echo=FALSE, message=FALSE}
-tabs <- organize_tables(file)[-2]
+tabs <- organize_tables(file)
 ```
@@
   row_spec(0, bold = TRUE) %>%
-  kable_styling(full_width = TRUE, font_size = 10)
+  kable_styling(full_width = TRUE, font_size = 8)
 
@@
 if the user would want to perform a log transformation).
-This output of this function is critical as an argument in "plate_view" function which is further explained in the visualization section.
+The output of this function is critical as an argument in the "plate_view" function which is further explained in the visualization section.
 
@@
 ```{r, echo=FALSE}
+#| label: tbl-samp-loc
+#| tbl-cap: Well locations of each sample.
+Included in this is the dilution factor which has been transformed as the negative log of original dilution values.
+This table is important for input into the plate_view function.
 get_sample_locations(
@@
 ```{r, echo=FALSE, message=FALSE}
+#| label: tbl-meta
+#| tbl-cap: Metadata which is included in the header of the Excel file.
 get_meta(file) %>%
@@
 
+\newpage
+
 ### Retrieve Raw Data
@@
 ```{r, eval=FALSE}
+#| label: tbl-raw
+#| tbl-cap: Raw data retrieved directly from the MARS output file.
 get_real(file)[[1]]
@@
 ```{r, eval=FALSE}
+#| label: tbl-transposed
+#| tbl-cap: Transposed raw data. This converted the data columns to rows and the rows to columns.
 get_real(file)[[1]] %>% transpose_real()
@@
 ```{r, echo=FALSE, message=FALSE}
+#| label: tbl-norm
+#| tbl-cap: Normalized raw data Note that the "transposed" argument was set to false, so a call was made to the "transpose_real" function.
 df_norm <- normalize_RFU(df_, bg_cycle = 4, transposed = FALSE)
@@
 
-### Time-to-threshold & Rate of Amyloid Formation
+### Time-to-Threshold & Rate of Amyloid Formation
 TtT is calculated using the "calculate_TtT" function.
@@
 ```{r, eval=FALSE}
-df_norm <- get_real(file) %>% normalize_RFU()
+df_norm <- get_real(file)[[1]] %>% normalize_RFU()
 
@@
     geom_boxplot() +
-    facet_wrap(~variable, scales = "free") +
+    facet_wrap(~variable, scales = "free_y") +
     theme(
@@
 
-# Validation & Performance
+## Example Workflow
+```{r, eval=FALSE}
+library(quicR)
+
+# Import and Format Data --------------------------------------------------
+
+file <- "example.xlsx"
+raw <- get_real(file)[[1]]
+normal <- normalize_RFU(raw, transposed = FALSE)
+meta <- file |>
+  organize_tables() |>
+  convert_tables()
+
+# Calculate Key Metrics ---------------------------------------------------
+
+mpr <- calculate_MPR(normal, data_is_norm = TRUE)
+ms  <- calculate_MS(normal, data_is_norm = TRUE)
+ttt <- calculate_TtT(normal, threshold = 2)
+
+analyzed <- data.frame(
+  `Sample IDs`                = meta$`Sample IDs`,
+  `Dilutions`                 = meta$Dilutions,
+  `Maxpoint Ratio`            = mpr,
+  `Max Slope`                 = ms,
+  `Time-to-Threshold`         = ttt,
+  `Rate of Amyloid Formation` = 1 / ttt
+)
+```
+\newpage
+
+<!-- # Validation & Performance -->
 
 # Discussion
+The quicR package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
+By integrating key metrics such as time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS), quicR addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting complex fluorescence data.
+
+One of the primary strengths of quicR lies in its flexibility and user-centric design.
+The package leverages R’s powerful ecosystem, including the tidyverse and ggplot2, to streamline workflows and create high-quality, customizable visualizations.
+This ensures accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
+Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
+
+Despite these strengths, there are limitations to consider.
+Currently, quicR is tailored to data exported from the MARS software, which may limit its applicability to researchers using alternative fluorescence readers.
+Future iterations of the package could expand compatibility by incorporating functions to handle diverse data formats.
+Furthermore, while quicR includes robust visualization tools, users seeking highly specialized plots may require additional customization beyond the package’s default capabilities.
+
+Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
+quicR provides tools to calculate key metrics, but consensus on thresholds and interpretations remains a challenge for the field.
+Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling quicR to fully realize its potential as a diagnostic aid.
 
 # Conclusion
-quicR provides improved and standardized methods for analyzing RT-QuIC data.
+quicR offers a powerful solution for the analysis and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
+By enabling consistent data handling and interpretation, quicR lays the groundwork for improved diagnostic consistency and reproducibility.
+The package's open-source nature ensures that it will continue to evolve, integrating new insights and technologies as they emerge.
+
+As RT-QuIC technology advances, tools like quicR will play a pivotal role in bridging the gap between assay development and practical application.
+By equipping researchers with reliable, standardized tools, quicR not only supports the study of prion and protein misfolding disorders but also serves as a model for the development of software solutions in other diagnostic fields.
 

### 2025-01-14 man/manuscript/manuscript.qmd
Updated the devlopment section

@@
     fig-pos: "H"
-    keep-tex: true
+    # keep-tex: true
     template-partials: 
@@
 Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates [@Atarashi2011].
-The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Wilham2010; @Orru2012; @Bongianni2019; @Orru2017; @Orru2015; @Dassanayake2016; @Hwang2018; @Groveman2018; @Metrick2020].
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Wilham2010; @Orru2012; @Orru2017; @Orru2015; @Bongianni2019; @Dassanayake2016; @Hwang2018; @Groveman2018; @Metrick2020].
 The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies [@Fiorini2020; @Franceschini2017; @Picasso-Risso2022, @Holz2021].
@@
 
--   Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold [@Orru2015].
--   Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed [@Gallups2022].
--   Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities [@Rowden2023].
--   Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation [@Henderson2015].
+1.    Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold [@Orru2015].
+2.    Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed [@Gallups2022].
+3.    Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities [@Rowden2023].
+4.    Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation [@Henderson2015].
 
@@
 This package requires the following dependencies: dplyr, ggplot2, stringr, tidyr, janitor, openxlsx, readxl, reshape2, and slider.
-Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing downstream handling.
+Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing initial data handling.
 The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization [@tidyverse2019].
@@
 
-Finally, MS is determined by approximating the maximum of the derivative of the raw data and is typically reported in units of $\Delta$RFU/h (i.e.
+MS is determined by approximating the maximum of the derivative of the raw data and is typically reported in units of $\Delta$RFU/h (i.e.
 the change in relative fluorescent units per hour).
@@
 Now, the slopes are calculated using differences between two data points within the range of the sliding window.
-While this slightly reduces the accuracy of the approximation, it was decided that the improvement in computation time was worth the loss in accuracy.
+While this slightly reduces the accuracy of the approximation, the improvement in computation time exceeded the loss in accuracy.
 
@@
 
-quicR was developed to address the need for efficient data conversion and analysis of RT-QuIC data.
-The functions were designed with usability and reproducibility in mind, ensuring compatibility between multiple labs.
-Currently, the package accepts data exported from the proprietary MARS software (BMG Labtech, Ortenberg, Germany) as an Excel workbook.
+quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data.
+With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
+Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
+Design Philosophy
 
-This project was devloped using Git version control.
-GitHub workflows were utilized to ensure that the package is able to be installed on current operating systems.
-Additionally, tests were performed on each function using the testthat package [@testthat2011].
+The development of quicR was guided by three key principles:
 
-The functionality in this package revolves around data curation, metric calculations, and visualization.
+1.    Usability: The package features intuitive functions and a user-friendly interface that cater to both novice and experienced R users.
+2.    Reproducibility: quicR incorporates rigorous testing and version control to ensure consistent performance across operating systems and environments.
+3.    Flexibility: Recognizing the diverse needs of the RT-QuIC community, the package supports customizable workflows and outputs, allowing users to tailor analyses to their specific research goals.
+
+## Version Control and Collaboration
+
+The project was managed using Git for version control, enabling efficient tracking of changes and fostering collaborative development.
+The source code is hosted on GitHub, ensuring transparency and encouraging contributions from the research community.
+GitHub Actions were employed to automate testing and deployment workflows, verifying that the package remains compatible with current versions of R and its dependencies.
+
+## Testing and Validation
+Robust testing protocols were implemented to guarantee the reliability of quicR’s functionality.
+Each function was subjected to comprehensive unit testing using the testthat package [@testthat2011].
+These tests ensure that key metrics, data manipulation routines, and visualization tools perform as expected, even as the package evolves.
+
+## Core Functionalities
+The functionality of quicR is centered around three primary objectives:
+
+1.    Data Curation: Functions for importing, cleaning, and normalizing raw RT-QuIC data to streamline pre-processing.
+2.    Metric Calculations: Tools for deriving critical metrics, such as time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS), to enable standardized data interpretation.
+3.    Visualization: High-quality plotting capabilities powered by the ggplot2 library, enabling users to create publication-ready figures with minimal effort.
+
+## Continuous Development
+quicR is an ongoing project, with future updates planned to expand its functionality and improve its user experience. Planned enhancements include:
+
+-   Support for alternative data formats to broaden compatibility.
+-   Additional metrics and visualization options to meet the evolving needs of the RT-QuIC community.
+-   Integration with R Shiny for interactive data exploration.
+
+By combining rigorous development practices, a commitment to open science, and a focus on community-driven improvements, quicR serves as a foundational tool for advancing the analysis of RT-QuIC data.
 

### 2025-01-15 man/manuscript/manuscript.qmd
Updated manuscript

@@
 ## Input Formatting
-MARS exports data into Excel workbooks.
-For many of the quicR functions to work together, the workbooks must be formatted correctly.
-In MARS, select "Excel Report", and a pop-up window will appear (see [@fig-mars]).
+The FLUOstar® Omega series microplate readers (BMG Labtech, Ortenberg, Germany) are by far the most common readers used for RT-QuIC.
+As such, their analysis software, MARS, is integral to data input for this package.
+MARS exports data into Excel workbooks, and for many of the quicR functions to work together, the workbooks must be formatted correctly.
+In MARS, select "Excel Report", and a pop-up window ([@fig-mars]) will appear.
 The following options must be checked for proper output: "Microplate View", "Table view", "Transpose table", and "Add test run information".
+
+![Excel export settings in MARS. Ensure that "Microplate View", "Table view", "Transpose table", and "Add test run information" are selected.](images/MARS_settings.png){#fig-mars height=50%}
+
 After clicking "Export report to Excel", an Excel workbook is created such as in [@fig-marsoutput].
-
-![Excel export settings in MARS](images/MARS_settings.png){#fig-mars height=50%}
+This workbook will contain two sheets, the first with the microplate views and the second with the table view.
+The first sheet will have all of the relevant metadata while the second sheet will have all of the raw fluorescent data.
 
@@
 
-Excel spreadsheet exported from MARS.  
+Excel workbook exported from MARS.  
 :::
@@
 A graphical representation of these can be found in [@fig-metrics].
-There is no dedicated function for RAF since it can simply be expressed as the inverse of TtT, and can therefore be calculated separately as in [@tbl-metrics].
+There is no dedicated function for RAF since it can simply be expressed as the inverse of TtT, and can therefore be calculated separately as in the example in [@tbl-metrics].
 
@@
 This is done by choosing a cycle for background determination, and then dividing each read by that value.
-Once this is done, the MPR is taken as the max value.
+The MPR is taken as the max value of the normalized data.
 
@@
 Originally, this was accomplished by applying a linear regression to a sliding window; however, this proved to be very computationally expensive.
-Now, the slopes are calculated using differences between two data points within the range of the sliding window.
-While this slightly reduces the accuracy of the approximation, the improvement in computation time exceeded the loss in accuracy.
+Now, slopes are calculated using differences between two data points within the range of a sliding window.
+While this slightly reduces the accuracy of the approximation, the improvement in computation time exceeded the loss in resolution.
 
@@
 The red curve represents a raw data curve that has been normalized against background.
+The level has also been decreased by 1 to better show the relationship with the derivative.
 MPR is calculated as the maximum fluorescent value achieved in the normalized raw data.
@@
 The project was managed using Git for version control, enabling efficient tracking of changes and fostering collaborative development.
-The source code is hosted on GitHub, ensuring transparency and encouraging contributions from the research community.
+The source code is hosted on GitHub (https://github.com/gage1145/quicR), ensuring transparency and encouraging contributions from the research community.
 GitHub Actions were employed to automate testing and deployment workflows, verifying that the package remains compatible with current versions of R and its dependencies.
@@
 These tests ensure that key metrics, data manipulation routines, and visualization tools perform as expected, even as the package evolves.
+Each new build of quicR must pass these tests in order to be released.
 
@@
 Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling quicR to fully realize its potential as a diagnostic aid.
+Diagnostic determinations could easily be built into the library, but a larger consensus within the research community will need to be reached to warrant inclusion.
 
 # Conclusion
-quicR offers a powerful solution for the analysis and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
+quicR offers a powerful solution for the cleaning, analysis, and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
 By enabling consistent data handling and interpretation, quicR lays the groundwork for improved diagnostic consistency and reproducibility.
@@
 # Acknowledgments
+Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.
 

### 2025-01-21 man/manuscript/manuscript.qmd
Updated the manuscript.

@@
 The janitor package [@janitor2024] has data cleaning functions which were useful when importing data from Excel.
-The slider package provides tools which apply some function to a moving window which was crucial for determining the approximate derivative of raw data [@slider2024].
+The slider package [@slider2024] provides tools which apply some function to a moving window which was crucial for determining the approximate derivative of raw data.
 
@@
 -   Support for alternative data formats to broaden compatibility.
+-   Inclusion of analysis pipeline given popular research community methods.
 -   Additional metrics and visualization options to meet the evolving needs of the RT-QuIC community.
@@
 ```{r, eval=FALSE}
-#| label: tbl-transposed
-#| tbl-cap: Transposed raw data. This converted the data columns to rows and the rows to columns.
 get_real(file)[[1]] %>% transpose_real()
@@
 ```{r, echo=FALSE}
+#| label: tbl-transposed
+#| tbl-cap: Transposed raw data. This converted the data columns to rows and the rows to columns.
 columns <- 12
@@
 ```
-
 ```{r, echo=FALSE}
 #| label: tbl-metrics
-#| tbl-cap: Calculated metrics
+#| tbl-cap: Calculated metrics. Each row indicates an individual well. This table shows only the first 12 wells which correspond to the top row of the microplate.
 #| tbl-cap-location: top
@@
 #| fig-height: 8
+#| fig-cap: Plate-view analog of a 96-well microplate.
+Each facet in the 8$\times$12 grid shows the real-time curves of an RT-QuIC reaction.
+The numbers underneath the sample IDs are the dilution factors.
 sample_locations <- get_sample_locations(
@@
 
-<!-- # Validation & Performance -->
-
 # Discussion

### 2025-01-28 man/manuscript/manuscript.qmd
Updated manuscript

@@
 Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
-Design Philosophy
+
+## Design Philosophy
 
@@
   row_spec(0, bold = TRUE) %>%
-  kable_styling(full_width = TRUE, font_size = 8)
+  kable_styling(full_width = TRUE, font_size = 6.5)
 
@@
   row_spec(0, bold = TRUE) %>%
-  kable_styling(full_width = TRUE, font_size = 10)
+  kable_styling(full_width = TRUE, font_size = 6.5)
 ```
@@
 ```{r, eval=FALSE}
-df_norm <- get_real(file)[[1]] %>% normalize_RFU()
+df_norm <- get_real(file)[[1]] %>% 
+  normalize_RFU()
 
@@
   head(12) %>%
-  kable(row.names = FALSE, align = rep("c", ncol(df_analyzed)))
+  kable(row.names = FALSE, align = rep("c", ncol(df_analyzed))) %>%
+  row_spec(0, bold = TRUE)
 ```
@@
 #| fig-height: 8
-#| fig-cap: Plate-view analog of a 96-well microplate.
-Each facet in the 8$\times$12 grid shows the real-time curves of an RT-QuIC reaction.
-The numbers underneath the sample IDs are the dilution factors.
+#| fig-cap: Plate-view analog of a 96-well microplate. Each facet in the 8x12 grid shows the real-time curves of an RT-QuIC reaction. The numbers underneath the sample IDs are the dilution factors.
 sample_locations <- get_sample_locations(

### 2025-01-29 man/manuscript/manuscript.qmd
Updated manuscript

@@
 
-abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
-Given that the technology is still relatively new, academic and industry standards for cleaning data and analyzing results have yet to be fully established.
-The open source R library, quicR, was developed to fill this lack of standardization.
-This library provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
+abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become a valuable diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
+Given that the technology is relatively new, academic and industry standards for quality filtering data and high throughput analysis of results have yet to be fully established.
+The open source R library, quicR, was developed to provide a standradized approach to RT-QuIC data analysis.
+quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
 keywords: quicR, R, library, RT-QuIC, prion, diagnostics, CJD, Parkinson's
@@
   html: default
+crossref: 
+  fig-title: "**Figure**"
+  tbl-title: "**Table**"
 mainfont: Calibri
@@
 # Introduction
-Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ability to detect misfolded protein aggregates [@Atarashi2011].
+Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates [@Wilham2010; @Atarashi2011].
 The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed [@Wilham2010; @Orru2012; @Orru2017; @Orru2015; @Bongianni2019; @Dassanayake2016; @Hwang2018; @Groveman2018; @Metrick2020].
-The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies [@Fiorini2020; @Franceschini2017; @Picasso-Risso2022, @Holz2021].
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies [@Fiorini2020; @Franceschini2017; @Picasso-Risso2022; @Holz2021].
 However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation [@Rowden2023].
@@
 To address this gap, we introduce quicR, an open-source library, developed in R [@R2024], dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of seeded amplification assays.
+By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC [@Christenson2023] and Micro-QuIC [@Lee2024].
 quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
@@
 This package requires the following dependencies: dplyr, ggplot2, stringr, tidyr, janitor, openxlsx, readxl, reshape2, and slider.
-Because the MARS software (BMG Labtech, Ortenberg, Germany) exports data as an Excel workbook, the packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing initial data handling.
+The packages, openxlsx [@openxlsx2024] and readxl [@readxl2023], were fundamental to performing initial data handling of raw data Excel files.
 The tidyverse packages (dplyr, ggplot2, stringr, and tidyr), were vital for writing easy-to-read code and for data visualization [@tidyverse2019].
@@
 ## Key Metrics and Calculations
-quicR has functions for calculating TtT, MPR, and MS.
-A graphical representation of these can be found in [@fig-metrics].
-There is no dedicated function for RAF since it can simply be expressed as the inverse of TtT, and can therefore be calculated separately as in the example in [@tbl-metrics].
+quicR has functions for calculating TtT, MPR, and MS (vizualized in [@fig-metrics]).
+There is no dedicated function for RAF since it can be expressed as the inverse of TtT, and can therefore be calculated separately as in the example in [@tbl-metrics].
 
-TtT is calculated by iterating through each sample until a value is greater than the supplied threshold.
+TtT is calculated by iterating through each sample until a value is greater than the user-supplied threshold.
 It then determines the intersection between the previous and current read times and the threshold.
@@
 
-MPR is defined as the maximum fluorescence divided by the background fluorescence.
+MPR is defined as the maximum fluorescence divided by the background fluorescence [@Rowden2023].
 Thus, in order to calculate, the raw data must first be normalized against the background.
-This is done by choosing a cycle for background determination, and then dividing each read by that value.
+This is done by the user choosing a cycle for background determination, and then dividing each read by that value.
 The MPR is taken as the max value of the normalized data.
@@
 
-![Example graphs highlighting the different calculated metrics.
+![Example graph highlighting the calculated metrics described above.
 The red curve represents a raw data curve that has been normalized against background.
-The level has also been decreased by 1 to better show the relationship with the derivative.
-MPR is calculated as the maximum fluorescent value achieved in the normalized raw data.
-TtT is determined as the time required to cross a given threshold (in this example, the threshold is 0.2).
+The maxpoint ratio is calculated as the maximum fluorescent value achieved in the normalized raw data.
+Time-to-threshold is determined as the time required to cross a given threshold (in this example, the threshold is set at 0.2).
 The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.](images/metric_example.png){#fig-metrics}
@@
 Orange nodes are functions which calculate some metric.
-Finally, yellow nodes represent endpoints in the data analysis.](images/workflow2.png){#fig-workflow}
+Finally, yellow nodes represent data analysis endpoints.](images/workflow2.png){#fig-workflow}
 
-quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data.
+<!-- quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data.
 With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
 Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
+-->
 
-## Design Philosophy
+<!-- ## Design Philosophy -->
 
-The development of quicR was guided by three key principles:
+<!-- The development of quicR was guided by three key principles: -->
 
-1.    Usability: The package features intuitive functions and a user-friendly interface that cater to both novice and experienced R users.
-2.    Reproducibility: quicR incorporates rigorous testing and version control to ensure consistent performance across operating systems and environments.
-3.    Flexibility: Recognizing the diverse needs of the RT-QuIC community, the package supports customizable workflows and outputs, allowing users to tailor analyses to their specific research goals.
+<!-- 1.    Usability: The package features intuitive functions and a user-friendly interface that cater to both novice and experienced R users. -->
+<!-- 2.    Reproducibility: quicR incorporates rigorous testing and version control to ensure consistent performance across operating systems and environments. -->
+<!-- 3.
+Flexibility: Recognizing the diverse needs of the RT-QuIC community, the package supports customizable workflows and outputs, allowing users to tailor analyses to their specific research goals.
+-->
 
 ## Version Control and Collaboration
-
 The project was managed using Git for version control, enabling efficient tracking of changes and fostering collaborative development.
@@
 
-## Continuous Development
-quicR is an ongoing project, with future updates planned to expand its functionality and improve its user experience. Planned enhancements include:
+<!-- ## Continuous Development -->
+<!-- quicR is an ongoing project, with future updates planned to expand its functionality and improve its user experience. Planned enhancements include: -->
 
--   Support for alternative data formats to broaden compatibility.
--   Inclusion of analysis pipeline given popular research community methods.
--   Additional metrics and visualization options to meet the evolving needs of the RT-QuIC community.
--   Integration with R Shiny for interactive data exploration.
+<!-- -   Support for alternative data formats to broaden compatibility. -->
+<!-- -   Inclusion of analysis pipeline given popular research community methods. -->
+<!-- -   Additional metrics and visualization options to meet the evolving needs of the RT-QuIC community. -->
+<!-- -   Integration with R Shiny for interactive data exploration. -->
 
-By combining rigorous development practices, a commitment to open science, and a focus on community-driven improvements, quicR serves as a foundational tool for advancing the analysis of RT-QuIC data.
+<!-- By combining rigorous development practices, a commitment to open science, and a focus on community-driven improvements, quicR serves as a foundational tool for advancing the analysis of RT-QuIC data.
+-->
 
@@
 ```{r, eval=FALSE, message=FALSE}
-BMG_format(sample_file, write_file = TRUE)
+BMG_format(file, write_file = TRUE, save_path = "", save_name = "formatted.txt")
 ```
@@
 The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
-Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what will be most useful.
-Those tables are the "Sample IDs" and the "Dilutions" tables (if dilutions were included in the export).
-For much of the downstream analysis, it is crucial the the "Sample IDs" table was exported.
+Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what is most useful for downstream processes.
+Those tables include the "Sample IDs" and "Dilutions" tables (if dilutions were included in the MARS export).
+For much of the downstream analysis, it is crucial that the "Sample IDs" table was exported from MARS.
 If there is no table, the user can simply add it manually (see [@fig-sheet1] for proper formatting).
@@
 
-tabs$`Sample IDs` %>%
-  as.data.frame() %>%
-  rename() %>%
+tabs$`Sample IDs` |>
+  as.data.frame() |>
+  rename() |>
   kable(
@@
     align = rep("c", 12)
-  ) %>%
-  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) %>%
-  column_spec(13, border_right = TRUE) %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(full_width = TRUE, font_size = 6.5)
+  ) |>
+  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) |>
+  column_spec(13, border_right = TRUE) |>
+  row_spec(0, bold = TRUE) |>
+  kable_styling(full_width = TRUE, font_size = 10)
 
-tabs$Dilutions %>%
-  as.data.frame() %>%
-  rename() %>%
+tabs$Dilutions |>
+  as.data.frame() |>
+  rename() |>
   kable(
@@
     align = rep("c", 12)
-  ) %>%
-  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) %>%
-  column_spec(13, border_right = TRUE) %>%
-  row_spec(0, bold = TRUE) %>%
-  kable_styling(full_width = TRUE, font_size = 6.5)
+  ) |>
+  column_spec(1, border_left = TRUE, border_right = TRUE, bold = TRUE) |>
+  column_spec(13, border_right = TRUE) |>
+  row_spec(0, bold = TRUE) |>
+  kable_styling(full_width = TRUE, font_size = 10)
 ```
@@
 ```{r, eval=FALSE}
-organize_tables(file) %>% convert_tables()
+organize_tables(file) |> convert_tables()
 ```
@@
 tabs <- convert_tables(tabs)
-tabs %>% head(12) %>% kable(row.names = FALSE, align = c("c", "c"))
+tabs |> head(12) |> kable(row.names = FALSE, align = c("c", "c"))
 ```
@@
 The "get_sample_locations" function accepts additional arguments if dilution factors were exported from MARS.
+The "dilution_bool" argument can be set to TRUE if dilutions are to be included in the output.
 The "dilution_fun" argument will supply a function for transforming the dilution factors (e.g.
 if the user would want to perform a log transformation).
+The user can supply a delimiter using the "sep" function.
 The output of this function is critical as an argument in the "plate_view" function which is further explained in the visualization section.
@@
     -log10(x), 
-  sep = " "
+  sep = "_"
 )
@@
 Included in this is the dilution factor which has been transformed as the negative log of original dilution values.
-This table is important for input into the plate_view function.
+This table is important for input into the "plate_view" function.
 get_sample_locations(
   file, dilution_bool = TRUE, dilution_fun = function(x) -log10(x), sep = " "
-) %>%
-  head(12) %>%
+) |>
+  head(12) |>
   kable(row.names = FALSE, align = c("c", "c"))
@@
 #| tbl-cap: Metadata which is included in the header of the Excel file.
-get_meta(file) %>%
-  mutate_at("Meta_info", ~gsub("\\\\", "/", .)) %>%
+get_meta(file) |>
+  mutate_at("Meta_info", ~gsub("\\\\", "/", .)) |>
   kable(row.names = FALSE)
@@
 ## Retrieving and Manipulating Raw Data
-The raw, real-time data is typically found on the second sheet of the Excel workbook. There are three functions dedicated to the retrieval and cleaning of raw data.
-1.  get_real: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
-2.  transpose_real: Swaps the rows and columns which makes some downstream analyses easier.
-3.  normalize_RFU: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
+The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS. There are three functions dedicated to the retrieval and cleaning of raw data.
+
+1.  `get_real`: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
+2.  `transpose_real`: Swaps the rows and columns which makes some downstream analyses easier.
+3.  `normalize_RFU`: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
 
@@
 columns <- 8
-df_ <- get_real(file, ordered = FALSE)[[1]] %>% as.data.frame()
-df_[1:11, 1:columns] %>% kable(row.names = FALSE, align = rep("c", columns))
+df_ <- get_real(file, ordered = FALSE)[[1]] |> as.data.frame()
+df_[1:11, 1:columns] |> kable(row.names = FALSE, align = rep("c", columns))
 ```
@@
 ```{r, eval=FALSE}
-get_real(file)[[1]] %>% transpose_real()
+get_real(file)[[1]] |> transpose_real()
 ```
@@
 columns <- 12
-transpose_real(df_)[1:7, 1:columns] %>% 
+transpose_real(df_)[1:7, 1:columns] |> 
   kable(row.names = FALSE, align = rep("c", columns))
@@
 ```{r, eval=FALSE}
-get_real(file)[[1]] %>% normalize_RFU(transposed = FALSE)
+get_real(file)[[1]] |> normalize_RFU(transposed = FALSE)
 ```
@@
 
-df_norm <- df_norm %>%
+df_norm <- df_norm |>
   mutate(`Sample IDs` = tabs$`Sample IDs`)
@@
 Many publications have different methods of determining thresholds.
-By and large, the most popular method is to take the average background fluorescence of the entire plate and add some multiple of standard deviations.
+By convention, the most popular method is to take the average background fluorescence of the every well and add some multiple of standard deviations [@Rowden2023].
 The quicR package provides the "calculate_threshold" function for this purpose.
@@
 ```{r, eval=FALSE}
-get_real(file)[[1]] %>% 
+get_real(file)[[1]] |> 
   calculate_threshold(method = "stdev", multiplier = 10)
@@
 ```{r, eval=FALSE}
-df_norm <- get_real(file)[[1]] %>% 
+df_norm <- get_real(file)[[1]] |> 
   normalize_RFU()
 
-data.frame("Sample IDs" = tabs$`Sample IDs`) %>%
+data.frame("Sample IDs" = tabs$`Sample IDs`) |>
   mutate(
@@
 #| tbl-cap-location: top
-df_analyzed <- data.frame("Sample IDs" = tabs$`Sample IDs`, check.names = FALSE) %>%
+df_analyzed <- data.frame("Sample IDs" = tabs$`Sample IDs`, check.names = FALSE) |>
   mutate(
-    Dilutions = -log10(tabs$Dilutions %>% na.omit() %>% as.numeric()),
-    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE) %>% round(2),
-    MS = calculate_MS(df_norm, data_is_norm = TRUE) %>% round(3),
-    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3) %>% round(2),
-    RAF = (1 / TtT) %>% round(4)
+    Dilutions = -log10(tabs$Dilutions |> na.omit() |> as.numeric()),
+    MPR = calculate_MPR(df_norm, start_col = 3, data_is_norm = TRUE) |> round(2),
+    MS = calculate_MS(df_norm, data_is_norm = TRUE) |> round(3),
+    TtT = calculate_TtT(df_norm, threshold = 2, start_col = 3) |> round(2),
+    RAF = (1 / TtT) |> round(4)
   )
-df_analyzed%>%
-  head(12) %>%
-  kable(row.names = FALSE, align = rep("c", ncol(df_analyzed))) %>%
+df_analyzed|>
+  head(12) |>
+  kable(row.names = FALSE, align = rep("c", ncol(df_analyzed))) |>
   row_spec(0, bold = TRUE)
@@
 #| fig-height: 6.5
-df_analyzed %>%
-  melt(id.vars = c("Sample IDs", "Dilutions")) %>%
-  mutate_at("Dilutions", as.factor) %>%
+df_analyzed |>
+  melt(id.vars = c("Sample IDs", "Dilutions")) |>
+  mutate_at("Dilutions", as.factor) |>
 
@@
 Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.
+We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
+We would like to acknowledge Suzanne Stone and Sarah Gresch for maintaining lab operations.
+
+# Funding
+This work was funded through the Legislative-Citizen Commission on Minnesota Resources (LCCMR).
 
@@
 :::
+
+# Appendix

### 2025-01-30 R/calculate_MS.R
Fixed bug where calculate_MS would throw a warning if NAs were coerced.

@@ -36,9 +36,9 @@ calculate_MS <- function(data, window = 3, data_is_norm = TRUE) {
       t() %>%
       as.data.frame() %>%
       mutate_all(~ as.numeric(as.character(.))) %>%
+      mutate(Time = as.numeric(rownames(.))) %>%
       suppressWarnings() %>%
       na.omit() %>%
-      mutate(Time = as.numeric(rownames(.))) %>%
       relocate("Time", .before = 1)
   }
 

### 2025-01-30 R/convert_tables.R
Added a conditional argument to convert_tables to remove rows with NAs.

@@ -4,6 +4,7 @@
 #' and converts them into dataframe columns.
 #'
 #' @param tab A table/matrix or a list of tables/matrices.
+#' @param na_moit Logical; if true, will remove rows with NA.
 #'
 #' @return A dataframe column.
 #'
@@ -20,7 +21,7 @@
 #' convert_tables(tabs)
 #'
 #' @export
-convert_tables <- function(tab) {
+convert_tables <- function(tab, na_omit = TRUE) {
   df_list <- data.frame()
   if (is.vector(tab)) {
     for (i in 1:length(tab)) {
@@ -34,6 +35,7 @@ convert_tables <- function(tab) {
     }
     df_ <- as.data.frame(df_list)
     colnames(df_) <- names(tab)
+    if (na_omit) df_ <- na.omit(df_)
     return(df_)
   }
 }

### 2025-01-30 R/calculate_threshold.R
Import sd function from stats library.

@@ -8,6 +8,7 @@
 #' @param multiplier For some methods, will add a multiplier for more conservative thresholds.
 #'
 #' @importFrom dplyr select
+#' @importFrom stats sd
 #'
 #' @return A float value.
 #'

### 2025-01-30 R/convert_tables.R
Fixed typo in convert_tables.

@@ -4,7 +4,7 @@
 #' and converts them into dataframe columns.
 #'
 #' @param tab A table/matrix or a list of tables/matrices.
-#' @param na_moit Logical; if true, will remove rows with NA.
+#' @param na_omit Logical; if true, will remove rows with NA.
 #'
 #' @return A dataframe column.
 #'

### 2025-01-30 R/plate_view.R
Fixed note from R CMD Check that didn't like how I was assigning my variables.

@@ -40,6 +40,7 @@
 #'
 #' @export
 plate_view <- function(df, meta, plate = 96) {
+
   if (plate != 96 & plate != 384) {
     return("Invalid plate layout. Format should be either 96 or 384. ")
   }
@@ -98,14 +99,14 @@ plate_view <- function(df, meta, plate = 96) {
     separate("variable", c("Well", "ID"), "\\.", fill = "right") |>
     # Ensures that Time and observations are numeric.
     mutate(
-      "Time" = as.numeric(.data[["Time"]]),
-      "value" = as.numeric(.data[["value"]]),
-      "ID" = as.character(.data[["ID"]]),
-      "Well" = as.factor(.data[["Well"]])
+      Time  = as.numeric  (.data$Time),
+      value = as.numeric  (.data$value),
+      ID    = as.character(.data$ID),
+      Well  = as.factor   (.data$Well)
     ) |>
-    mutate(ID = replace_na(.data[["ID"]], "none")) |>
+    mutate(ID = replace_na(.data$ID, "none")) |>
     # Create the facet plot.
-    ggplot(aes(x = Time, y = value)) +
+    ggplot(aes(x = .data$Time, y = .data$value)) +
     geom_line() +
     labs(
       y = "RFU",
@@ -118,7 +119,7 @@ plate_view <- function(df, meta, plate = 96) {
       axis.text.x = element_blank(),
       axis.text.y = element_blank()
     ) +
-    facet_wrap(vars(Well),
+    facet_wrap(vars(.data$Well),
       nrow = ifelse(plate == 96, 8, 16),
       ncol = ifelse(plate == 96, 12, 24),
       labeller = ID_labeller

### 2025-02-06 man/manuscript/manuscript.qmd
Updated manuscript.

@@
 quicR has functions for calculating TtT, MPR, and MS (vizualized in [@fig-metrics]).
-There is no dedicated function for RAF since it can be expressed as the inverse of TtT, and can therefore be calculated separately as in the example in [@tbl-metrics].
+There is no dedicated function for RAF since it can be expressed as the inverse of TtT, and can therefore be calculated separately as in the example in the Calculations section.
 
@@
 the change in relative fluorescent units per hour).
-Originally, this was accomplished by applying a linear regression to a sliding window; however, this proved to be very computationally expensive.
-Now, slopes are calculated using differences between two data points within the range of a sliding window.
+Slopes are calculated using differences between two data points within the range of a sliding window.
 While this slightly reduces the accuracy of the approximation, the improvement in computation time exceeded the loss in resolution.
@@
 Time-to-threshold is determined as the time required to cross a given threshold (in this example, the threshold is set at 0.2).
-The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.](images/metric_example.png){#fig-metrics}
+The blue curve represents the approximate derivative of the raw data, and max slope is determined as the maximum of the derivative.](images/metric_example.png){#fig-metrics}
 
@@
   dilution_bool = TRUE, 
-  dilution_fun = function(x) 
-    -log10(x), 
+  dilution_fun = function(x) -log10(x), 
   sep = "_"
@@
 Additionally, since there can be more than one instance of real-time data (depending on if the user added some calculations in MARS), "get_real" returns a list of dataframes.
-Therefore, the output should be indexed to access the data frame of interest.
+Therefore, the output must be indexed to access the data frame of interest.
 ```{r, eval=FALSE}
@@
 There are three analytical metrics with dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
-The rate of amyloid formation does not have a designated function since it is simply the inverse of the time-to-threshold.
+The rate of amyloid formation does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
 Each function below accepts input from the "transpose_real" or the "normalize_RFU" functions.

### 2025-02-12 man/manuscript/softwareX_submission.tex
Initialized the submission manuscript for SoftwareX.

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%\usepackage{lineno}

\journal{SoftwareX}

\begin{document}
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Title (quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays)}

\author[label1,label2,label3]{Gage Rowden}
\author[label1,label2,label3]{Peter Larsen}
\address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, St. Paul, MN 55108, USA.}
\address[label2]{Minnesota Center for Prion Research and Outreach, University of Minnesota, St. Paul, MN 55108, USA.}
\address[label3]{Priogen Corp., St. Paul, MN 55114, USA.}

\begin{abstract}
Real-time quaking induced conversion (RT-QuIC) has quickly become a valuable diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is relatively new, academic and industry standards for quality filtering data and high throughput analysis of results have yet to be fully established. The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis. quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
R package \sep R library \sep RT-QuIC \sep prion \sep diagnostics \sep CJD \sep Parkinson's

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

% \linenumbers

\section*{Metadata}
\label{}
\textit{The ancillary data table~\ref{codeMetadata} is required for the sub-version of the codebase. Please replace the italicized text in the right column with the correct information about your current code and leave the left column untouched.}

\begin{table}[ht]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
\hline
C1 & Current code version & v2.1.0 \\
\hline
C2 & Permanent link to code/repository used for this code version & For example: \url{https://github.com/gage1145/quicR} \\
\hline
C3  & Permanent link to Reproducible Capsule & For example: \url{https://codeocean.com/capsule/0270963/tree/v1}\\
\hline
C4 & Legal Code License   & All software and code must be released under one of the pre-approved licenses listed in the \href{https://www.elsevier.com/journals/softwarex/2352-7110/guide-for-authors}{Guide for Authors}, such as Apache License, GNU General Public License (GPL) or MIT License. Write the name of the license you’ve chosen here. \\
\hline
C5 & Code versioning system used & git \\
\hline
C6 & Software code languages, tools, and services used & R \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual & For example: \url{https://github.com/gage1145/quicR/blob/main/man/manuscript/manuscript.pdf} \\
\hline
C9 & Support email for questions & rowde002@umn.edu\\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{codeMetadata} 
\end{table}

% \textit{Optionally, you can provide information about the current executable
% software version filling in the left column of
% Table~\ref{executabelMetadata}. Please leave the first column as it is.}

\begin{table}[ht]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & For example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & For example: \url{https://github.com/combogenomics/DuctApe/releases/tag/DuctApe-0.16.4} \\
\hline
S3  & Permanent link to Reproducible Capsule & \\
\hline
S4 & Legal Software License & List one of the approved licenses \\
\hline
S5 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S6 & Installation requirements \& dependencies & \\
\hline
S7 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: \url{http://mozart.github.io/documentation/} \\
\hline
S8 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{executabelMetadata} 
\end{table}

\section{Motivation and significance}
\textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}

\begin{itemize}
    \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
    \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
    \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
    \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
\end{itemize}

\section{Software description}

    Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}. The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}. The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies \cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}. However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation \cite{Rowden2023}.

    To address this gap, we introduce quicR, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data. By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}. quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.

    While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics. These include:

    \begin{enumerate}
        \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold \cite{Orru2015}.
        \item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed \cite{Gallups2022}.
        \item Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities \cite{Rowden2023}.
        \item Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation \cite{Henderson2015}.
    \end{enumerate}

    Together, these metrics enable researchers to characterize the kinetics of RT-QuIC reactions comprehensively, enhancing the rigor and reliability of diagnostic decisions.

    In addition to analytical tools, quicR provides flexible and customizable visualization capabilities. Leveraging the powerful ggplot2 library \cite{ggplot2016}, quicR enables users to generate high-quality, publication-ready figures. These visualizations can be further customized using the intuitive '+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.

    By combining standardized metrics, advanced visualization tools, and a commitment to open source science, quicR serves as a foundational resource for the growing RT-QuIC community. Its goal is to empower researchers to analyze and present their data with clarity, consistency, and cohesion.

\subsection{Software architecture}
    quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data. With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories. Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows. See Figure \ref{fig:workflow} for a detailed workflow.
    \begin{figure}[ht]
        \caption{Workflow hierarchy of the quicR package. Blue nodes indicate steps where BMG software is needed. Purple nodes indicate functions dedicated to handling metadata. Red nodes are functions that acquire and manipulate raw data. Orange nodes are functions which calculate some metric. Finally, yellow nodes represent data analysis endpoints.}
        \centering
        \includegraphics[width=\textwidth]{images/workflow2.png}
        \label{fig:workflow}
    \end{figure}

\subsection{Software functionalities}
\textit{  Present the major functionalities of the software.}

 \subsection{Sample code snippets analysis (optional)}

\section{Illustrative examples}

% \textit{Provide at least one illustrative example to demonstrate the major
% functions of your software/code.}

% \textit{\textbf{Optional}: you may include one explanatory  video or screencast that will appear next to your article, in the right hand side panel. Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 150MB maximum size, video is possible per article. Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second. Prior to submission please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification} . This tool will display your video exactly in the same way as it will appear on ScienceDirect. }

\section{Impact}
\textit{This is the main section of the article and reviewers will weight it appropriately.
Please indicate:}
\begin{itemize}
    \item \textit{Any new research questions that can be pursued as a result of your software.}
    \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
    \item \textit{Any ways in which your software has changed the daily practice of its users.}
    \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
    \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
    \end{itemize}
% \textit{Please note that points 1 and 2 are best demonstrated by
%   references to citable publications.}

\section{Conclusions}
    quicR offers a powerful solution for the cleaning, analysis, and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field. By enabling consistent data handling and interpretation, quicR lays the groundwork for improved diagnostic consistency and reproducibility. The package's open-source nature ensures that it will continue to evolve, integrating new insights and technologies as they emerge.

    As RT-QuIC technology advances, tools like quicR will play a pivotal role in bridging the gap between assay development and practical application. By equipping researchers with reliable, standardized tools, quicR not only supports the study of prion and protein misfolding disorders but also serves as a model for the development of software solutions in other diagnostic fields.

\section*{Acknowledgements}
\label{}
Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN. We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach. We would like to acknowledge Suzanne Stone and Sarah Gresch for maintaining lab operations.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-num} 
\bibliography{references.bib}

% \textit{If the software repository you used supplied a DOI or another
% Persistent IDentifier (PID), please add a reference for your software
% here. For more guidance on software citation, please see our guide for
% authors or \href{https://f1000research.com/articles/9-1257/v2}{this
%   article on the essentials of software citation by FORCE 11}, of
% which Elsevier is a member.}

% \large{\textbf{Reminder: Before you submit, please delete all 
% the instructions in this document, 
% including this paragraph. 
% Thank you!}}

\end{document}
\endinput
%%
%% End of file `SoftwareX_article_template.tex'.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2025-02-12 man/manuscript/softwareX_submission.tex
Updated softwareX submission files.

@@
 
-\title{Title (quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays)}
+\title{quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
 
-\author[label1,label2,label3]{Gage Rowden}
+\author[label1,label2,label3]{Gage Rowden\corref{cor}\fnref{email}}
+\ead{rowde002@umn.edu}
+\fntext[email]{}
+\cortext[cor]{}
 \author[label1,label2,label3]{Peter Larsen}
@@
 %% keywords here, in the form: keyword \sep keyword
-R package \sep R library \sep RT-QuIC \sep prion \sep diagnostics \sep CJD \sep Parkinson's
+R package \sep RT-QuIC \sep prion \sep diagnostics \sep CJD \sep Parkinson's
 
@@
 \hline
-C1 & Current code version & v2.1.0 \\
+C1 & Current code version & V2.1.0 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & For example: \url{https://github.com/gage1145/quicR} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
 \hline
-C3  & Permanent link to Reproducible Capsule & For example: \url{https://codeocean.com/capsule/0270963/tree/v1}\\
+C3  & Permanent link to Reproducible Capsule & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0}\\
 \hline
-C4 & Legal Code License   & All software and code must be released under one of the pre-approved licenses listed in the \href{https://www.elsevier.com/journals/softwarex/2352-7110/guide-for-authors}{Guide for Authors}, such as Apache License, GNU General Public License (GPL) or MIT License.
-Write the name of the license you’ve chosen here.
-\\
+C4 & Legal Code License   & GPL-3 \\
 \hline
@@
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & \\
+C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
 \hline
-C8 & If available Link to developer documentation/manual & For example: \url{https://github.com/gage1145/quicR/blob/main/man/manuscript/manuscript.pdf} \\
+C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf} \\
 \hline
@@
 \end{tabular}
-\caption{Code metadata (mandatory)}
+\caption{Code metadata}
 \label{codeMetadata} 
@@
 
-% \textit{Optionally, you can provide information about the current executable
-% software version filling in the left column of
-% Table~\ref{executabelMetadata}. Please leave the first column as it is.}
-
-\begin{table}[ht]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-\hline
-\textbf{Nr.} & \textbf{(Executable) software metadata description} & \textbf{Please fill in this column} \\
-\hline
-S1 & Current software version & For example 1.1, 2.4 etc. \\
-\hline
-S2 & Permanent link to executables of this version  & For example: \url{https://github.com/combogenomics/DuctApe/releases/tag/DuctApe-0.16.4} \\
-\hline
-S3  & Permanent link to Reproducible Capsule & \\
-\hline
-S4 & Legal Software License & List one of the approved licenses \\
-\hline
-S5 & Computing platforms/Operating Systems & For example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
-\hline
-S6 & Installation requirements \& dependencies & \\
-\hline
-S7 & If available, link to user manual - if formally published include a reference to the publication in the reference list & For example: \url{http://mozart.github.io/documentation/} \\
-\hline
-S8 & Support email for questions & \\
-\hline
-\end{tabular}
-\caption{Software metadata (optional)}
-\label{executabelMetadata} 
-\end{table}
-
 \section{Motivation and significance}
-\textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
-
-\begin{itemize}
-    \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
-    \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
-    \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
-    \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
-\end{itemize}
-
-\section{Software description}
-
     Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
@@
 
+\textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
+
+\begin{itemize}
+    \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
+    \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
+    \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
+    \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
+\end{itemize}
+
+\section{Software description}
     \subsection{Software architecture}

### 2025-02-12 man/manuscript/softwareX_submission.tex
Updated submission.

@@
 %% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
+%% \usepackage{amssymb}
 \usepackage{hyperref}
@@
 %% for the whole article with \linenumbers.
-%\usepackage{lineno}
+% \usepackage{lineno}
 
@@
 \begin{document}
+
 \renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
@@
 %% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
+%% use the tnotetext command for the associated footnote;
 %% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
+%% use the fntext command for the associated footnote;
 %% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
+%% use the cortext command for the associated footnote;
 %% use the ead command for the email address,
@@
 
-\author[label1,label2,label3]{Gage Rowden\corref{cor}\fnref{email}}
-\ead{rowde002@umn.edu}
-\fntext[email]{}
-\cortext[cor]{}
+\author[label1,label2,label3]{Gage Rowden\corref{cor}}
+\fntext[ ]{\textit{E-mail address: }rowde002@umn.edu}
+\cortext[cor]{Corresponding author.}
 \author[label1,label2,label3]{Peter Larsen}
-\address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, St. Paul, MN 55108, USA.}
-\address[label2]{Minnesota Center for Prion Research and Outreach, University of Minnesota, St. Paul, MN 55108, USA.}
-\address[label3]{Priogen Corp., St. Paul, MN 55114, USA.}
+\address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, USA.}
+\address[label2]{Minnesota Center for Prion Research and Outreach, University of Minnesota, USA.}
+\address[label3]{Priogen Corp., USA.}
 
@@
 \section*{Metadata}
-\label{}
-\textit{The ancillary data table~\ref{codeMetadata} is required for the sub-version of the codebase.
-Please replace the italicized text in the right column with the correct information about your current code and leave the left column untouched.}
 
 \begin{table}[ht]
+    \fontsize{9}{9}\selectfont
     \begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
@@
 Leveraging the powerful ggplot2 library \cite{ggplot2016}, quicR enables users to generate high-quality, publication-ready figures.
-These visualizations can be further customized using the intuitive '+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
+These visualizations can be further customized using the intuitive `+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
 
@@
 
-\textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
-
-\begin{itemize}
-    \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
-    \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
-    \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
-    \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
-\end{itemize}
+% \textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
+% 
+% \begin{itemize}
+%     \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
+%     \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
+%     \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
+%     \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
+% \end{itemize}
 
@@
 \section{Impact}
-\textit{This is the main section of the article and reviewers will weight it appropriately.
-Please indicate:}
-\begin{itemize}
-    \item \textit{Any new research questions that can be pursued as a result of your software.}
-    \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
-    \item \textit{Any ways in which your software has changed the daily practice of its users.}
-    \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
-    \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
-    \end{itemize}
+% \textit{This is the main section of the article and reviewers will weight it appropriately.
+% Please indicate:}
+% \begin{itemize}
+%     \item \textit{Any new research questions that can be pursued as a result of your software.}
+%     \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
+%     \item \textit{Any ways in which your software has changed the daily practice of its users.}
+%     \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
+%     \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
+%     \end{itemize}
 % \textit{Please note that points 1 and 2 are best demonstrated by

### 2025-02-13 man/manuscript/softwareX_submission.tex
Updated SoftwareX submission

@@
 % \usepackage{lineno}
+\usepackage{tabularray}
+\usepackage{float}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-R package \sep RT-QuIC \sep prion \sep diagnostics \sep CJD \sep Parkinson's
+R package \sep{} RT-QuIC \sep{} prion \sep{} diagnostics \sep{} CJD \sep{} Parkinson's
 
@@
         \hline
-        C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf} \\
+        C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
         \hline
@@
 \section{Motivation and significance}
-    Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
-The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
-The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies \cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
-However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation \cite{Rowden2023}.
+    Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates~\cite{Wilham2010, Atarashi2011}.
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed~\cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies~\cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
+However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation~\cite{Rowden2023}.
 
-    To address this gap, we introduce quicR, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}.
+    To address this gap, we introduce quicR, an open-source library, developed in R~\cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC~\cite{Christenson2023} and Micro-QuIC~\cite{Lee2024}.
 quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
@@
 \subsection{Software functionalities}
-\textit{  Present the major functionalities of the software.}
+    The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of real-time fluorescence data.
+This section provides a comprehensive guide to utilizing the package's key functionalities, detailing how to:
 
- \subsection{Sample code snippets analysis (optional)}
+    \begin{enumerate}
+        \item Format and input sample data into Omega control software (BMG Labtech, Ortenberg, Germany).
+        \item Extract, clean, and organize metadata and raw fluorescence data.
+        \item Apply transformations and normalization to raw data for downstream analysis.
+        \item Calculate critical analytical metrics, such as time-to-threshold (TtT), rate of amyloid formation (RAF), maxpoint ratio (MPR), and maximum slope (MS).
+    \end{enumerate}
 
+    These steps are designed to enhance reproducibility, minimize manual data handling, and enable seamless integration with the MARS software workflow.
+Through practical examples, this section illustrates how each function operates, along with expected input and output formats, ensuring clarity and ease of use for researchers.
+
+    \subsection{Input of Sample IDs into Omega Control Software}
+        The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+This file is uniquely formatted, and not easily reproduced manually.
+The function, ``BMG\_format'', allows for input of a CSV file containing the plate layout (see Table~\ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+The file can then be imported into the control software before running.
+        \begin{table}[h]
+            \caption{Example CSV file plate layout for input into the ``BMG\_format'' function.
+The top left corner should be cell ``A1'' in the CSV file.
+The top numbered row and the left-most lettered column should never be altered.\medskip}
+            \label{tbl:layout}
+            \begin{tblr}{
+                colspec = {|c|cccccccccccc|}, 
+                row{1} = {font=\bfseries}, 
+                column{1} = {font=\bfseries}, 
+                rowhead = 1
+            }
+                \hline
+                & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
+                \hline
+                A & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                B & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                C & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                D & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                E & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                F & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                G & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                H & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                \hline
+            \end{tblr}
+        \end{table}
+
+    % \subsection{Formatted Plate Layout for MARS input}
+    %     The function, "BMG_format", includes the logical argument "write_file".
+If TRUE, it will create a TXT file.
+The path can be given to the "save_path" argument, and the file name can be supplied to the "save_name" argument.
+The text file will be formatted as follows, and can be imported into MARS.
+
+    \subsection{Data Cleaning and Transformation}
+        The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
+Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what is most useful for downstream processes.
+Those tables include the ``Sample IDa'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
+For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually (see [@fig-sheet1] for proper formatting).
+
+        \subsubsection{Retrieving Metadata}
+            The metadata is defined as either sample-dependent or -independent.
+Sample-dependent metadata includes information such as sample IDs and dilution factors, whereas sample-independent metadata includes the date, time, reaction ID, etc.
+
+            The dependent metadata can be retrieved using the ``organize\_tables'' and ``convert\_tables'' functions.
+The former returns a list of tables, and the latter converts each table into a column in a single data frame.
+
+        \subsubsection{Sample Locations}
+            Samples locations can be extracted based on their well ID.\@ The ``get\_sample\_locations'' function accepts additional arguments if dilution factors were exported from MARS.\@ The ``dilution\_bool'' argument can be set to TRUE if dilutions are to be included in the output.
+The ``dilution\_fun'' argument will supply a function for transforming the dilution factors (e.g.\ if the user would want to perform a log transformation).
+The user can supply a delimiter using the ``sep'' argument.
+The output of this function is critical as an argument in the ``plate\_view'' function which is further explained in the visualization section.
+
+            % \subsubsection{Sample-Independent Metadata}
+    \subsection{Retrieving and Manipulating Raw Data}
+        The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS. There are three functions dedicated to the retrieval and cleaning of raw data.
+
+    \begin{enumerate}
+        \item \textbf{get\_real}: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
+        \item \textbf{transpose\_real}: Swaps the rows and columns which makes some downstream analyses easier.
+        \item \textbf{normalize\_RFU}: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
+    \end{enumerate}
+
+        \subsubsection{Retrieve Raw Data}
+            Raw data can be retrieved using the ``get\_real'' function.
+The logical argument, ``ordered'', indicates whether the user would prefer the columns to be ordered by well or by sample ID.\@ By default, it is FALSE which will order the data by well.
+This should almost always be the case for easier integration with other downstream functions.
+Additionally, since there can be more than one instance of real-time data (depending on if the user added some calculations in MARS), ``get\_real'' returns a list of dataframes.
+Therefore, the output must be indexed to access the data frame of interest.
+
+        \subsubsection{Transpose Raw Data}
+            This data is structured such that each sample is its own column (variable) and each row (observation) is a time point.
+While this format is technically correct, a transposed format is more ideal for some downstream manipulation.
+This operation is performed using the function, ``transpose\_real''.
+After transposition, each time point is an individual column (variable), and each sample is an individual row (observation).
+
+        \subsubsection{Normalize Raw Data}
+            The function ``normalize\_RFU'' will convert the raw data into a background normalized data set.
+The function includes two additional arguments, ``bg\_cycle'' (the cycle which will be used as the background fluorescence value) and ``transposed'' (if FALSE, will make a call to the ``transpose\_real'' function).
+Note that the fourth time point is all ``1's'' since this was designated the background cycle.
+
+    \subsection{Calculations}
+        There are three analytical metrics with dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
+The rate of amyloid formation does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+Each function below accepts input from the ``transpose\_real'' or the ``normalize\_RFU'' functions.
+See @tbl-metrics for an example of the output of these functions.
+
+        \subsubsection{Thresholds}
+            Many publications have different methods of determining thresholds.
+By convention, the most popular method is to take the average background fluorescence of the every well and add some multiple of standard deviations~\cite{Rowden2023}.
+The quicR package provides the ``calculate\_threshold'' function for this purpose.
+A value can be provided as the optional argument, ``multiplier'', which will be applied to the standard deviation.
+
+        \subsubsection{Time-to-threshold and Rate of Amyloid Formation}
+            TtT is calculated using the ``calculate\_TtT'' function.
+The function must be supplied a threshold; default value is 2 (i.e.\ twice the background fluorescence if the data is normalized).
+A starting column should also be given as an integer; default value is 3.
+This is essentially asking how many columns of metadata are included before the fluorescence reads begin.
+
+            TtT is calculated by iterating through each row and checking if a value is greater than the threshold.
+If the value is greater, the slope of the previous time-point to the current time-point is calculated, and the time intersection of the current read is returned.
+
+        \subsubsection{Maxpoint Ratio}
+            MPR is calculated by the ``calculate\_MPR'' function.
+Data must be normalized in order to derive this metric.
+In a normalized data set, the MPR is simply the maximum value achieved during the run.
+Raw data can be passed to this function, but the argument ``data\_is\_norm'', must be set to FALSE.\ This will pass the raw data to ``normalize\_RFU'' before calculating the MPR values.
+
+        \subsubsection{Maximum Slope}
+            MS is calculated by the ``calculate\_MS'' function.
+The function iterates through each row using a rolling window which can be adjusted (default value is 3).
+Given the window size, the slope is calculated based on change in fluorescence divided by the range of the window.
+The MS is simply the largest slope value recorded.
+The units are typically reported as $\Delta$RFU/h.
+
+    % \subsection{Sample code snippets analysis (optional)}
 \section{Illustrative examples}

### 2025-02-13 man/manuscript/softwareX_submission.tex
Update submission

@@
 \usepackage{float}
+\usepackage[T1]{fontenc}
+\usepackage{helvet}
+\renewcommand{\familydefault}{\sfdefault}
 
@@
 
-\title{quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
+\title{quicR:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
 
@@
 Given that the technology is relatively new, academic and industry standards for quality filtering data and high throughput analysis of results have yet to be fully established.
-The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis.
-quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
+The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis.\ quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
 \end{abstract}
@@
     \begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-        \hline
+        \hline{}
         \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
-        \hline
+        \hline{}
         C1 & Current code version & V2.1.0 \\
-        \hline
+        \hline{}
         C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
-        \hline
+        \hline{}
         C3  & Permanent link to Reproducible Capsule & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0}\\
-        \hline
+        \hline{}
         C4 & Legal Code License & GPL-3 \\
-        \hline
+        \hline{}
         C5 & Code versioning system used & git \\
-        \hline
+        \hline{}
         C6 & Software code languages, tools, and services used & R \\
-        \hline
+        \hline{}
         C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
-        \hline
+        \hline{}
         C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
-        \hline
+        \hline{}
         C9 & Support email for questions & rowde002@umn.edu\\
-        \hline
+        \hline{}
     \end{tabular}
@@
     \subsection{Software architecture}
-        quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data.
+        quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
 With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
-Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
-See Figure \ref{fig:workflow} for a detailed workflow.
+        % Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
         \begin{figure}[ht]
@@
 \subsection{Software functionalities}
-    The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of real-time fluorescence data.
+    The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of RT-QuIC data.
 This section provides a comprehensive guide to utilizing the package's key functionalities, detailing how to:
@@
         \item Format and input sample data into Omega control software (BMG Labtech, Ortenberg, Germany).
-        \item Extract, clean, and organize metadata and raw fluorescence data.
-        \item Apply transformations and normalization to raw data for downstream analysis.
+        \item Extract, clean, and organize metadata and raw data and apply transformations and normalization for downstream analysis.
         \item Calculate critical analytical metrics, such as time-to-threshold (TtT), rate of amyloid formation (RAF), maxpoint ratio (MPR), and maximum slope (MS).
+        \item Vizualize raw and analyzed data.
     \end{enumerate}
@@
 
-    \subsection{Input of Sample IDs into Omega Control Software}
-        The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+    \subsubsection{Input of Sample IDs into Omega Control Software}
+        \begin{enumerate}
+            \item \textbf{BMG\_format()}: The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
 This file is uniquely formatted, and not easily reproduced manually.
-The function, ``BMG\_format'', allows for input of a CSV file containing the plate layout (see Table~\ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+This function allows for input of a CSV file containing the plate layout (see Table~\ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
 The file can then be imported into the control software before running.
+        \end{enumerate}
+
         \begin{table}[h]
@@
 
-    \subsection{Data Cleaning and Transformation}
+    \subsubsection{Data Cleaning and Transformation}
         The MARS software (BMG Labtech, Ortenberg, Germany) exports real-time data as an Excel workbook.
@@
 
-        \subsubsection{Retrieving Metadata}
-            The metadata is defined as either sample-dependent or -independent.
+        \begin{enumerate}
+            \item \textbf{organize\_tables()}: returns a list of tables contained in the first sheet of the exported Excel sheet.
+These tables contain valuable metadata such as sample IDs, dilution factors, and microplate locations.
+            \item \textbf{convert\_tables()}: accepts the tables outputted from \textbf{organize\_tables} and converts them to columns in a dataframe.
+            \item \textbf{get\_sample\_locations()}: extracts the well locations for each sample.
+Output of this function is used as an argument for vizualizing a microplate-level view of real-time data.
+        \end{enumerate}
+            % The metadata is defined as either sample-dependent or -independent.
 Sample-dependent metadata includes information such as sample IDs and dilution factors, whereas sample-independent metadata includes the date, time, reaction ID, etc.
 
-            The dependent metadata can be retrieved using the ``organize\_tables'' and ``convert\_tables'' functions.
+            % The dependent metadata can be retrieved using the ``organize\_tables'' and ``convert\_tables'' functions.
 The former returns a list of tables, and the latter converts each table into a column in a single data frame.
 
-        \subsubsection{Sample Locations}
-            Samples locations can be extracted based on their well ID.\@ The ``get\_sample\_locations'' function accepts additional arguments if dilution factors were exported from MARS.\@ The ``dilution\_bool'' argument can be set to TRUE if dilutions are to be included in the output.
+        % \subsubsection{Sample Locations}
+        %     Samples locations can be extracted based on their well ID.\@ The ``get\_sample\_locations'' function accepts additional arguments if dilution factors were exported from MARS.\@ The ``dilution\_bool'' argument can be set to TRUE if dilutions are to be included in the output.
 The ``dilution\_fun'' argument will supply a function for transforming the dilution factors (e.g.\ if the user would want to perform a log transformation).
@@
     \begin{enumerate}
-        \item \textbf{get\_real}: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
-        \item \textbf{transpose\_real}: Swaps the rows and columns which makes some downstream analyses easier.
-        \item \textbf{normalize\_RFU}: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
+        \item \textbf{get\_real()}: Retrieves the raw data from the Excel file, and outputs it as a dataframe.
+        \item \textbf{transpose\_real()}: Swaps the rows and columns which makes some downstream analyses easier.
+        \item \textbf{normalize\_RFU()}: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
     \end{enumerate}
 
-        \subsubsection{Retrieve Raw Data}
-            Raw data can be retrieved using the ``get\_real'' function.
+        % \subsubsection{Retrieve Raw Data}
+        %     Raw data can be retrieved using the ``get\_real'' function.
 The logical argument, ``ordered'', indicates whether the user would prefer the columns to be ordered by well or by sample ID.\@ By default, it is FALSE which will order the data by well.
@@
 
-        \subsubsection{Transpose Raw Data}
-            This data is structured such that each sample is its own column (variable) and each row (observation) is a time point.
+        % \subsubsection{Transpose Raw Data}
+        %     This data is structured such that each sample is its own column (variable) and each row (observation) is a time point.
 While this format is technically correct, a transposed format is more ideal for some downstream manipulation.
@@
 
-        \subsubsection{Normalize Raw Data}
-            The function ``normalize\_RFU'' will convert the raw data into a background normalized data set.
+        % \subsubsection{Normalize Raw Data}
+        %     The function ``normalize\_RFU'' will convert the raw data into a background normalized data set.
 The function includes two additional arguments, ``bg\_cycle'' (the cycle which will be used as the background fluorescence value) and ``transposed'' (if FALSE, will make a call to the ``transpose\_real'' function).
@@
 Each function below accepts input from the ``transpose\_real'' or the ``normalize\_RFU'' functions.
-See @tbl-metrics for an example of the output of these functions.
+See Figure \ref{fig:metrics} for an example of the output of these functions.
 
-        \subsubsection{Thresholds}
-            Many publications have different methods of determining thresholds.
+        \begin{enumerate}
+            \item \textbf{calculate\_threhold()}: returns a value which is a given number of standard deviations above the average background fluorescence of the entire microplate.
+            % Many publications have different methods of determining thresholds.
 By convention, the most popular method is to take the average background fluorescence of the every well and add some multiple of standard deviations~\cite{Rowden2023}.
@@
 
-        \subsubsection{Time-to-threshold and Rate of Amyloid Formation}
-            TtT is calculated using the ``calculate\_TtT'' function.
+            \item \textbf{calculate\_TtT()}: takes the real-time data and calculates the time in hours needed to reach a given threshold value.
+            % TtT is calculated using the ``calculate\_TtT'' function.
 The function must be supplied a threshold; default value is 2 (i.e.\ twice the background fluorescence if the data is normalized).
@@
 
-            TtT is calculated by iterating through each row and checking if a value is greater than the threshold.
+            % TtT is calculated by iterating through each row and checking if a value is greater than the threshold.
 If the value is greater, the slope of the previous time-point to the current time-point is calculated, and the time intersection of the current read is returned.
 
-        \subsubsection{Maxpoint Ratio}
-            MPR is calculated by the ``calculate\_MPR'' function.
+            \item \textbf{calculate\_MPR()}: accepts raw or normalized data and returns the maximum value obtained during the run.
+If supplied with raw data, it will make a call to the normalize\_RFU() function.
+            % MPR is calculated by the ``calculate\_MPR'' function.
 Data must be normalized in order to derive this metric.
@@
 
-        \subsubsection{Maximum Slope}
-            MS is calculated by the ``calculate\_MS'' function.
+            \item \textbf{calculate\_MS()}: computes the approximate derivative of the real-time data and returns the maximum value obtained during the run.
+            % MS is calculated by the ``calculate\_MS'' function.
 The function iterates through each row using a rolling window which can be adjusted (default value is 3).
@@
 The units are typically reported as $\Delta$RFU/h.
+        \end{enumerate}
+
+        \begin{figure}[h]
+            \caption{}
+            \centering{}
+            \includegraphics[width=\textwidth]{images/metric_example.png}
+            \label{fig:metrics}
+        \end{figure}
+
+    \subsection{Vizualization}
 

### 2025-02-26 R/plot_metrics.R
Added \donttest to plot_metrics since the example takes >5 sec to test.

@@ -16,6 +16,8 @@
 #' @return A ggplot object
 #'
 #' @examples
+#' # This test takes >5 sec
+#' \donttest{
 #' file <- system.file(
 #'   "extdata/input_files",
 #'   file = "test4.xlsx",
@@ -30,6 +32,7 @@
 #'
 #' calculate_metrics(data, meta) |>
 #'   plot_metrics()
+#' }
 #'
 #' @export
 plot_metrics <- function(data, sample_col = "Sample IDs", fill = "Dilutions", dilution_bool = TRUE, nrow = 2, ncol = 2) {

### 2025-02-26 R/quicR.R
Updated the help topic file to use the newer "_PACKAGE" sentinel. The older version would cause a note in R CMD Check.

@@ -1,14 +1,12 @@
-#'  \code{quicR} package
-#'
+#'  @description
 #'  Data handling for real-time quaking induced conversion assays
 #'
 #'  See the README on
 #'  \href{https://cran.r-project.org/web/packages/quicR/index.html}{CRAN}
 #'  or \href{https://github.com/gage1145/quicR}{Github}
 #'
-#'  @docType package
-#'  @name quicR
-NULL
+#'  @keywords internal
+"_PACKAGE"
 
 ## quiets concerns of R CMD check re: the .'s that appear in pipelines
 if (getRversion() >= "2.15.1") utils::globalVariables(c("."))

### 2025-02-26 R/quicR.R
Removed the CRAN URL in quicR-package.Rd since it was causing a NOTE in the CRAN build.

@@ -1,9 +1,7 @@
 #'  @description
 #'  Data handling for real-time quaking induced conversion assays
 #'
-#'  See the README on
-#'  \href{https://cran.r-project.org/web/packages/quicR/index.html}{CRAN}
-#'  or \href{https://github.com/gage1145/quicR}{Github}
+#'  See the README on \href{https://github.com/gage1145/quicR}{Github}
 #'
 #'  @keywords internal
 "_PACKAGE"

### 2025-02-26 R/calculate_MS.R
Removed a delta symbol which was causing issues with R CMD CHECK

@@ -6,7 +6,7 @@
 #' @param window Integer designating how wide you want the sliding window to be for calculating the moving average slope.
 #' @param data_is_norm Logical; if FALSE, will make a call to normalize_RFU.
 #'
-#' @return A dataframe containing the real-time slope values as ΔRFU/sec.
+#' @return A dataframe containing the real-time slope values as change in RFU/sec.
 #'
 #' @importFrom slider slide_dbl
 #' @importFrom purrr map_dbl

### 2025-02-26 man/manuscript/plots.R
Added to the manuscript plots script to export boxplot and plate view.

@@ -71,4 +71,29 @@ ggsave("images/metric_example.png", width = 12, height = 6)
 
 
 
+# Boxplots ----------------------------------------------------------------
 
+
+
+file <- "../../inst/extdata/input_files/test4.xlsx"
+df_raw <- get_real(file)[[1]]
+df_norm <- normalize_RFU(df_raw)
+
+meta <- organize_tables(file) %>%
+  convert_tables()
+
+df_analyzed <- calculate_metrics(df_norm, meta) %>%
+  mutate(Dilutions = -log10(as.integer(Dilutions)))
+
+plot_metrics(df_analyzed)
+ggsave("images/boxplot.png", width = 12, height = 8)
+
+
+
+# Plate View --------------------------------------------------------------
+
+
+
+locations <- get_sample_locations(file)
+plate_view(df_raw, locations)
+ggsave("images/plate_view.png", width = 12, height = 8)

### 2025-02-26 man/manuscript/softwareX_submission.tex
Updated manuscript.

--- 2025-02-12 man/manuscript/softwareX_submission.tex
@@
 
-\documentclass[preprint,12pt, a4paper]{elsarticle}
+\documentclass[preprint,12pt,a4paper]{elsarticle}
 
@@
 % \usepackage{lineno}
+\usepackage{tabularray}
+\usepackage{float}
+\usepackage[T1]{fontenc}
+\usepackage{helvet}
+\renewcommand{\familydefault}{\sfdefault}
+\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
 
@@
 
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for the associated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for the associated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for the associated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{quicR: An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
-
+        \title{quicR:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
         \author[label1,label2,label3]{Gage Rowden\corref{cor}}
@@
         \begin{abstract}
-Real-time quaking induced conversion (RT-QuIC) has quickly become a valuable diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
+            Real-time quaking induced conversion (RT-QuIC) has become a valuable diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease.
 Given that the technology is relatively new, academic and industry standards for quality filtering data and high throughput analysis of results have yet to be fully established.
-The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis.
-quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and vizualization.
+The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis.\ quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and visualization.
         \end{abstract}
@@
         \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
-R package \sep RT-QuIC \sep prion \sep diagnostics \sep CJD \sep Parkinson's
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
+            R package \sep{} RT-QuIC \sep{} prion \sep{} diagnostics \sep{} CJD \sep{} Parkinson's
         \end{keyword}
@@
     \begin{table}[ht]
-    \fontsize{9}{9}\selectfont
-    \begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
-        \hline
+        \label{tbl:codeMetadata} 
+        \begin{tabular}{|l|p{6cm}|p{6cm}|}
+            \hline{}
             \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
-        \hline
+            \hline{}
             C1 & Current code version & V2.1.0 \\
-        \hline
+            \hline{}
             C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
-        \hline
-        C3  & Permanent link to Reproducible Capsule & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0}\\
-        \hline
+            \hline{}
+            C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
+            \hline{}
             C4 & Legal Code License & GPL-3 \\
-        \hline
-        C5 & Code versioning system used & git \\
-        \hline
+            \hline{}
+            C5 & Code versioning system used & Git \\
+            \hline{}
             C6 & Software code languages, tools, and services used & R \\
-        \hline
+            \hline{}
             C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
-        \hline
-        C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf} \\
-        \hline
+            \hline{}
+            C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
+            \hline{}
             C9 & Support email for questions & rowde002@umn.edu\\
-        \hline
+            \hline{}
         \end{tabular}
         \caption{Code metadata}
-\label{codeMetadata} 
     \end{table}
@@
 
-    While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics. These include:
+        While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics.
+These include:
 
@@
 
-    By combining standardized metrics, advanced visualization tools, and a commitment to open source science, quicR serves as a foundational resource for the growing RT-QuIC community.
-Its goal is to empower researchers to analyze and present their data with clarity, consistency, and cohesion.
+        By combining standardized metrics, advanced visualization tools, and a commitment to open source science, quicR serves as a foundational tool to empower researchers to analyze and present RT-QuIC data with clarity, consistency, and cohesion.
 
@@
         \subsection{Software architecture}
-        quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data.
+            quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
 With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
-Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
-See Figure \ref{fig:workflow} for a detailed workflow.
+            % Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
             \begin{figure}[ht]
+                \centering
+                \includegraphics[width=\textwidth]{images/workflow.png}
                 \caption{Workflow hierarchy of the quicR package.
@@
 Finally, yellow nodes represent data analysis endpoints.}
-            \centering
-            \includegraphics[width=\textwidth]{images/workflow2.png}
                 \label{fig:workflow}
@@
     \subsection{Software functionalities}
-\textit{  Present the major functionalities of the software.}
+        The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of RT-QuIC data.
+This section provides a comprehensive guide to utilizing the package's key functionalities, detailing how to:
 
- \subsection{Sample code snippets analysis (optional)}
+        \begin{enumerate}
+            \item Format and input sample data into Omega control software (BMG Labtech, Ortenberg, Germany).
+            \item Extract, clean, and organize metadata and raw data and apply transformations and normalization for downstream analysis.
+            \item Calculate critical analytical metrics, such as time-to-threshold (TtT), rate of amyloid formation (RAF), maxpoint ratio (MPR), and maximum slope (MS).
+            \item Visualize raw and analyzed data.
+        \end{enumerate}
 
+        These steps are designed to enhance reproducibility, minimize manual data handling, and enable seamless integration with the MARS software (BMG Labtech, Ortenberg, Germany) workflow.
+Through practical examples, this section illustrates how each function operates, along with expected input and output formats, ensuring clarity and ease of use for researchers.
+
+        \subsubsection{Input of Sample IDs into Omega Control Software}
+            \begin{enumerate}
+                \item \textbf{BMG\_format()}: The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+This file is uniquely formatted, and not easily reproduced manually.
+This function allows for input of a CSV file containing the plate layout (see Table \ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+The file can then be imported into the control software before running.
+            \end{enumerate}
+
+            \begin{table}[ht]
+                \centering
+                \label{tbl:layout}
+                \begin{tblr}{
+                    cells     = {font = \fontsize{11pt}{11pt}\selectfont},
+                    colspec   = {|c|cccccccccccc|}, 
+                    row{1}    = {font=\bfseries}, 
+                    column{1} = {font=\bfseries}, 
+                    rowhead   = 1,
+                    width     = \textwidth
+                }
+                    \hline
+                    & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\ 
+                    \hline
+                    A & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    B & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    C & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    D & P & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    E & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    F & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    G & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    H & N & S01 & S02 & S03 & S04 & S05 & S06 & S07 & S08 & S09 & S10 & S11 \\ 
+                    \hline
+                \end{tblr}
+                \caption{Example CSV file plate layout for input into the ``BMG\_format'' function.
+The top left corner should be cell ``A1'' in the CSV file.
+The top numbered row and the left-most lettered column should never be altered.}
+            \end{table}
+
+        \subsubsection{Data Cleaning and Transformation}
+            The MARS software exports real-time data as an Excel workbook.
+Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what is most useful for downstream processes.
+Those tables include the ``Sample IDa'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
+For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually (see [@fig-sheet1] for proper formatting).
+
+            \begin{enumerate}
+                \item \textbf{organize\_tables()}: returns a list of tables contained in the first sheet of the exported Excel sheet.
+These tables contain valuable metadata such as sample IDs, dilution factors, and microplate locations.
+                \item \textbf{convert\_tables()}: accepts tables outputted from \textbf{organize\_tables} and converts them to columns in a data frame.
+                \item \textbf{get\_sample\_locations()}: extracts the well locations for each sample.
+Output of this function is used as an argument for visualizing a microplate-level view of real-time data.
+            \end{enumerate}
+
+        \subsubsection{Retrieving and Manipulating Raw Data}
+            The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS. There are three functions dedicated to the retrieval and cleaning of raw data.
+
+            \begin{enumerate}
+                \item \textbf{get\_real()}: Retrieves the raw data from the Excel file, and outputs it as a data frame.
+                \item \textbf{transpose\_real()}: Swaps the rows and columns which makes some downstream analyses easier.
+                \item \textbf{normalize\_RFU()}: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
+            \end{enumerate}
+
+        \subsubsection{Calculations}
+            Three analytical metrics have dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
+The rate of amyloid formation does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+Each function below accepts input from the transpose\_real() or the normalize\_RFU() functions.
+See Figure \ref{fig:metrics} for an example of the output of these functions.
+
+            \begin{enumerate}
+                \item \textbf{calculate\_threhold()}: returns a value which is a given number of standard deviations above the average background fluorescence of the entire microplate.
+                \item \textbf{calculate\_TtT()}: takes the real-time data and calculates the time in hours needed to reach a given threshold value.
+                \item \textbf{calculate\_MPR()}: accepts raw or normalized data and returns the maximum value obtained during the run.
+If supplied with raw data, it will make a call to the normalize\_RFU() function.
+                \item \textbf{calculate\_MS()}: computes the approximate derivative of the real-time data and returns the maximum value obtained during the run.
+            \end{enumerate}
+
+            \begin{figure}[ht]
+                \centering{}
+                \includegraphics[width=\textwidth]{images/metric_example.png}
+                \caption{Example graph highlighting the calculated metrics described above.
+The red curve represents a raw data curve that has been normalized against background.
+The maxpoint ratio is calculated as the maximum fluorescent value achieved in the normalized raw data.
+Time‐to‐threshold is determined as the time required to cross a given threshold (in this example, the threshold is set at 0.2).
+The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.}
+                \label{fig:metrics}
+            \end{figure}
+
+        \subsubsection{Visualization}
+            The ensuing goal of this package is visualizing RT-QuIC data.
+While there are many ways to represent this data, quicR includes two functions which provide a quick assessment of the reactions.
+            \begin{enumerate}
+                \item \textbf{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
+Makes an 8$\times$12 or 16$\times$24 faceted plot depending on if the plate has 96 or 384 wells.
+Each facet shows the real-time data of each well.
+                \item \textbf{plot\_metrics()}: generates a boxplot of each sample's MPR, MS, RAF, and TtT.
+            \end{enumerate}
+
+        % \subsection{Sample code snippets analysis (optional)}
     \section{Illustrative examples}
@@
 }
+        To demonstrate the utility of quicR, we used a typical RT-QuIC run performed on a 96-well plate.
+The reaction was performed on a FLUOstar Omega plate reader (BMG Labtech, Ortenberg, Germany).
+The file was exported as an Excel worksheet where the metadata appears on the first sheet and the raw data on the second sheet.
+
+        \subsection{Example Code}
+            \# Step 1: Identify the raw file.\\
+            file <- "example.xlsx"\\
+
+            \# Step 2: Extract the raw data.\\
+            raw <- get\_real(file)[[1]]\\
+
+            \# Step 3: Normalize the data against the background.\\
+            normal <- normalize\_RFU(raw, transposed = FALSE)\\
+
+            \# Step 4: Extract the metadata.\\
+            meta <- file |> organize\_tables() |> convert\_tables()\\
+
+            \# Step 5: Get sample locations.\\
+            locations <- get\_sample\_locations(file)\\
+
+            \# Step 6: Create the analyzed data frame.\\
+            analyzed <- calculate\_metrics(normal, meta, dilution\_bool = TRUE)\\
+
+            \# Step 7: Plot the analyzed data frame.\\
+            plot\_metrics(analyzed)\\
+
+            \# Step 8: Plot the plate view.\\
+            plate\_view(raw, locations)\\
+
+            Once the file name is identified, the function get\_real() is used to extract the raw data.
+This data is imported as a data frame with each sample designated as an individual column and the first column designated as time.
+Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to the normalize\_RFU() function.
+This function accepts an integer as an argument for the desired cycle to be selected for background measurement.
+Next, the metadata is extracted using the organize\_tables() and convert\_tables() functions.
+These take the metadata found on the first sheet of the Excel file and convert them into data frame columns.
+Finally, metrics are calculated and assigned to their given sample ID using calculate\_metrics().
+This generates a data frame with sample IDs, dilution factors (if chosen), MPR's, MS's, RAF's, and TtT's.
+
+            Once the proper variables have been defined, they can be used as input in the visualization functions.
+The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as \ref{fig:boxplot}.
+Additionally, the raw data and sample locations are used to plot the plate view as in \ref{fig:plateview}.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[width=\textwidth]{images/boxplot.png}
+                \caption{Boxplot of the four metrics calculated in the quicR package.}
+                \label{fig:boxplot}
+            \end{figure}
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[width=\textwidth]{images/plate_view.png}
+                \caption{Plate view of RT-QuIC. Wells are identified with a sample ID and dilution factor separated by an optional delimiter (in this case, a whitespace).}
+                \label{fig:plateview}
+            \end{figure}
 
     \section{Impact}
-% \textit{This is the main section of the article and reviewers will weight it appropriately.
-% Please indicate:}
-% \begin{itemize}
-%     \item \textit{Any new research questions that can be pursued as a result of your software.}
-%     \item \textit{In what way, and to what extent, your software improves the pursuit of existing research questions.}
-%     \item \textit{Any ways in which your software has changed the daily practice of its users.}
-%     \item \textit{How widespread the use of the software is within and outside the intended user group (downloads, number of users if your software is a service, citable publications, etc.).}
-%     \item \textit{How the software is being used in commercial settings and/or how it has led to the creation of spin-off companies.}
-%     \end{itemize}
-% \textit{Please note that points 1 and 2 are best demonstrated by
-%   references to citable publications.}
+
+        The quicR package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
+By integrating key metrics such as time-to-threshold (TtT) \cite{Orru2015}, maxpoint ratio (MPR) \cite{Rowden2023}, and maximum slope (MS) \cite{Henderson2015}, quicR addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
+
+        One of the primary strengths of quicR lies in its flexibility and user-centric design.
+The package leverages R’s powerful ecosystem, including the tidyverse and ggplot2, to streamline workflows and create high-quality, customizable visualizations.
+This ensures accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
+Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
+
+        Despite these strengths, there are limitations to consider.
+Currently, quicR is tailored to data exported from the MARS software, which may limit its applicability to researchers using alternative microplate readers.
+Future iterations of the package could expand compatibility by incorporating functions to handle diverse data formats.
+Furthermore, while quicR includes robust visualization tools, users seeking highly specialized plots may require additional customization beyond the package’s default capabilities.
+
+        Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
+quicR provides tools to calculate key metrics, but consensus on thresholds and interpretations remains a challenge for the field \cite{Rowden2023}.
+Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling quicR to fully realize its potential as a diagnostic aid.
+Diagnostic determinations could easily be built into the library, but a larger consensus within the research community will need to be reached to warrant inclusion.
 
@@
     \section*{Acknowledgements}
-\label{}
         Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.
@@
 
-% \textit{If the software repository you used supplied a DOI or another
-% Persistent IDentifier (PID), please add a reference for your software
-% here. For more guidance on software citation, please see our guide for
-% authors or \href{https://f1000research.com/articles/9-1257/v2}{this
-%   article on the essentials of software citation by FORCE 11}, of
-% which Elsevier is a member.}
-
-% \large{\textbf{Reminder: Before you submit, please delete all 
-% the instructions in this document, 
-% including this paragraph. 
-% Thank you!}}
+    \textit{If the software repository you used supplied a DOI or another
+    Persistent IDentifier (PID), please add a reference for your software
+    here. For more guidance on software citation, please see our guide for
+    authors or \href{https://f1000research.com/articles/9-1257/v2}{this
+      article on the essentials of software citation by FORCE 11}, of
+    which Elsevier is a member.}
 

### 2025-02-26 man/manuscript/softwareX_submission.tex
Updated manuscript.

@@
 With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
-            % Its primary input format is data exported as Excel workbooks from the proprietary MARS software (BMG Labtech, Ortenberg, Germany), providing seamless integration with existing experimental workflows.
+The overall architecture revolves around integration with the proprietary MARS software (BMG Labtech, Ortenberg, Germany) which exports raw data as Excel workbooks.
+The data from these workbooks is then curated into usable objects in the R environment, and visualized.
+
             \begin{figure}[ht]
@@
             \item Format and input sample data into Omega control software (BMG Labtech, Ortenberg, Germany).
-            \item Extract, clean, and organize metadata and raw data and apply transformations and normalization for downstream analysis.
+            \item Extract, clean, and organize metadata and raw data and apply transformations/normalization for downstream analysis.
             \item Calculate critical analytical metrics, such as time-to-threshold (TtT), rate of amyloid formation (RAF), maxpoint ratio (MPR), and maximum slope (MS).
@@
 
-        These steps are designed to enhance reproducibility, minimize manual data handling, and enable seamless integration with the MARS software (BMG Labtech, Ortenberg, Germany) workflow.
-Through practical examples, this section illustrates how each function operates, along with expected input and output formats, ensuring clarity and ease of use for researchers.
+        These steps are designed to enhance reproducibility, minimize manual data handling, and enable seamless integration with the MARS software workflow.
 
         \subsubsection{Input of Sample IDs into Omega Control Software}
+            The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
+This file is uniquely formatted, and not easily reproduced manually.
+
             \begin{enumerate}
-                \item \textbf{BMG\_format()}: The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
-This file is uniquely formatted, and not easily reproduced manually.
-This function allows for input of a CSV file containing the plate layout (see Table \ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
-The file can then be imported into the control software before running.
+                \item \textbf{BMG\_format()}: This function allows for input of a CSV file containing the plate layout (see Table \ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+The file can then be imported into the Omega control software before running.
             \end{enumerate}
@@
                 \centering
-                \label{tbl:layout}
                 \begin{tblr}{
@@
 The top numbered row and the left-most lettered column should never be altered.}
+                \label{tbl:layout}
             \end{table}
@@
 Typically, the first sheet in the workbook will include microplate views of both raw data and metadata; however, the metadata on this page is what is most useful for downstream processes.
-Those tables include the ``Sample IDa'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
-For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually (see [@fig-sheet1] for proper formatting).
+Those tables include the ``Sample IDs'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
+For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually.
 
@@
             Three analytical metrics have dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
-The rate of amyloid formation does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+The rate of amyloid formation (RAF) does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+However, it can be calculated using the calculate\_metrics() function if TtT is chosen as an optional parameter.
 Each function below accepts input from the transpose\_real() or the normalize\_RFU() functions.
@@
                 \item \textbf{calculate\_MS()}: computes the approximate derivative of the real-time data and returns the maximum value obtained during the run.
+                \item \textbf{calculate\_metrics()}: makes a call to functions 2--4 above and generates a data frame with the sample-matched metrics. Also computes RAF if TtT is given as an argument.
             \end{enumerate}
@@
 Each facet shows the real-time data of each well.
-                \item \textbf{plot\_metrics()}: generates a boxplot of each sample's MPR, MS, RAF, and TtT.
+                \item \textbf{plot\_metrics()}: requires the output of calculate\_metrics() and generates a boxplot of each sample's MPR, MS, RAF, and TtT.
             \end{enumerate}
 
-        % \subsection{Sample code snippets analysis (optional)}
     \section{Illustrative examples}
-
-    % \textit{Provide at least one illustrative example to demonstrate the major
-    % functions of your software/code.}
-
-    % \textit{\textbf{Optional}: you may include one explanatory  video or screencast that will appear next to your article, in the right hand side panel.
-Please upload any video as a single supplementary file with your article.
-Only one MP4 formatted, with 150MB maximum size, video is possible per article.
-Recommended video dimensions are 640 x 480 at a maximum of 30 frames / second.
-Prior to submission please test and validate your .mp4 file at  \url{http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification} .
-This tool will display your video exactly in the same way as it will appear on ScienceDirect.
-}
         To demonstrate the utility of quicR, we used a typical RT-QuIC run performed on a 96-well plate.
 The reaction was performed on a FLUOstar Omega plate reader (BMG Labtech, Ortenberg, Germany).
-The file was exported as an Excel worksheet where the metadata appears on the first sheet and the raw data on the second sheet.
+The file was exported as an Excel workbook where the metadata appears on the first sheet and the raw data on the second.
 
@@
 This function accepts an integer as an argument for the desired cycle to be selected for background measurement.
+
             Next, the metadata is extracted using the organize\_tables() and convert\_tables() functions.
@@
             Once the proper variables have been defined, they can be used as input in the visualization functions.
-The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as \ref{fig:boxplot}.
-Additionally, the raw data and sample locations are used to plot the plate view as in \ref{fig:plateview}.
+The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as Figure \ref{fig:boxplot}.
+Additionally, the raw data and sample locations are used to plot the plate view as in Figure \ref{fig:plateview}.
 
@@
         One of the primary strengths of quicR lies in its flexibility and user-centric design.
-The package leverages R’s powerful ecosystem, including the tidyverse and ggplot2, to streamline workflows and create high-quality, customizable visualizations.
+The package leverages R’s powerful ecosystem and the tidyverse to streamline workflows and create high-quality, customizable visualizations.
 This ensures accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
@@
 Future iterations of the package could expand compatibility by incorporating functions to handle diverse data formats.
-Furthermore, while quicR includes robust visualization tools, users seeking highly specialized plots may require additional customization beyond the package’s default capabilities.
+Furthermore, while quicR includes robust visualization tools, users seeking highly specialized plots like those made by Li, et al.\cite{Li2025} may require additional customization beyond the package’s default capabilities.
 

### 2025-02-27 man/manuscript/manuscript.qmd
Updated the Quarto file to include the calculate_metrics() function.

@@
 
-# Calculate Key Metrics ---------------------------------------------------
-
-mpr <- calculate_MPR(normal, data_is_norm = TRUE)
-ms  <- calculate_MS(normal, data_is_norm = TRUE)
-ttt <- calculate_TtT(normal, threshold = 2)
-
-analyzed <- data.frame(
-  `Sample IDs`                = meta$`Sample IDs`,
-  `Dilutions`                 = meta$Dilutions,
-  `Maxpoint Ratio`            = mpr,
-  `Max Slope`                 = ms,
-  `Time-to-Threshold`         = ttt,
-  `Rate of Amyloid Formation` = 1 / ttt
-)
+analyzed <- calculate_metrics(normal, meta)
 ```

### 2025-02-27 man/manuscript/plots.R
Changed the file in the plots script to use file test5.xlsx.

@@ -75,17 +75,17 @@ ggsave("images/metric_example.png", width = 12, height = 6)
 
 
 
-file <- "../../inst/extdata/input_files/test4.xlsx"
+file <- "../../inst/extdata/input_files/test5.xlsx"
 df_raw <- get_real(file)[[1]]
 df_norm <- normalize_RFU(df_raw)
 
 meta <- organize_tables(file) %>%
   convert_tables()
 
-df_analyzed <- calculate_metrics(df_norm, meta) %>%
-  mutate(Dilutions = -log10(as.integer(Dilutions)))
+df_analyzed <- calculate_metrics(df_norm, meta)
 
-plot_metrics(df_analyzed)
+plot_metrics(df_analyzed) +
+  guides(fill = guide_legend(nrow = 1))
 ggsave("images/boxplot.png", width = 12, height = 8)
 
 
@@ -94,6 +94,6 @@ ggsave("images/boxplot.png", width = 12, height = 8)
 
 
 
-locations <- get_sample_locations(file)
+locations <- get_sample_locations(file, dilution_bool = TRUE, sep = " ")
 plate_view(df_raw, locations)
 ggsave("images/plate_view.png", width = 12, height = 8)

### 2025-02-27 man/manuscript/softwareX_submission.tex
Updated the manuscript.

@@
 \usepackage[T1]{fontenc}
-\usepackage{helvet}
+% \usepackage{helvet}
 \renewcommand{\familydefault}{\sfdefault}
@@
 
-        \title{quicR:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
+        \title{\textbf{quicR}:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
         \author[label1,label2,label3]{Gage Rowden\corref{cor}}
@@
 Given that the technology is relatively new, academic and industry standards for quality filtering data and high throughput analysis of results have yet to be fully established.
-The open source R library, quicR, was developed to provide a standardized approach to RT-QuIC data analysis.\ quicR provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and visualization.
+The open source R library, \textbf{quicR}, was developed to provide a standardized approach to RT-QuIC data analysis.\ \textbf{quicR} provides functions, which can be easily integrated into existing R workflows, for data curation, analysis, and visualization.
         \end{abstract}
@@
     \begin{table}[ht]
-        \label{tbl:codeMetadata} 
-        \begin{tabular}{|l|p{6cm}|p{6cm}|}
+        \fontsize{9pt}{9pt}\selectfont
+        \centering
+        \begin{tabular}{lp{6cm}p{6cm}}
             \hline{}
@@
             C1 & Current code version & V2.1.0 \\
-            \hline{}
-            C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR} \\
-            \hline{}
+            % \hline{}
+            C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0} \\
+            % \hline{}
             C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
-            \hline{}
+            % \hline{}
             C4 & Legal Code License & GPL-3 \\
-            \hline{}
+            % \hline{}
             C5 & Code versioning system used & Git \\
-            \hline{}
+            % \hline{}
             C6 & Software code languages, tools, and services used & R \\
-            \hline{}
+            % \hline{}
             C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
-            \hline{}
+            % \hline{}
             C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
-            \hline{}
+            % \hline{}
             C9 & Support email for questions & rowde002@umn.edu\\
@@
         \end{tabular}
-        \caption{Code metadata}
     \end{table}
@@
 
-        To address this gap, we introduce quicR, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, quicR aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}.
-quicR is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
+        To address this gap, we introduce \textbf{quicR}, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, \textbf{quicR} aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}.
+\textbf{quicR} is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
 
@@
 
-        In addition to analytical tools, quicR provides flexible and customizable visualization capabilities.
-Leveraging the powerful ggplot2 library \cite{ggplot2016}, quicR enables users to generate high-quality, publication-ready figures.
+        In addition to analytical tools, \textbf{quicR} provides flexible and customizable visualization capabilities.
+Leveraging the powerful ggplot2 library \cite{ggplot2016}, \textbf{quicR} enables users to generate high-quality, publication-ready figures.
 These visualizations can be further customized using the intuitive `+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
 
-        By combining standardized metrics, advanced visualization tools, and a commitment to open source science, quicR serves as a foundational tool to empower researchers to analyze and present RT-QuIC data with clarity, consistency, and cohesion.
-
-    % \textit{In this section, we want you to introduce the scientific background and the motivation for developing the software.}
-    % 
-    % \begin{itemize}
-    %     \item \textit{Explain why the software is important and describe the exact (scientific) problem(s) it solves.}
-    %     \item \textit{Indicate in what way the software has contributed (or will contribute in the future) to the process of scientific discovery; if available, please cite a research paper using the software.}
-    %     \item \textit{Provide a description of the experimental setting. (How does the user use the software?)}
-    %     \item \textit{Introduce related work in literature (cite or list algorithms used, other software etc.).}
-    % \end{itemize}
+        By combining standardized metrics, advanced visualization tools, and a commitment to open source science, \textbf{quicR} serves as a foundational tool to empower researchers to analyze and present RT-QuIC data with clarity, consistency, and cohesion.
 
@@
         \subsection{Software architecture}
-            quicR was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
+            \textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
 With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
@@
                 \includegraphics[width=\textwidth]{images/workflow.png}
-                \caption{Workflow hierarchy of the quicR package.
+                \caption{Workflow hierarchy of the \textbf{quicR} package.
 Blue nodes indicate steps where BMG software is needed.
@@
     \subsection{Software functionalities}
-        The implementation of the quicR package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of RT-QuIC data.
+        The implementation of the \textbf{quicR} package encompasses several streamlined processes designed to facilitate data input, cleaning, transformation, and analysis of RT-QuIC data.
 This section provides a comprehensive guide to utilizing the package's key functionalities, detailing how to:
@@
                 \item \textbf{calculate\_threhold()}: returns a value which is a given number of standard deviations above the average background fluorescence of the entire microplate.
+This is a popular method of threshold calculation as reviewed in Rowden, et al.\cite{Rowden2023}.
                 \item \textbf{calculate\_TtT()}: takes the real-time data and calculates the time in hours needed to reach a given threshold value.
+This threshold can be supplied by calculate\_threshold() or determined separately by the user.
                 \item \textbf{calculate\_MPR()}: accepts raw or normalized data and returns the maximum value obtained during the run.
@@
             The ensuing goal of this package is visualizing RT-QuIC data.
-While there are many ways to represent this data, quicR includes two functions which provide a quick assessment of the reactions.
+While there are many ways to represent this data, \textbf{quicR} includes two functions which provide a quick assessment of the reactions.
             \begin{enumerate}
@@
     \section{Illustrative examples}
-        To demonstrate the utility of quicR, we used a typical RT-QuIC run performed on a 96-well plate.
+        To demonstrate the utility of \textbf{quicR}, we used a typical RT-QuIC run performed on a 96-well plate.
 The reaction was performed on a FLUOstar Omega plate reader (BMG Labtech, Ortenberg, Germany).
@@
             file <- "example.xlsx"\\
-
             \# Step 2: Extract the raw data.\\
             raw <- get\_real(file)[[1]]\\
-
             \# Step 3: Normalize the data against the background.\\
             normal <- normalize\_RFU(raw, transposed = FALSE)\\
-
             \# Step 4: Extract the metadata.\\
-            meta <- file |> organize\_tables() |> convert\_tables()\\
-
+            meta <- organize\_tables(file) |> convert\_tables()\\
             \# Step 5: Get sample locations.\\
             locations <- get\_sample\_locations(file)\\
-
             \# Step 6: Create the analyzed data frame.\\
             analyzed <- calculate\_metrics(normal, meta, dilution\_bool = TRUE)\\
-
             \# Step 7: Plot the analyzed data frame.\\
             plot\_metrics(analyzed)\\
-
             \# Step 8: Plot the plate view.\\
@@
                 \includegraphics[width=\textwidth]{images/boxplot.png}
-                \caption{Boxplot of the four metrics calculated in the quicR package.}
+                \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}
                 \label{fig:boxplot}
@@
     \section{Impact}
+        The \textbf{quicR} package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
+By integrating key metrics such as time-to-threshold (TtT) \cite{Orru2015}, maxpoint ratio (MPR) \cite{Rowden2023}, and maximum slope (MS) \cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
 
-        The quicR package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
-By integrating key metrics such as time-to-threshold (TtT) \cite{Orru2015}, maxpoint ratio (MPR) \cite{Rowden2023}, and maximum slope (MS) \cite{Henderson2015}, quicR addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
-
-        One of the primary strengths of quicR lies in its flexibility and user-centric design.
-The package leverages R’s powerful ecosystem and the tidyverse to streamline workflows and create high-quality, customizable visualizations.
-This ensures accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
+        One of the primary strengths of \textbf{quicR} lies in its streamlined workflow and user-centric design.
+The package leverages R’s powerful ecosystem and the tidyverse to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
 Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
@@
         Despite these strengths, there are limitations to consider.
-Currently, quicR is tailored to data exported from the MARS software, which may limit its applicability to researchers using alternative microplate readers.
+Currently, \textbf{quicR} is tailored to data exported from the MARS software, which may limit its applicability to researchers using alternative microplate readers.
 Future iterations of the package could expand compatibility by incorporating functions to handle diverse data formats.
-Furthermore, while quicR includes robust visualization tools, users seeking highly specialized plots like those made by Li, et al.\cite{Li2025} may require additional customization beyond the package’s default capabilities.
+Furthermore, while \textbf{quicR} includes robust visualization tools, users seeking highly specialized plots like those made by Li, et al.\cite{Li2025} may require additional customization beyond the package’s default capabilities.
 
         Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
-quicR provides tools to calculate key metrics, but consensus on thresholds and interpretations remains a challenge for the field \cite{Rowden2023}.
-Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling quicR to fully realize its potential as a diagnostic aid.
+\textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and interpretations remains a challenge for the field \cite{Rowden2023}.
+Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling \textbf{quicR} to fully realize its potential as a diagnostic aid.
 Diagnostic determinations could easily be built into the library, but a larger consensus within the research community will need to be reached to warrant inclusion.
@@
     \section{Conclusions}
-        quicR offers a powerful solution for the cleaning, analysis, and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
-By enabling consistent data handling and interpretation, quicR lays the groundwork for improved diagnostic consistency and reproducibility.
+        \textbf{quicR} offers a powerful solution for the cleaning, analysis, and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
+By enabling consistent data handling and interpretation, \textbf{quicR} lays the groundwork for improved diagnostic consistency and reproducibility.
 The package's open-source nature ensures that it will continue to evolve, integrating new insights and technologies as they emerge.
 
-        As RT-QuIC technology advances, tools like quicR will play a pivotal role in bridging the gap between assay development and practical application.
-By equipping researchers with reliable, standardized tools, quicR not only supports the study of prion and protein misfolding disorders but also serves as a model for the development of software solutions in other diagnostic fields.
+        As RT-QuIC technology advances, tools like \textbf{quicR} will play a pivotal role in bridging the gap between assay development and practical application.
+By equipping researchers with reliable, standardized tools, \textbf{quicR} not only supports the study of prion and protein misfolding disorders but also serves as a model for the development of software solutions in other diagnostic fields.
 
@@
 
-    %% \section{}
-    %% \label{}
-
-    %% References:
-    %% If you have bibdatabase file and want bibtex to generate the
-    %% bibitems, please use
-    %%
     \bibliographystyle{elsarticle-num} 
-    \bibliography{references.bib}
-
-    \textit{If the software repository you used supplied a DOI or another
-    Persistent IDentifier (PID), please add a reference for your software
-    here. For more guidance on software citation, please see our guide for
-    authors or \href{https://f1000research.com/articles/9-1257/v2}{this
-      article on the essentials of software citation by FORCE 11}, of
-    which Elsevier is a member.}
+    \bibliography{references}
 
@@
 \endinput
-%%
-%% End of file `SoftwareX_article_template.tex'.
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2025-02-27 R/plot_metrics.R
Fixed a bug where plot_metrics() would not return a figure if dilutions are not in the input data.

@@ -38,13 +38,25 @@
 plot_metrics <- function(data, sample_col = "Sample IDs", fill = "Dilutions", dilution_bool = TRUE, nrow = 2, ncol = 2) {
 
   variables <- function() {
-    (data %>% gather("variable", "value", -c(sample_col, fill)))$variable %>%
-      unique() %>%
-      length()
+    if (dilution_bool) {
+      (data %>% gather("variable", "value", -c(sample_col, fill)))$variable %>%
+        unique() %>%
+        length()
+    } else {
+      (data %>% gather("variable", "value", -c(sample_col)))$variable %>%
+        unique() %>%
+        length()
+    }
   }
 
   data %>%
-    gather("variable", "value", -c(sample_col, fill)) %>%
+    {
+      if (dilution_bool) {
+        gather(., "variable", "value", -c(sample_col, fill))
+      } else {
+        gather(., "variable", "value", -c(sample_col))
+      }
+    } %>%
     ggplot(
       aes(!!sym(sample_col),
         .data$value,
@@ -57,9 +69,9 @@ plot_metrics <- function(data, sample_col = "Sample IDs", fill = "Dilutions", di
     {if (variables() > 1) {
       facet_wrap(~variable, scales = "free_y", nrow = nrow, ncol = ncol)
     }} +
-    labs(
-      fill = if (dilution_bool) "Dilutions"
-    ) +
+    {if (dilution_bool) {
+      labs(fill = "Dilutions")
+    }} +
     theme(
       legend.position = "bottom",
       strip.text = element_text(face = "bold"),

### 2025-02-27 R/calculate_metrics.R
Fixed a bug where calculate_metrics() wouldn't work if dilutions weren't in the metadata input.

@@ -50,10 +50,10 @@ calculate_metrics <- function(
 
   data.frame(
     `Sample IDs` = if ("Sample IDs" %in% colnames(meta)) meta$`Sample IDs`,
-    Dilutions = if ("Dilutions" %in% colnames(meta)) meta$Dilutions,
     check.names = FALSE
   ) |>
     mutate(
+      Dilutions = if ("Dilutions" %in% colnames(meta)) meta$Dilutions,
       MPR = if ("MPR" %in% metrics) calculate_MPR(data, start_col),
       MS = if ("MS" %in% metrics) calculate_MS(data, MS_window),
       TtT = if ("TtT" %in% metrics) calculate_TtT(data, threshold),

### 2025-02-27 man/manuscript/softwareX_submission.tex
Updated the manuscript.

@@
         \title{\textbf{quicR}:\ An R Library for Streamlined Data Handling of Real-Time Quaking Induced Conversion Assays}
-        \author[label1,label2,label3]{Gage Rowden\corref{cor}}
+        \author[label1,label2,label3]{Gage R. Rowden\corref{cor}}
         \fntext[ ]{\textit{E-mail address: }rowde002@umn.edu}
         \cortext[cor]{Corresponding author.}
-        \author[label1,label2,label3]{Peter Larsen}
+        \author[label1,label2,label3]{Peter A. Larsen}
         \address[label1]{Department of Veterinary and Biomedical Sciences, University of Minnesota, USA.}
@@
             \textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
-With a focus on usability and reproducibility, the package is designed to standardize workflows and ensure compatibility across multiple laboratories.
 The overall architecture revolves around integration with the proprietary MARS software (BMG Labtech, Ortenberg, Germany) which exports raw data as Excel workbooks.
@@
                 \end{tblr}
-                \caption{Example CSV file plate layout for input into the ``BMG\_format'' function.
-The top left corner should be cell ``A1'' in the CSV file.
+                \caption{Example CSV file 96-well plate layout for input into the BMG\_format() function.
+The top left corner is cell ``A1'' in the CSV file.
 The top numbered row and the left-most lettered column should never be altered.}
@@
 These tables contain valuable metadata such as sample IDs, dilution factors, and microplate locations.
-                \item \textbf{convert\_tables()}: accepts tables outputted from \textbf{organize\_tables} and converts them to columns in a data frame.
+                \item \textbf{convert\_tables()}: accepts tables outputted from organize\_tables() and converts them to columns in a data frame.
                 \item \textbf{get\_sample\_locations()}: extracts the well locations for each sample.
@@
                 \item \textbf{get\_real()}: Retrieves the raw data from the Excel file, and outputs it as a data frame.
-                \item \textbf{transpose\_real()}: Swaps the rows and columns which makes some downstream analyses easier.
+                \item \textbf{transpose\_real()}: Swaps the rows and columns which facilitates downstream analyses.
                 \item \textbf{normalize\_RFU()}: normalizes the raw data by dividing each read by background fluorescence at a given cycle.
@@
         \subsubsection{Calculations}
-            Three analytical metrics have dedicated functions: time-to-threshold (TtT), maxpoint ratio (MPR), and maximum slope (MS).
-The rate of amyloid formation (RAF) does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+            Three analytical metrics have dedicated functions: TtT, MPR, and MS.
+RAF does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
 However, it can be calculated using the calculate\_metrics() function if TtT is chosen as an optional parameter.
@@
                 \includegraphics[width=\textwidth]{images/metric_example.png}
-                \caption{Example graph highlighting the calculated metrics described above.
+                \caption{Example graph highlighting the calculated metrics described herein.
 The red curve represents a raw data curve that has been normalized against background.
@@
             The ensuing goal of this package is visualizing RT-QuIC data.
-While there are many ways to represent this data, \textbf{quicR} includes two functions which provide a quick assessment of the reactions.
+While there are many ways to represent these data, \textbf{quicR} includes two functions which provide a rapid assessment of the RT-QuIC results.
             \begin{enumerate}
@@
             \# Step 6: Create the analyzed data frame.\\
-            analyzed <- calculate\_metrics(normal, meta, dilution\_bool = TRUE)\\
+            analyzed <- calculate\_metrics(normal, meta)\\
             \# Step 7: Plot the analyzed data frame.\\
@@
 
-            Once the file name is identified, the function get\_real() is used to extract the raw data.
+            Once the file name is identified, the get\_real() function is used to extract the raw data.
 This data is imported as a data frame with each sample designated as an individual column and the first column designated as time.
-Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to the normalize\_RFU() function.
+Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to the normalize\_RFU() function \cite{Rowden2023}.
 This function accepts an integer as an argument for the desired cycle to be selected for background measurement.
@@
                 \centering
-                \includegraphics[width=\textwidth]{images/boxplot.png}
+                \includegraphics[height=8in]{images/boxplot.png}
                 \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}
@@
     \section{Impact}
+        Since its development in 2010 \cite{Wilham2010,Atarashi2011}, the utility of RT-QuIC has expanded to a host of neurodegenerative diseases caused by prions and other misfolded proteins \cite{Orru2024,ALWAKIL202597,Wang2024}.
+The improved speed and accuracy of the assay has been a boon to human health \cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts \cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
+Thus, given the increasing usage of the assay, it is imperative that standardized practices and analyses are adopted.
+
         The \textbf{quicR} package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
-By integrating key metrics such as time-to-threshold (TtT) \cite{Orru2015}, maxpoint ratio (MPR) \cite{Rowden2023}, and maximum slope (MS) \cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
+By integrating key metrics such as TtT \cite{Orru2015}, RAF \cite{Gallups2022}, MPR \cite{Rowden2023}, and MS \cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
 
@@
         \textbf{quicR} offers a powerful solution for the cleaning, analysis, and visualization of RT-QuIC data, addressing critical needs in a rapidly evolving field.
-By enabling consistent data handling and interpretation, \textbf{quicR} lays the groundwork for improved diagnostic consistency and reproducibility.
+By enabling consistent data handling and interpretation, \textbf{quicR} provides the foundation for improved diagnostic consistency and reproducibility.
 The package's open-source nature ensures that it will continue to evolve, integrating new insights and technologies as they emerge.
@@
 We would like to acknowledge Suzanne Stone and Sarah Gresch for maintaining lab operations.
+This work was funded by the Legislative-Citizen Commission on Minnesota Resources.
 

### 2025-02-28 man/manuscript/plots.R
Updated the acknowledgments.

@@ -84,9 +84,9 @@ meta <- organize_tables(file) %>%
 
 df_analyzed <- calculate_metrics(df_norm, meta)
 
-plot_metrics(df_analyzed) +
+plot_metrics(df_analyzed, nrow = 4, ncol = 1) +
   guides(fill = guide_legend(nrow = 1))
-ggsave("images/boxplot.png", width = 12, height = 8)
+ggsave("images/boxplot.png", width = 4, height = 8)
 
 
 
@@ -95,5 +95,8 @@ ggsave("images/boxplot.png", width = 12, height = 8)
 
 
 locations <- get_sample_locations(file, dilution_bool = TRUE, sep = " ")
-plate_view(df_raw, locations)
+plate_view(df_raw, locations) +
+  theme(
+    strip.text = element_text(face = "bold", size = 12)
+  )
 ggsave("images/plate_view.png", width = 12, height = 8)

### 2025-03-03 man/manuscript/plots.R
Adjusted the manuscript boxplot to be more readable.

@@ -42,21 +42,124 @@ ms_time <- df_[which(df_$der == max(df_$der)), "x"]
 ggplot(df_, aes(x)) +
   geom_line(aes(y = raw), color = "darkred", size = 1.2) +
   geom_line(aes(y = der), color = "darkblue", size = 1.2) +
-
-  geom_segment(x = 0, xend = mpr_time, y = mpr, yend = mpr, color = "darkred", size = 1.2, linetype = "dashed") +
-  geom_segment(x = mpr_time, xend = mpr_time, y = -0.15, yend = mpr, color = "darkred", size = 1.2, linetype = "dashed") +
-  geom_segment(x = 0, xend = ms_time, y = ms, yend = ms, color = "darkblue", size = 1.2, linetype = "dashed") +
-  geom_segment(x = ms_time, xend = ms_time, y = -0.15, yend = ms, color = "darkblue", size = 1.2, linetype = "dashed") +
-  geom_segment(x = 0, xend = ttt, y = threshold, yend = threshold, color = "darkred", size = 1.2, linetype = "dashed") +
-  geom_segment(x = ttt, xend = ttt, y = -0.15, yend = threshold, color = "darkred", size = 1.2, linetype = "dashed") +
-
-  geom_label_repel(label = "Maxpoint Ratio", x = mpr_time, y = mpr, hjust = "inward", data = subset(df_, raw == mpr), force_pull = -200, color = "darkred", size = 5, segment.size = 1.2) +
-  geom_label_repel(label = "Max Slope", x = ms_time, y = ms, hjust = "outward", vjust = "outward", data = subset(df_, der == ms), force_pull = -100, color = "darkblue", size = 5, segment.size = 1.2) +
-  geom_label_repel(label = "Threshold", x = 1, y = threshold, vjust = "outward", data = subset(df_, x == 0), force_pull = -50, color = "darkred", size = 5, segment.size = 1.5) +
-  geom_label_repel(label = "Time-to-threshold", x = ttt, y = threshold, hjust = "inward", vjust = "outward", data = subset(df_, x == ttt), force_pull = -250, color = "darkred", size = 5, segment.size = 1.2) +
-  geom_text(label = "-- Normalized RFU", x = 1, y = 4, hjust = 0, vjust = 0, color = "darkred", size = 5) +
[…]

### 2025-03-03 man/manuscript/softwareX_submission.tex
Updated the acknowledgments.
Updated the manuscript

@@
                 \centering
-                \includegraphics[height=8in]{images/boxplot.png}
+                \includegraphics[width=\textwidth]{images/boxplot.png}
                 \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}
@@
 The improved speed and accuracy of the assay has been a boon to human health \cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts \cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
-Thus, given the increasing usage of the assay, it is imperative that standardized practices and analyses are adopted.
+Thus, it is imperative that standardized practices and analyses are adopted.
 
@@
         One of the primary strengths of \textbf{quicR} lies in its streamlined workflow and user-centric design.
-The package leverages R’s powerful ecosystem and the tidyverse to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users, from experienced data scientists to wet-lab researchers unfamiliar with programming.
+The package leverages R’s powerful ecosystem and the tidyverse \cite{tidyverse2019} to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users.
 Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
@@
         Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
-\textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and interpretations remains a challenge for the field \cite{Rowden2023}.
-Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling \textbf{quicR} to fully realize its potential as a diagnostic aid.
+\textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and diagnostic interpretations remains a challenge for the field \cite{Rowden2023}.
+Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling \textbf{quicR} to fully realize its potential as a diagnostic tool.
 Diagnostic determinations could easily be built into the library, but a larger consensus within the research community will need to be reached to warrant inclusion.
@@
 We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
+We thank Miranda Huang and Kristin Bondo for testing the code.
 We would like to acknowledge Suzanne Stone and Sarah Gresch for maintaining lab operations.

### 2025-03-13 man/manuscript/softwareX_submission.tex
Finally fixed .gitignore. Had to add "*" in front of file extensions.
Updated the keywords

@@
         \begin{keyword}
-            R package \sep{} RT-QuIC \sep{} prion \sep{} diagnostics \sep{} CJD \sep{} Parkinson's
+            R package \sep{} RT-QuIC \sep{} Nano-QuIC \sep{} Micro-QuIC \sep{} prion \sep{} diagnostics \sep{} Creutzfeldt-Jakob \sep{} Chronic Wasting Disease \sep{} Parkinson's
         \end{keyword}
@@
             % \hline{}
-            C4 & Legal Code License & GPL-3 \\
+            C4 & Legal Code License & GPL-3\\
             % \hline{}
-            C5 & Code versioning system used & Git \\
+            C5 & Code versioning system used & Git\\
             % \hline{}
-            C6 & Software code languages, tools, and services used & R \\
+            C6 & Software code languages, tools, and services used & R\\
             % \hline{}
-            C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0) \\
+            C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0)\\
             % \hline{}

### 2025-04-09 R/normalize_RFU.R
Vectorized the normalize_RFU function.

@@ -31,7 +31,6 @@
 normalize_RFU <- function(data, bg_cycle = 4, transposed = FALSE) {
 
   curate <- function(x) {
-
     colnames(x) %>%
       rbind(x) %>%
       unname() %>%
@@ -43,16 +42,7 @@ normalize_RFU <- function(data, bg_cycle = 4, transposed = FALSE) {
   }
 
   normalize <- function(x) {
-
-    df_norm <- x
-    for (i in 1:nrow(x)) {
-      for (j in 2:ncol(x)) {
-        raw_value <- df_norm[i, j]
-        df_norm[i, j] <- raw_value / x[i, bg_cycle + 1]
-      }
-    }
-
-    return(df_norm)
+    cbind(x[1], sweep(x[-1], 1, x[[bg_cycle + 1]], FUN = "/"))
   }
 
   if (transposed) normalize(data) else normalize(curate(data))

### 2025-04-09 R/normalize_RFU.R
Removed an unnecessary step in the example script.

@@ -20,9 +20,6 @@
 #' )
 #' df_ <- get_real(file)[[1]]
 #'
-#' # Export the tables in the first sheet of the file.
-#' dic <- quicR::organize_tables(file)
-#'
 #' # Normalize the raw data against the background reading.
 #' normalize_RFU(df_)
 #' }

### 2025-04-09 R/get_meta.R
Suppress messages from the readxl library.

@@ -22,7 +22,8 @@
 #' @export
 get_meta <- function(file) {
   if (is.character(file)) { # Read the Excel file into R.
-    data <- read_excel(file, sheet = 1, col_names = FALSE)
+    data <- read_excel(file, sheet = 1, col_names = FALSE) %>%
+      suppressMessages()
   } else if (is.data.frame(file)) {
     data <- file
   } else {

### 2025-04-09 R/get_meta.R
Vectorize getting the first NA index.

@@ -29,12 +29,8 @@ get_meta <- function(file) {
   } else {
     stop("Please enter either .xlsx string or dataframe. ")
   }
-  for (i in 1:nrow(data[, 1])) {
-    if (is.na(data[i, 1])) {
-      break
-    }
-  }
-  data <- data[1:i, 1] |>
+
+  data[1:which(is.na(data[[1]]))[1], 1] |>
     as.data.frame() |>
     na.omit() |>
     separate_wider_delim(
@@ -44,5 +40,4 @@ get_meta <- function(file) {
       too_few = "align_start",
       too_many = "merge"
     )
-  return(data)
 }

### 2025-04-09 R/calculate_TtT.R
Updated the example.

@@ -16,10 +16,9 @@
 #'   file = "test2.xlsx",
 #'   package = "quicR"
 #' )
-#' df_ <- get_real(file)[[1]] |>
-#'   quicR::transpose_real() |>
-#'   quicR::normalize_RFU(transposed = TRUE)
-#' calculate_TtT(df_, threshold = 2)
+#' get_real(file)[[1]] |>
+#'   quicR::normalize_RFU() |>
+#'   calculate_TtT(threshold = 2)
 #' }
 #'
 #' @export

### 2025-04-09 R/calculate_TtT.R
Vectorized calculateTtT.

@@ -23,42 +23,43 @@
 #'
 #' @export
 calculate_TtT <- function(data, threshold, start_col = 3) {
-  # Initialize the list containing the times-to-threshold.
-  TtT_list <- c(rep(NA, nrow(data)))
+  # Get numeric cycle times
+  cycles <- as.numeric(colnames(data)[start_col:ncol(data)])
+  cycle_interval <- diff(cycles[1:2])  # assumes uniform intervals
 
-  # Set the cycle interval.
-  cycle_interval <- diff(as.numeric(colnames(data[, start_col:(start_col + 1)])))
+  # Extract just the numeric matrix portion
+  readings <- as.matrix(data[, start_col:ncol(data)])
 
-  # Calculate the Time to Threshold
-  for (i in 1:nrow(data)) {
-    for (j in start_col:(ncol(data))) {
-      # Use the threshold argument.
-      current_read <- data[i, j]
+  # Apply function across rows
+  TtT <- apply(
+    readings,
+    1,
+    function(row) {
+      # Find first index where threshold is crossed
+      cross_idx <- which(row >= threshold)[1]
 
-      if (is.na(current_read)) {
-        TtT_list[i] <- as.numeric(colnames(data[j - 1]))
-        break
-      }
+      if (!is.na(cross_idx)) {
+        if (cross_idx == 1) {
+          return(cycles[1])  # threshold met at first timepoint
+        }
 
-      if (current_read >= threshold) {
-        previous_read <- data[i, j - 1]
+        # Linear interpolation
+        prev <- row[cross_idx - 1]
+        curr <- row[cross_idx]
+        slope <- curr - prev
 
-        delta_rfu <- current_read - previous_read
-        slope <- delta_rfu / cycle_interval
+        if (slope == 0) return(cycles[cross_idx])  # avoid division by zero
 
-        delta_threshold <- threshold - previous_read
-        delta_t <- delta_threshold / slope
+        delta_threshold <- threshold - prev
+        delta_time <- delta_threshold / slope
 
-        previous_cycle <- as.numeric(colnames(data[j - 1]))
-        TtT_list[i] <- previous_cycle + delta_t
-
-        break
-      }
-
-      if (j == ncol(data)) {
-        TtT_list[i] <- as.numeric(colnames(data[j]))
+        return(cycles[cross_idx - 1] + delta_time)
+      } else {
+        # If never crossed, return last cycle time
[…]

### 2025-04-09 inst/extdata/time_testing.R
Added a script for testing time improvements

@@ -1,0 +1,130 @@
+library(quicR)
+library(tidyverse)
+library(janitor)
+library(readxl)
+
+functions <- list.files("R", full.names = TRUE)
+sapply(functions, source)
+files <- list.files("inst/extdata/input_files", ".xlsx", full.names = TRUE)
+df_list <- sapply(files, get_real)
+norm_list <- sapply(df_list, normalize_RFU)
+tabs <- sapply(files, organize_tables)
+
+
+time_change <- function(fun1, fun2) {
+  start1 <- Sys.time()
+  fun1
+  time1 <- as.numeric(Sys.time() - start1)
+
+  start2 <- Sys.time()
+  fun2
+  time2 <- as.numeric(Sys.time() - start2)
+
+  paste0("time decreased by ", round(100 * (1 - (time1 / time2)), 2), "%")
+}
+
+
+
+
+# get_real ----------------------------------------------------------------
+
+
+
+get_real_delta <- paste(
+  "get_real",
+  time_change(
+    sapply(df_list, get_real),
+    sapply(df_list, quicR::get_real)
+  )
+)
+
+
+
+# normalize_RFU -----------------------------------------------------------
+
+
+
+normalize_RFU_delta <- paste(
+  "normalize_RFU",
+  time_change(
+    sapply(df_list, normalize_RFU),
+    sapply(df_list, quicR::normalize_RFU)
+  )
+)
+
+
+
+# calculate_TtT -----------------------------------------------------------
+
+
+
+calculate_TtT_delta <- paste(
+  "calculate_TtT",
+  time_change(
+    sapply(norm_list, calculate_TtT, threshold = 2),
+    sapply(norm_list, quicR::calculate_TtT, threshold = 2)
+  )
+)
+
+
+
+# organize_tables ---------------------------------------------------------
+
+
+
+organize_tables_delta <- paste(
+  "organize_tables",
+  time_change(
+    sapply(files, organize_tables),
+    sapply(files, quicR::organize_tables)
+  )
+)
+
+
+
+# convert_tables ----------------------------------------------------------
+
+
+
+convert_tables_delta <- paste(
+  "convert_tables",
+  time_change(
+    sapply(tabs, convert_tables),
+    sapply(tabs, quicR::convert_tables)
+  )
+)
+
+
+
+# get_meta ----------------------------------------------------------------
+
+
+
+get_meta_delta <- paste(
[…]

### 2025-04-09 man/manuscript/softwareX_submission.tex

@@
 
+    \section*{Declaration of Conflicting Interests}
+        Peter A.
+Larsen is a co-founder and stock owner, and Gage R.
+Rowden is a stock owner of Priogen Corp., a diagnostic company specializing in the ultra-sensitive detection of pathogenic proteins associated with prion and protein-misfolding diseases.
+The University of Minnesota licensed patent applications to Priogen.
+
     \section*{Acknowledgements}

### 2025-05-21 inst/extdata/benchmarking.R
Added a benchmarking script and results.

@@ -1,0 +1,98 @@
+library(quicR)
+library(QuICSeedR)
+library(dplyr)
+library(readxl)
+library(stringr)
+library(rbenchmark)
+
+
+
+# QuICSeedR Pipeline ------------------------------------------------------
+
+
+
+path <- "input_files/QuICSeedR benchmarking"
+
+bulk <- BulkReadMARS(path, "plate", "raw") %>%
+  BulkProcessing(do_analysis = FALSE)
+
+files <- list.files(path, ".xlsx", full.names = TRUE, recursive = TRUE)
+
+raw <- read_xlsx(files[2])
+plate <- read_xlsx(files[1])
+replicates <- GetReplicate(plate)
+meta <- CleanMeta(raw, plate, replicates)
+time <- ConvertTime(raw)
+clean_raw <- CleanRaw(meta, raw, time, 48)
+calcs <- GetCalculation(clean_raw, meta, threshold_method = "bg_ratio", binw = 3)
+
+
+quicseedr_results <- benchmark(
+  BulkReadMARS(path, "plate", "raw") %>%
+    BulkProcessing(do_analysis = FALSE),
+  GetReplicate(read_xlsx(files[1])),
+  CleanMeta(read_xlsx(files[2]), read_xlsx(files[1]), replicates),
+  ConvertTime(read_xlsx(files[2])),
+  CleanRaw(meta, read_xlsx(files[2]), time, 48),
+  GetCalculation(clean_raw, meta, threshold_method = "bg_ratio", binw = 3),
+  PlotMetric(calcs),
+  PlotPlate(read_xlsx(files[2]), time),
+  replications = 50,
+  columns = c("test", "elapsed", "replications")
+)
+
+
+
+
+# quicR Pipeline ----------------------------------------------------------
+
+
+
+bulk_analyze <- function(files) {
+  calculate <- function(file) {
+    calculate_metrics(
+      get_real(file)[[1]] |>
+        normalize_RFU(),
+      organize_tables(file, ifelse(str_detect(file, "384"), 384, 96)) |>
+        convert_tables()
+    )
+  }
+  sapply(files, calculate)
+}
+
+files <- list.files("input_files", ".xlsx", full.names = TRUE)
+file <- files[1]
+
+plate <- read_xlsx(file)
+raw <- read_xlsx(file, sheet = 2)
+data <- get_real(raw)[[1]]
+norm <- normalize_RFU(data)
+meta <- convert_tables(organize_tables(file))
+analyzed <- calculate_metrics(norm, meta)
[…]

### 2025-05-21 man/manuscript/softwareX_submission.tex
Added a clarification that RT-QuIC is an SAA.

@@
     \section{Motivation and significance}
-        Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
+        Real-time quaking induced conversion (RT-QuIC) is type of seed amplification assay (SAA) that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
 The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.

### 2025-05-21 man/manuscript/softwareX_submission.tex
Added clarification that time-to-threshold is also known as lag time.
Addressed reviewer comments.

@@
         \begin{enumerate}
-            \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold \cite{Orru2015}.
+            \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold (also known as lag time) \cite{Orru2015}. 
             \item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed \cite{Gallups2022}.
@@
                     \item \textbf{calculate\_MS()}: computes the approximate derivative of the real-time data and returns the maximum value obtained during the run.
-                \item \textbf{calculate\_metrics()}: makes a call to functions 2--4 above and generates a data frame with the sample-matched metrics. Also computes RAF if TtT is given as an argument.
+                    \item \textbf{calculate\_metrics()}: makes a call to functions 2--4 above and generates a data frame with the sample-matched metrics.
+Also computes RAF if TtT is given as an argument.
                 \end{enumerate}
@@
 
+        \subsection{Comparable Methods}
+            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, \textbf{QuICSeedR} \cite{Li2025}.
+While both \textbf{quicR} and \textbf{QuICSeedR} offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
+
+            Benchmarking was performed using equivalent functions between the two packages, and results are summarized in Table~\ref{tbl:benchmark}.
+In general, \textbf{QuICSeedR} out-performs \textbf{quicR} across the board.
+However, \textbf{quicR} addresses several practical limitations that the authors believe justifies the slower times.
+Notably, \textbf{QuICSeedR} requires an additional, manually formatted Excel file to input sample metadata, whereas \textbf{quicR} directly parses raw and meta data embedded within a single MARS export file.
+This design reduces user overhead and minimizes potential for transcription errors.
+
+            \textbf{quicR} also provides more granular control over metric calculations, allowing users to compute MPR, MS, TtT, and RAF independently rather than as a fixed batch.
+While \textbf{QuICSeedR} includes built-in support for bulk analysis and diagnostic outputs, these features can be approximated in \textbf{quicR} via standard R idioms (e.g., \textbf{apply} family of functions), and are planned for future development.
+
+            Importantly, \textbf{quicR} is actively maintained, in contrast to \textbf{QuICSeedR}, which, to the authors’ knowledge, is no longer under active development.
+Overall, \textbf{quicR} favors flexibility, reproducibility, and usability with raw instrument output at the expense of execution speed—trade-offs that align with the package’s intended use in diagnostic pipelines.
+
+            \begin{table}[ht]
+                \centering
+                \begin{tblr}{
+                    cells     = {font = \fontsize{11pt}{11pt}\selectfont},
+                    colspec   = {rcc}, 
+                    row{1}    = {font=\bfseries},
+                    rowhead   = 1,
+                    width     = \textwidth
+                }
+                    \hline
+                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} \\ 
+                    \hline
+                    Number of input files required & 1 & 2 \\ 
+                    Number of threshold methods & 2 & 3 \\
+                    Requires manual metadata entry & No & Yes \\
+                    Actively maintained & Yes & No \\
+                    Built-in bulk analysis support & No & Yes \\
+                    Diagnostic analysis functionality & No & Yes \\
+                    Incorporates dilution factors & Yes & No \\
+                    Converts time units & No & Yes \\
+                    Calculates individual metrics independently & Yes & No \\
+                    \hline
+                    Plate view plot execution time (s) & 0.0978 & 0.0616 \\
+                    Metric plot execution time (s) & 0.0108 & 0.0052 \\
+                    Metric calculations (MPR, MS, etc.) (s) & 0.3912 & 0.0184 \\
+                    Metadata parsing time (s) & 0.1376 & 0.0374 \\
+                    Raw data parsing time (s) & 0.0722 & 0.0498 \\
+                    Bulk analysis (6 files) (s) & 10.9738 & 0.8486 \\
+                    \hline
+                \end{tblr}
+                \caption{Comparison of core features and execution times between \textbf{quicR} and \textbf{QuICSeedR}.
+While \textbf{QuICSeedR} demonstrates superior execution speed, \textbf{quicR} offers enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files.
+All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM).}
+                \label{tbl:benchmark}
+            \end{table}
+
+        \subsection{Maintenance and Community Involvement}
+            The \textbf{quicR} package is developed with long-term maintainability and community engagement in mind.
+The source code is hosted on GitHub (\url{https://github.com/gagerowden/quicR}), where users can report issues, request features, and contribute improvements via pull requests.
+A comprehensive \textbf{CONTRIBUTING.md} file and issue templates are provided to streamline collaboration and lower the barrier for external contributions.
+In addition to continuous integration testing, we plan to tag releases with semantic versioning and maintain a changelog to track updates and improvements.
+Feedback from diagnostic users has already led to enhancements in metadata parsing and output plotting, and we anticipate continued improvements through engagement with the broader scientific community.
+We encourage users to share their use cases, raise issues, and help shape future development directions.
+
     \section{Illustrative examples}
@@
         \subsection{Example Code}
-            \# Step 1: Identify the raw file.\\
+            \# Step 1: Install and load the package\\
+            install.packages("quicR")\\
+            library(quicR)\\
+            \# Step 2: Identify the raw file.\\
             file <- "example.xlsx"\\
-            \# Step 2: Extract the raw data.\\
+            \# Step 3: Extract the raw data.\\
             raw <- get\_real(file)[[1]]\\
-            \# Step 3: Normalize the data against the background.\\
+            \# Step 4: Normalize the data against the background.\\
             normal <- normalize\_RFU(raw, transposed = FALSE)\\
-            \# Step 4: Extract the metadata.\\
+            \# Step 5: Extract the metadata.\\
             meta <- organize\_tables(file) |> convert\_tables()\\
-            \# Step 5: Get sample locations.\\
+            \# Step 6: Get sample locations.\\
             locations <- get\_sample\_locations(file)\\
-            \# Step 6: Create the analyzed data frame.\\
+            \# Step 7: Create the analyzed data frame.\\
             analyzed <- calculate\_metrics(normal, meta)\\
-            \# Step 7: Plot the analyzed data frame.\\
+            \# Step 8: Plot the analyzed data frame.\\
             plot\_metrics(analyzed)\\
-            \# Step 8: Plot the plate view.\\
+            \# Step 9: Plot the plate view.\\
             plate\_view(raw, locations)\\

### 2025-05-21 man/manuscript/softwareX_submission.tex
Edited the comparisons table.

@@
                     Number of threshold methods & 2 & 3 \\
-                    Requires manual metadata entry & No & Yes \\
+                    Automated metadata entry & Yes & No \\
                     Actively maintained & Yes & No \\
@@
                     Converts time units & No & Yes \\
-                    Calculates individual metrics independently & Yes & No \\
+                    Calculates metrics independently & Yes & No \\
                     \hline

### 2025-05-22 man/manuscript/softwareX_submission.tex
Added benchmarking for the rtquicR package as well.

@@
         \begin{keyword}
-            R package \sep{} RT-QuIC \sep{} Nano-QuIC \sep{} Micro-QuIC \sep{} prion \sep{} diagnostics \sep{} Creutzfeldt-Jakob \sep{} Chronic Wasting Disease \sep{} Parkinson's
+            Chronic Wasting Disease \sep{} Creutzfeldt-Jakob Disease \sep{} Nano-QuIC \sep{} RT-QuIC \sep{} prion diagnostics \sep{} Parkinson's Disease \sep{} seed amplification assay
         \end{keyword}
@@
     \section{Motivation and significance}
-        Real-time quaking induced conversion (RT-QuIC) is type of seed amplification assay (SAA) that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
+        Real-time quaking induced conversion (RT-QuIC) is within the family of seed amplification assays (SAAs), similiar to protein misfolding cyclic amplification (PMCA), and has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
 The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
@@
         \subsection{Comparable Methods}
-            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, \textbf{QuICSeedR} \cite{Li2025}.
-While both \textbf{quicR} and \textbf{QuICSeedR} offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
+            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R packages, \textbf{QuICSeedR} \cite{Li2025} and \textbf{rtquicR} \cite{Slota2023}.
+While all three offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
 
-            Benchmarking was performed using equivalent functions between the two packages, and results are summarized in Table~\ref{tbl:benchmark}.
+            Benchmarking was performed using the rbenchmark library \cite{rbenchmark} with 50 replications for each function.
+Comparisons are approximate as equivalent functions were not necessarily found between the three packages, and results are summarized in Table~\ref{tbl:benchmark}.
 In general, \textbf{QuICSeedR} out-performs \textbf{quicR} across the board.
@@
             \textbf{quicR} also provides more granular control over metric calculations, allowing users to compute MPR, MS, TtT, and RAF independently rather than as a fixed batch.
-While \textbf{QuICSeedR} includes built-in support for bulk analysis and diagnostic outputs, these features can be approximated in \textbf{quicR} via standard R idioms (e.g., \textbf{apply} family of functions), and are planned for future development.
+While \textbf{QuICSeedR} includes built-in support for bulk analysis and diagnostic outputs, these features can be approximated in \textbf{quicR} via standard R idioms (e.g., `apply' family of functions), and are planned for future development.
 
-            Importantly, \textbf{quicR} is actively maintained, in contrast to \textbf{QuICSeedR}, which, to the authors’ knowledge, is no longer under active development.
             Overall, \textbf{quicR} favors flexibility, reproducibility, and usability with raw instrument output at the expense of execution speed—trade-offs that align with the package’s intended use in diagnostic pipelines.
 
-            \begin{table}[ht]
+            \begin{table}[H]
                 \centering
@@
                     cells     = {font = \fontsize{11pt}{11pt}\selectfont},
-                    colspec   = {rcc}, 
+                    colspec   = {rccc}, 
                     row{1}    = {font=\bfseries},
@@
                     \hline
-                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} \\ 
+                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} & \textbf{rtquicR} \\ 
                     \hline
-                    Number of input files required & 1 & 2 \\ 
-                    Number of threshold methods & 2 & 3 \\
-                    Automated metadata entry & Yes & No \\
-                    Actively maintained & Yes & No \\
-                    Built-in bulk analysis support & No & Yes \\
-                    Diagnostic analysis functionality & No & Yes \\
-                    Incorporates dilution factors & Yes & No \\
-                    Converts time units & No & Yes \\
-                    Calculates metrics independently & Yes & No \\
+                    Available on CRAN & Yes & Yes & No \\
+                    Number of input files required & 1 & 2 & 2 \\ 
+                    Number of threshold methods & 2 & 3 & 4 \\
+                    Number of normalization methods & 1 & 1 & 2 \\
+                    Automated metadata entry & Yes & No & No \\
+                    Automated sample locations & Yes & Yes & No \\
+                    Allows empty data & Yes & Yes & No \\
+                    Compatible with 384-well plates & Yes & Yes & No \\
+                    % Actively maintained & Yes & No \\
+                    Built-in bulk analysis support & No & Yes & Yes \\
+                    Diagnostic analysis functionality & No & Yes & No \\
+                    Incorporates dilution factors & Yes & No & Yes \\
+                    Converts time units & No & Yes & Yes \\
+                    Calculates metrics independently & Yes & No & Yes \\
+                    Calculates metrics in bulk & Yes & Yes & No \\
+                    Calcualates MPR & Yes & Yes & Yes \\
+                    Calculates MS & Yes & Yes & No \\
+                    Calculates TtT & Yes & Yes & Yes \\
+                    Calculates RAF & Yes & Yes & No \\
+                    Calculates area under the curve & No & No & Yes \\
+                    Calculates SD50 & No & No & Yes \\
                     \hline
-                    Plate view plot execution time (s) & 0.0978 & 0.0616 \\
-                    Metric plot execution time (s) & 0.0108 & 0.0052 \\
-                    Metric calculations (MPR, MS, etc.) (s) & 0.3912 & 0.0184 \\
-                    Metadata parsing time (s) & 0.1376 & 0.0374 \\
-                    Raw data parsing time (s) & 0.0722 & 0.0498 \\
-                    Bulk analysis (6 files) (s) & 10.9738 & 0.8486 \\
+                    Plate view plot execution time (s) & 0.082 & 0.062 & NA \\
+                    Metric plot execution time (s) & 0.009 & 0.005 & 0.007 \\
+                    Metric calculations (MPR, MS, etc.) (s) & 0.355 & 0.018 & NA\\
+                    MPR calculation (s) & 0.002 & NA & 0.028 \\
+                    TtT calculation (s) & 0.001 & NA & 0.131 \\
+                    Metadata parsing time (s) & 0.127 & 0.037 & NA \\
+                    Raw data parsing time (s) & 0.069 & 0.050 & 0.191 \\
+                    Bulk analysis (s/file) & 6.550 & 0.849 & 1.986 \\
                     \hline

### 2025-05-22 inst/extdata/benchmarking.R

@@ -1,5 +1,6 @@
 library(quicR)
 library(QuICSeedR)
+library(rtquicR)
 library(dplyr)
 library(readxl)
 library(stringr)
@@ -50,12 +51,14 @@ quicseedr_results <- benchmark(
 
 bulk_analyze <- function(files) {
   calculate <- function(file) {
-    calculate_metrics(
-      get_real(file)[[1]] |>
-        normalize_RFU(),
-      organize_tables(file, ifelse(str_detect(file, "384"), 384, 96)) |>
-        convert_tables()
-    )
+    if (!str_detect(file, "384")) {
+      calculate_metrics(
+        get_real(file)[[1]] |>
+          normalize_RFU(),
+        organize_tables(file, ifelse(str_detect(file, "384"), 384, 96)) |>
+          convert_tables()
+      )
+    } else return()
   }
   sapply(files, calculate)
 }
@@ -77,9 +80,49 @@ quicr_results <- benchmark(
   get_real(raw),
   normalize_RFU(data),
   calculate_metrics(norm, meta),
+  calculate_MPR(norm),
+  calculate_TtT(norm, 2),
   plot_metrics(analyzed),
   get_sample_locations(file),
   plate_view(data, locations),
+  replications = 50,
+  columns = c("test", "elapsed", "replications")
+)
+
+
+
+# rtquicR -----------------------------------------------------------------
+
+
+
+files <- list.files("input_files/rtquicR benchmarking", "test", full.names = TRUE)
+file <- files[1]
+
+batch_rtqr <- function(files) {
+  analyze <- function(file) {
+    data <- load_quic_results(file, "raw_table", "All Cycles", 11, 2)
+    meta <- read_xlsx(file, sheet = 3)
+    plot_data <- signal_curve(data, meta)
+    lag_data <- calc_lag_phase(data, meta, cutoff = 48)
+    calc_AUC_sig(plot_data)
+    calc_mpr(plot_data)
+  }
+  sapply(files, analyze)
+}
+
+raw <- load_quic_results(file, "raw_table", "All Cycles", 11, 2)
+meta <- read_xlsx(file, sheet = 3)
+data <- signal_curve(raw, meta, "baseline_RFU_per_well", 4)
+# p <- plot_signal_curve(data)
+
+
+
+rtquicR_results <- benchmark(
+  load_quic_results(file, "raw_table", "All Cycles", 11, 2),
+  batch_rtqr(files),
+  calc_mpr(data),
[…]

### 2025-05-28 man/manuscript/softwareX_submission.tex
Quieted chktex warnings.

@@
 \documentclass[preprint,12pt,a4paper]{elsarticle}
+
+% Quiet chktex warnings.
+% chktex-file 44
+% chktex-file 36
 
@@
         \begin{tabular}{lp{6cm}p{6cm}}
-            \hline{}
+            \hline
             \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
-            \hline{}
+            \hline
             C1 & Current code version & V2.1.0 \\
-            % \hline{}
             C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0} \\
-            % \hline{}
             C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
-            % \hline{}
             C4 & Legal Code License & GPL-3\\
-            % \hline{}
             C5 & Code versioning system used & Git\\
-            % \hline{}
             C6 & Software code languages, tools, and services used & R\\
-            % \hline{}
             C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0)\\
-            % \hline{}
             C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
-            % \hline{}
             C9 & Support email for questions & rowde002@umn.edu\\
-            \hline{}
+            \hline
         \end{tabular}
@@
     \section{Motivation and significance}
-        Real-time quaking induced conversion (RT-QuIC) is within the family of seed amplification assays (SAAs), similiar to protein misfolding cyclic amplification (PMCA), and has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
-The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
-The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies \cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
-However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation \cite{Rowden2023}.
+        Real-time quaking induced conversion (RT-QuIC) is within the family of seed amplification assays (SAAs), similiar to protein misfolding cyclic amplification (PMCA), and has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates~\cite{Wilham2010, Atarashi2011}.
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed~\cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies~\cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
+However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation~\cite{Rowden2023}.
 
-        To address this gap, we introduce \textbf{quicR}, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, \textbf{quicR} aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}.
-\textbf{quicR} is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
+        To address this gap, we introduce \textbf{quicR}, an open-source library, developed in R~\cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, \textbf{quicR} aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC~\cite{Christenson2023} and Micro-QuIC~\cite{Lee2024}.\ \textbf{quicR} is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
 
@@
         \begin{enumerate}
-            \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold (also known as lag time) \cite{Orru2015}. 
-            \item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed \cite{Gallups2022}.
-            \item Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities \cite{Rowden2023}.
-            \item Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation \cite{Henderson2015}.
+            \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold (also known as lag time)~\cite{Orru2015}. 
+            \item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed~\cite{Gallups2022}.
+            \item Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities~\cite{Rowden2023}.
+            \item Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation~\cite{Henderson2015}.
         \end{enumerate}
@@
         In addition to analytical tools, \textbf{quicR} provides flexible and customizable visualization capabilities.
-Leveraging the powerful ggplot2 library \cite{ggplot2016}, \textbf{quicR} enables users to generate high-quality, publication-ready figures.
+Leveraging the powerful ggplot2 library~\cite{ggplot2016}, \textbf{quicR} enables users to generate high-quality, publication-ready figures.
 These visualizations can be further customized using the intuitive `+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
@@
         \subsection{Software architecture}
-            \textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
+            \textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure~\ref{fig:workflow}).
 The overall architecture revolves around integration with the proprietary MARS software (BMG Labtech, Ortenberg, Germany) which exports raw data as Excel workbooks.
@@
 Orange nodes are functions which calculate some metric.
-Finally, yellow nodes represent data analysis endpoints.}
-                \label{fig:workflow}
+Finally, yellow nodes represent data analysis endpoints.}\label{fig:workflow}
             \end{figure}
@@
                 \begin{enumerate}
-                    \item \textbf{BMG\_format()}: This function allows for input of a CSV file containing the plate layout (see Table \ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+                    \item \textbf{BMG\_format()}: This function allows for input of a CSV file containing the plate layout (see Table~\ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
 The file can then be imported into the Omega control software before running.
@@
 The top left corner is cell ``A1'' in the CSV file.
-The top numbered row and the left-most lettered column should never be altered.}
-                    \label{tbl:layout}
+The top numbered row and the left-most lettered column should never be altered.}\label{tbl:layout}
                 \end{table}
@@
 Those tables include the ``Sample IDs'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
-For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually.
+For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\ If there is no table, the user can simply add it manually.
 
@@
             \subsubsection{Retrieving and Manipulating Raw Data}
-                The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS. There are three functions dedicated to the retrieval and cleaning of raw data.
+                The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS.\ There are three functions dedicated to the retrieval and cleaning of raw data.
 
@@
             \subsubsection{Calculations}
-                Three analytical metrics have dedicated functions: TtT, MPR, and MS.
-RAF does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+                Three analytical metrics have dedicated functions: TtT, MPR, and MS.\ RAF does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
 However, it can be calculated using the calculate\_metrics() function if TtT is chosen as an optional parameter.
 Each function below accepts input from the transpose\_real() or the normalize\_RFU() functions.
-See Figure \ref{fig:metrics} for an example of the output of these functions.
+See Figure~\ref{fig:metrics} for an example of the output of these functions.
 
@@
 
-            Once the file name is identified, the get\_real() function is used to extract the raw data.
+            Once the file name is identified, get\_real() is used to extract the raw data.
 This data is imported as a data frame with each sample designated as an individual column and the first column designated as time.
-Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to the normalize\_RFU() function \cite{Rowden2023}.
+Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to normalize\_RFU()~\cite{Rowden2023}.
 This function accepts an integer as an argument for the desired cycle to be selected for background measurement.
@@
             Once the proper variables have been defined, they can be used as input in the visualization functions.
-The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as Figure \ref{fig:boxplot}.
-Additionally, the raw data and sample locations are used to plot the plate view as in Figure \ref{fig:plateview}.
+The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as Figure~\ref{fig:boxplot}.
+Additionally, the raw data and sample locations are used to plot the plate view as in Figure~\ref{fig:plateview}.
 
@@
                 \includegraphics[width=\textwidth]{images/boxplot.png}
-                \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}
-                \label{fig:boxplot}
+                \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}\label{fig:boxplot}
             \end{figure}
@@
                 \includegraphics[width=\textwidth]{images/plate_view.png}
-                \caption{Plate view of RT-QuIC. Wells are identified with a sample ID and dilution factor separated by an optional delimiter (in this case, a whitespace).}
-                \label{fig:plateview}
+                \caption{Plate view of RT-QuIC.\ Wells are identified with a sample ID and dilution factor separated by an optional delimiter (in this case, a whitespace).}\label{fig:plateview}
             \end{figure}
@@
     \section{Impact}
-        Since its development in 2010 \cite{Wilham2010,Atarashi2011}, the utility of RT-QuIC has expanded to a host of neurodegenerative diseases caused by prions and other misfolded proteins \cite{Orru2024,ALWAKIL202597,Wang2024}.
-The improved speed and accuracy of the assay has been a boon to human health \cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts \cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
+        Since its development in 2010~\cite{Wilham2010,Atarashi2011}, the utility of RT-QuIC has expanded to a host of neurodegenerative diseases caused by prions and other misfolded proteins~\cite{Orru2024,ALWAKIL202597,Wang2024}.
+The improved speed and accuracy of the assay has been a boon to human health~\cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts~\cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
 Thus, it is imperative that standardized practices and analyses are adopted.
@@
         The \textbf{quicR} package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
-By integrating key metrics such as TtT \cite{Orru2015}, RAF \cite{Gallups2022}, MPR \cite{Rowden2023}, and MS \cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
+By integrating key metrics such as TtT~\cite{Orru2015}, RAF~\cite{Gallups2022}, MPR~\cite{Rowden2023}, and MS~\cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
 
         One of the primary strengths of \textbf{quicR} lies in its streamlined workflow and user-centric design.
-The package leverages R’s powerful ecosystem and the tidyverse \cite{tidyverse2019} to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users.
+The package leverages R’s powerful ecosystem and the tidyverse~\cite{tidyverse2019} to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users.
 Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
@@
 
-        Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
-\textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and diagnostic interpretations remains a challenge for the field \cite{Rowden2023}.
+        Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.\ \textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and diagnostic interpretations remains a challenge for the field~\cite{Rowden2023}.
 Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling \textbf{quicR} to fully realize its potential as a diagnostic tool.
@@
     \section*{Acknowledgements}
-        Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.
-We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
+        Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.\ We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
 We thank Miranda Huang and Kristin Bondo for testing the code.

### 2025-05-28 man/manuscript/softwareX_submission.tex
Updated Comparable Methods section.

@@
 Time‐to‐threshold is determined as the time required to cross a given threshold (in this example, the threshold is set at 0.2).
-The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.}
-                    \label{fig:metrics}
+The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.}\label{fig:metrics}
                 \end{figure}
@@
                 \begin{enumerate}
-                    \item \textbf{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
+                    \item \texttt{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
 Makes an 8$\times$12 or 16$\times$24 faceted plot depending on if the plate has 96 or 384 wells.
@@
         \subsection{Comparable Methods}
-            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R packages, \textbf{QuICSeedR} \cite{Li2025} and \textbf{rtquicR} \cite{Slota2023}.
+            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, QuICSeedR\ \cite{Li2025}, and the unpublished rtquicR\ \cite{Slota2023}.
 While all three offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
 
-            Benchmarking was performed using the rbenchmark library \cite{rbenchmark} with 50 replications for each function.
-Comparisons are approximate as equivalent functions were not necessarily found between the three packages, and results are summarized in Table~\ref{tbl:benchmark}.
-In general, \textbf{QuICSeedR} out-performs \textbf{quicR} across the board.
-However, \textbf{quicR} addresses several practical limitations that the authors believe justifies the slower times.
-Notably, \textbf{QuICSeedR} requires an additional, manually formatted Excel file to input sample metadata, whereas \textbf{quicR} directly parses raw and meta data embedded within a single MARS export file.
-This design reduces user overhead and minimizes potential for transcription errors.
+            Benchmarking was performed using the rbenchmark library~\cite{rbenchmark} with 50 replications for each function.
+Comparisons are approximate, as equivalent functions were not necessarily found between the three packages.
+Results are summarized in Table~\ref{tbl:benchmark}.
+In general, QuICSeedR\ demonstrates the fastest execution times across most core functions.
+However, \textbf{quicR} addresses several practical limitations that the authors believe justify the slower performance in some areas.
+Notably, QuICSeedR requires an additional, manually formatted Excel file to input sample metadata, whereas \textbf{quicR} directly parses both raw and meta data embedded within a single MARS export file.
+This design reduces user overhead and minimizes the potential for transcription errors.
 
-            \textbf{quicR} also provides more granular control over metric calculations, allowing users to compute MPR, MS, TtT, and RAF independently rather than as a fixed batch.
-While \textbf{QuICSeedR} includes built-in support for bulk analysis and diagnostic outputs, these features can be approximated in \textbf{quicR} via standard R idioms (e.g., `apply' family of functions), and are planned for future development.
+            The rtquicR\ package introduces support for additional thresholding methods and normalization strategies, and uniquely includes features such as SD50 and area-under-the-curve calculations.
+However, it does not currently support 384-well plate layouts, automated metadata parsing, or input files with missing data, all of which are supported by \textbf{quicR}.
+Its functions also require pre-cleaned and pre-structured input data, placing more burden on the user to prepare their dataset prior to analysis.
 
-            Overall, \textbf{quicR} favors flexibility, reproducibility, and usability with raw instrument output at the expense of execution speed—trade-offs that align with the package’s intended use in diagnostic pipelines.
+            \textbf{quicR} further distinguishes itself through its modular design: it allows users to calculate metrics such as MPR, MS, TtT, and RAF independently rather than as a bundled operation.
+While QuICSeedR includes built-in support for bulk analysis and diagnostic outputs, these workflows can be achieved in \textbf{quicR} using standard R idioms (e.g., the \texttt{apply} family of functions), and are planned for future releases.
+
+            Overall, \textbf{quicR} favors flexibility, reproducibility, and usability with raw instrument output at the expense of execution speed trade-offs that align with the package’s intended use in diagnostic pipelines.
 
@@
                     colspec   = {rccc}, 
+                    rows      = {rowsep = 1pt},
                     row{1}    = {font=\bfseries},
@@
                 \end{tblr}
-                \caption{Comparison of core features and execution times between \textbf{quicR} and \textbf{QuICSeedR}.
-While \textbf{QuICSeedR} demonstrates superior execution speed, \textbf{quicR} offers enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files.
-All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM).}
-                \label{tbl:benchmark}
+                \caption{Comparison of core features and execution times between \textbf{quicR}, QuICSeedR, and rtquicR.
+While QuICSeedR demonstrated the fastest overall execution times, \textbf{quicR} offered enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files.\ rtquicR introduces additional metrics such as SD50 and area under the curve but requires pre-structured input and lacks support for 384-well microplate formats and automated metadata parsing.
+All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM) in 50 replicates.}\label{tbl:benchmark}
             \end{table}

### 2025-05-28 man/manuscript/softwareX_submission.tex
Added a Reproducibility section.

@@
 
+        \subsection{Reproducibility}
+            To promote transparency and reproducibility, we provide a standardized benchmarking and data extraction script alongside the \textbf{quicR} package.
+This script processes raw RT-QuIC output files in MARS export format, computes key kinetic metrics (MPR, MS, TtT, RAF), and writes all intermediate and final results to CSV files.
+Users are instructed to run the script locally, generating three files (\texttt{<user>\_meta.csv}, \texttt{<user>\_data.csv}, and \texttt{<user>\_calcs.csv}) which were then compared across systems or submissions to ensure consistent performance.
+
+            To further guard against system-dependent variability, the script includes the following measures:
+
+            \begin{enumerate}
+                % \item Sorting of input and output data by sample ID to enforce deterministic row order;
+                \item Cross-platform user ID resolution to enable standardized filenames
+                \item Fixed random seed initialization to control for any stochastic components
+                \item Output of full session metadata via \texttt{sessionInfo()} to record package versions and platform details
+                \item UTF-8 encoding of all CSV files for consistent parsing across operating systems.
+            \end{enumerate}
+
+            This reproducibility framework ensures that benchmark results, as reported in Table~\ref{tbl:benchmark}, can be independently validated and extended.
+The script, along with example data, is included in the package repository and supplementary materials.
+
         \subsection{Maintenance and Community Involvement}

### 2025-05-28 man/manuscript/softwareX_submission.tex
Updated Community Involvement section.

@@
 The source code is hosted on GitHub (\url{https://github.com/gagerowden/quicR}), where users can report issues, request features, and contribute improvements via pull requests.
-A comprehensive \textbf{CONTRIBUTING.md} file and issue templates are provided to streamline collaboration and lower the barrier for external contributions.
+A comprehensive \textbf{CONTRIBUTING} file and issue templates are provided to streamline collaboration and lower the barrier for external contributions.
 In addition to continuous integration testing, we plan to tag releases with semantic versioning and maintain a changelog to track updates and improvements.

### 2025-05-28 man/manuscript/softwareX_submission.tex
Updated Illustrative examples section.

@@
 The reaction was performed on a FLUOstar Omega plate reader (BMG Labtech, Ortenberg, Germany).
-The file was exported as an Excel workbook where the metadata appears on the first sheet and the raw data on the second.
+The file was exported as an Excel workbook where the metadata appears on the first sheet and the raw data on the second sheet.
 
         \subsection{Example Code}
-            \# Step 1: Install and load the package\\
-            install.packages("quicR")\\
+            \# Step 1: Install and load the package.\\
+            install.packages(``quicR'')\\
             library(quicR)\\
             \# Step 2: Identify the raw file.\\
-            file <- "example.xlsx"\\
+            file <- ``example.xlsx''\\
             \# Step 3: Extract the raw data.\\
@@
 
-            Next, the metadata is extracted using the organize\_tables() and convert\_tables() functions.
+            Next, the metadata is extracted using organize\_tables() and convert\_tables().
 These take the metadata found on the first sheet of the Excel file and convert them into data frame columns.

### 2025-05-30 man/manuscript/reproducibility-study-quicR/analysis.R
Added the reproducibility study.

@@ -1,0 +1,53 @@
+install.packages("quicR")
+library(quicR)
+library(dplyr)
+
+
+
+user <- Sys.info()[["user"]]
+set.seed(45)
+
+files <- list.files("raw", ".xlsx", full.names = TRUE)
+
+get_data <- function(file) {
+  get_real(file)[[1]] %>%
+    normalize_RFU()
+}
+
+get_meta <- function(file) {
+  organize_tables(file) %>%
+    convert_tables()
+}
+
+meta <- lapply(files, get_meta) %>%
+  bind_rows() %>%
+  mutate(Dilutions = -log10(as.integer(Dilutions)))
+
+data <- lapply(files, get_data) %>%
+  bind_rows()
+
+calcs <- data.frame(
+  `Sample IDs` = meta$`Sample IDs`,
+  Dilutions = meta$Dilutions,
+  check.names = FALSE
+)%>%
+  mutate(
+    MPR = calculate_MPR(data),
+    MS  = calculate_MS(data),
+    TtT = calculate_TtT(data, 2),
+    TtT = ifelse(is.na(TtT), 72, TtT),
+    RAF = 1/TtT
+  )
+
+write.csv(meta,  paste0(user, "_meta.csv"),  row.names = FALSE, fileEncoding = "UTF-8")
+write.csv(data,  paste0(user, "_data.csv"),  row.names = FALSE, fileEncoding = "UTF-8")
+write.csv(calcs, paste0(user, "_calcs.csv"), row.names = FALSE, fileEncoding = "UTF-8")
+writeLines(capture.output(sessionInfo()), paste0(user, "_sessionInfo.txt"))
+
+
+
+
+
+
+
+

### 2025-05-30 man/manuscript/reproducibility-study-quicR/comparison.R

@@ -1,0 +1,63 @@
+library(dplyr)
+library(readr)
+library(purrr)
+
+# Set tolerance for numeric comparisons
+tolerance <- 1e-12
+
+# Load all user files (assumes pattern like Gage_meta.csv, Alice_meta.csv, etc.)
+files <- list.files("data", ".csv", full.names = TRUE)
+
+# Organize files into a list by user
+grouped <- files %>%
+  split(gsub("_(meta|data|calcs)\\.csv", "", .)) %>%
+keep(~ length(.x) == 3)  # Only keep complete sets
+
+compare_files <- function(user_files) {
+  meta <- read_csv(user_files[grep("_meta", user_files)], show_col_types = FALSE)
+  data <- read_csv(user_files[grep("_data", user_files)], show_col_types = FALSE)
+  calcs <- read_csv(user_files[grep("_calcs", user_files)], show_col_types = FALSE)
+  list(meta = meta, data = data, calcs = calcs)
+}
+
+# Load data for each user
+user_data <- map(grouped, compare_files)
+
+# Choose a reference user (first one alphabetically)
+reference_user <- names(user_data)[[1]]
+ref <- user_data[[reference_user]]
+
+# Function to compare two data frames
+compare_dfs <- function(df1, df2, df_name, user, tol = tolerance) {
+  if (!all(names(df1) == names(df2))) {
+    message(sprintf("❌ Column names mismatch in '%s' for user %s.", df_name, user))
+    return(FALSE)
+  }
+  if (!all(nrow(df1) == nrow(df2))) {
+    message(sprintf("❌ Row count mismatch in '%s' for user %s.", df_name, user))
+    return(FALSE)
+  }
+  is_equal <- map2_lgl(df1, df2, function(col1, col2) {
+    if (is.numeric(col1)) all(abs(col1 - col2) < tol, na.rm = TRUE)
+    else all(col1 == col2, na.rm = TRUE)
+  })
+  if (all(is_equal)) {
+    message(sprintf("✅ %s matches for user %s.", df_name, user))
+    return(TRUE)
+  } else {
+    mismatch_cols <- names(df1)[!is_equal]
+    message(sprintf("⚠️ Differences in columns of '%s' for user %s: %s",
+                    df_name, user, paste(mismatch_cols, collapse = ", ")))
+    return(FALSE)
+  }
+}
+
+# Compare each user against the reference
[…]

### 2025-05-30 man/manuscript/softwareX_submission.tex
Updated the manuscript with the reproducibility study.

@@
                 \begin{enumerate}
-                    \item \texttt{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
+                    \item \textbf{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
 Makes an 8$\times$12 or 16$\times$24 faceted plot depending on if the plate has 96 or 384 wells.
@@
                     Calculates metrics in bulk & Yes & Yes & No \\
-                    Calcualates MPR & Yes & Yes & Yes \\
+                    Calculates MPR & Yes & Yes & Yes \\
                     Calculates MS & Yes & Yes & No \\
@@
         \subsection{Reproducibility}
-            To promote transparency and reproducibility, we provide a standardized benchmarking and data extraction script alongside the \textbf{quicR} package.
-This script processes raw RT-QuIC output files in MARS export format, computes key kinetic metrics (MPR, MS, TtT, RAF), and writes all intermediate and final results to CSV files.
-Users are instructed to run the script locally, generating three files (\texttt{<user>\_meta.csv}, \texttt{<user>\_data.csv}, and \texttt{<user>\_calcs.csv}) which were then compared across systems or submissions to ensure consistent performance.
+            To evaluate the reproducibility of \textbf{quicR} across systems and users, we developed a standardized script that processes MARS output files and writes three key result CSV files: metadata, normalized fluorescence data, and calculated metrics as well as a plain-text file containing R session information (See Table \ref{tbl:comparisons}).
+This script was distributed, and users were only expected to source the script in the project folder.
+The files were compared between each user for inconsistencies.
+Numerical data were given a floating point tolerance of 1E\textsuperscript{-13}.
+Additionally, session summaries were parsed to extract R version, environment, and machine information.
+We did not observe any divergent results between any two users.
+A copy of the benchmarking script is available in the GitHub repository.
 
-            To further guard against system-dependent variability, the script includes the following measures:
-
-            \begin{enumerate}
-                % \item Sorting of input and output data by sample ID to enforce deterministic row order;
-                \item Cross-platform user ID resolution to enable standardized filenames
-                \item Fixed random seed initialization to control for any stochastic components
-                \item Output of full session metadata via \texttt{sessionInfo()} to record package versions and platform details
-                \item UTF-8 encoding of all CSV files for consistent parsing across operating systems.
-            \end{enumerate}
-
-            This reproducibility framework ensures that benchmark results, as reported in Table~\ref{tbl:benchmark}, can be independently validated and extended.
-The script, along with example data, is included in the package repository and supplementary materials.
+            \begin{table}[H]
+                \centering
+                \begin{tblr}{
+                    cells     = {font = \fontsize{10pt}{10pt}\selectfont},
+                    colspec   = {c c c c c}, 
+                    rows      = {rowsep = 1pt},
+                    row{1}    = {font=\bfseries\fontsize{10pt}{10pt}\selectfont},
+                    rowhead   = 1,
+                    width     = \textwidth
+                }
+                    \hline
+                    User & {R\\Version} & {quicR\\Version} & Platform & OS\\
+                    \hline
+                    1 & 4.4.3 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 26100) \\
+                    2 & 4.4.1 & 2.1.0 & aarch64-apple-darwin20  & macOS 15.5 \\
+                    3 & 4.4.3 & 2.1.0 & aarch64-apple-darwin20  & macOS Sequoia 15.5 \\
+                    4 & 4.5.0 & 2.1.0 & aarch64-apple-darwin20  & macOS Sonoma 14.7.5 \\
+                    5 & 4.4.3 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 26100) \\
+                    \hline
+                \end{tblr}
+                \caption{User session information.
+The script was run on both Windows and Mac machines with a variety of R versions.
+The quicR versions were kept identical to ensure reproducibility.}\label{tbl:comparisons}
+            \end{table}
 
@@
         \subsection{Example Code}
-            \# Step 1: Install and load the package.\\
+            \texttt{\# Step 1: Install and load the package.\\
             install.packages(``quicR'')\\
@@
             \# Step 9: Plot the plate view.\\
-            plate\_view(raw, locations)\\
+            plate\_view(raw, locations)\\}
 
@@
 We would like to acknowledge Suzanne Stone and Sarah Gresch for maintaining lab operations.
+We thank Sarah Gresch, Kendra Phelps, Laramie Lindsey, Miranda Huang, and Kristin Bondo for their participation in the reproducibility study.
 This work was funded by the Legislative-Citizen Commission on Minnesota Resources.

### 2025-06-02 man/manuscript/softwareX_submission.tex
Updated manuscript with new reproducibility data.

@@
         \subsection{Comparable Methods}
-            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, QuICSeedR\ \cite{Li2025}, and the unpublished rtquicR\ \cite{Slota2023}.
+            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, QuICSeedR\ \cite{Li2025}, and the unpublished package, rtquicR\ \cite{Slota2023}.
 While all three offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
@@
 
-            \textbf{quicR} further distinguishes itself through its modular design: it allows users to calculate metrics such as MPR, MS, TtT, and RAF independently rather than as a bundled operation.
+            \textbf{quicR} further distinguishes itself through its modular design, allowing users to calculate metrics such as MPR, MS, TtT, and RAF independently rather than as a bundled operation.
 While QuICSeedR includes built-in support for bulk analysis and diagnostic outputs, these workflows can be achieved in \textbf{quicR} using standard R idioms (e.g., the \texttt{apply} family of functions), and are planned for future releases.
@@
                     \hline
-                    Available on CRAN & Yes & Yes & No \\
+                    Available on CRAN & \textbf{Yes} & \textbf{Yes} & No \\
                     Number of input files required & 1 & 2 & 2 \\ 
@@
                     Number of normalization methods & 1 & 1 & 2 \\
-                    Automated metadata entry & Yes & No & No \\
-                    Automated sample locations & Yes & Yes & No \\
-                    Allows empty data & Yes & Yes & No \\
-                    Compatible with 384-well plates & Yes & Yes & No \\
-                    % Actively maintained & Yes & No \\
-                    Built-in bulk analysis support & No & Yes & Yes \\
-                    Diagnostic analysis functionality & No & Yes & No \\
-                    Incorporates dilution factors & Yes & No & Yes \\
-                    Converts time units & No & Yes & Yes \\
-                    Calculates metrics independently & Yes & No & Yes \\
-                    Calculates metrics in bulk & Yes & Yes & No \\
-                    Calculates MPR & Yes & Yes & Yes \\
-                    Calculates MS & Yes & Yes & No \\
-                    Calculates TtT & Yes & Yes & Yes \\
-                    Calculates RAF & Yes & Yes & No \\
-                    Calculates area under the curve & No & No & Yes \\
-                    Calculates SD50 & No & No & Yes \\
+                    Automated metadata entry & \textbf{Yes} & No & No \\
+                    Automated sample locations & \textbf{Yes} & \textbf{Yes} & No \\
+                    Allows empty data & \textbf{Yes} & \textbf{Yes} & No \\
+                    Compatible with 384-well plates & \textbf{Yes} & \textbf{Yes} & No \\
+                    % Actively maintained & \textbf{Yes} & No \\
+                    Built-in bulk analysis support & No & \textbf{Yes} & \textbf{Yes} \\
+                    Diagnostic analysis functionality & No & \textbf{Yes} & No \\
+                    Incorporates dilution factors & \textbf{Yes} & No & \textbf{Yes} \\
+                    Converts time units & No & \textbf{Yes} & \textbf{Yes} \\
+                    Calculates metrics independently & \textbf{Yes} & No & \textbf{Yes} \\
+                    Calculates metrics in bulk & \textbf{Yes} & \textbf{Yes} & No \\
+                    Calculates MPR & \textbf{Yes} & \textbf{Yes} & \textbf{Yes} \\
+                    Calculates MS & \textbf{Yes} & \textbf{Yes} & No \\
+                    Calculates TtT & \textbf{Yes} & \textbf{Yes} & \textbf{Yes} \\
+                    Calculates RAF & \textbf{Yes} & \textbf{Yes} & No \\
+                    Calculates area under the curve & No & No & \textbf{Yes} \\
+                    Calculates SD50 & No & No & \textbf{Yes} \\
                     \hline
@@
                     5 & 4.4.3 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 26100) \\
+                    6 & 4.4.3 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 26100) \\
                     \hline

### 2025-06-02 man/manuscript/softwareX_submission_v2.tex
Updated manuscript.

--- 2025-06-02 man/manuscript/softwareX_submission.tex
@@
 %% for the whole article with \linenumbers.
-% \usepackage{lineno}
+\usepackage{lineno}
 \usepackage{tabularray}
@@
 
-    % \linenumbers
+    \linenumbers
 
@@
                     Compatible with 384-well plates & \textbf{Yes} & \textbf{Yes} & No \\
-                    % Actively maintained & \textbf{Yes} & No \\
                     Built-in bulk analysis support & No & \textbf{Yes} & \textbf{Yes} \\
@@
                 \caption{Comparison of core features and execution times between \textbf{quicR}, QuICSeedR, and rtquicR.
-While QuICSeedR demonstrated the fastest overall execution times, \textbf{quicR} offered enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files.\ rtquicR introduces additional metrics such as SD50 and area under the curve but requires pre-structured input and lacks support for 384-well microplate formats and automated metadata parsing.
 All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM) in 50 replicates.}\label{tbl:benchmark}
@@
             To evaluate the reproducibility of \textbf{quicR} across systems and users, we developed a standardized script that processes MARS output files and writes three key result CSV files: metadata, normalized fluorescence data, and calculated metrics as well as a plain-text file containing R session information (See Table \ref{tbl:comparisons}).
-This script was distributed, and users were only expected to source the script in the project folder.
-The files were compared between each user for inconsistencies.
-Numerical data were given a floating point tolerance of 1E\textsuperscript{-13}.
+This script and accompanying raw data files were distributed, and users were instructed to source the script in the project directory.
+The output files were compared between each user for inconsistencies.
+Numerical data were given a floating point tolerance of 1E\textsuperscript{-12}.
 Additionally, session summaries were parsed to extract R version, environment, and machine information.
@@
 The source code is hosted on GitHub (\url{https://github.com/gagerowden/quicR}), where users can report issues, request features, and contribute improvements via pull requests.
-A comprehensive \textbf{CONTRIBUTING} file and issue templates are provided to streamline collaboration and lower the barrier for external contributions.
+A comprehensive \textbf{CONTRIBUTING} file and issue templates are provided to streamline collaboration and to facilitate external contributions.
 In addition to continuous integration testing, we plan to tag releases with semantic versioning and maintain a changelog to track updates and improvements.
-Feedback from diagnostic users has already led to enhancements in metadata parsing and output plotting, and we anticipate continued improvements through engagement with the broader scientific community.
 We encourage users to share their use cases, raise issues, and help shape future development directions.

### 2025-07-02 man/manuscript/softwareX_submission_v1.tex

--- 2025-05-28 man/manuscript/softwareX_submission.tex
@@
 \documentclass[preprint,12pt,a4paper]{elsarticle}
-
-% Quiet chktex warnings.
-% chktex-file 44
-% chktex-file 36
 
@@
 \begin{keyword}
-            Chronic Wasting Disease \sep{} Creutzfeldt-Jakob Disease \sep{} Nano-QuIC \sep{} RT-QuIC \sep{} prion diagnostics \sep{} Parkinson's Disease \sep{} seed amplification assay
+R package \sep{} RT-QuIC \sep{} Nano-QuIC \sep{} Micro-QuIC \sep{} prion \sep{} diagnostics \sep{} Creutzfeldt-Jakob \sep{} Chronic Wasting Disease \sep{} Parkinson's
 \end{keyword}
@@
 \begin{tabular}{lp{6cm}p{6cm}}
-            \hline
+\hline{}
 \textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata} \\
-            \hline
+\hline{}
 C1 & Current code version & V2.1.0 \\
+% \hline{}
 C2 & Permanent link to code/repository used for this code version & \url{https://github.com/gage1145/quicR/releases/tag/v2.1.0} \\
+% \hline{}
 C3  & Permanent link to Reproducible Capsule & \url{https://cran.r-project.org/web/packages/quicR}\\
+% \hline{}
 C4 & Legal Code License & GPL-3\\
+% \hline{}
 C5 & Code versioning system used & Git\\
+% \hline{}
 C6 & Software code languages, tools, and services used & R\\
+% \hline{}
 C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0)\\
+% \hline{}
 C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
+% \hline{}
 C9 & Support email for questions & rowde002@umn.edu\\
-            \hline
+\hline{}
 \end{tabular}
@@
 \section{Motivation and significance}
-        Real-time quaking induced conversion (RT-QuIC) is within the family of seed amplification assays (SAAs), similiar to protein misfolding cyclic amplification (PMCA), and has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates~\cite{Wilham2010, Atarashi2011}.
-The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed~\cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
-The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies~\cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
-However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation~\cite{Rowden2023}.
+Real-time quaking induced conversion (RT-QuIC) is a cutting-edge diagnostic assay that has garnered significant attention for its ultra-sensitive detection of misfolded protein aggregates \cite{Wilham2010, Atarashi2011}.
+The assay works by converting a recombinant protein substrate into an amyloid aggregate in the presence of a misfolded seed \cite{Wilham2010, Orru2012, Orru2017, Orru2015, Bongianni2019, Dassanayake2016, Hwang2018, Groveman2018, Metrick2020}.
+The assay's sensitivity and specificity make RT-QuIC a promising tool for diagnosing diseases such as prion disorders and other protein misfolding pathologies \cite{Fiorini2020, Franceschini2017, Picasso-Risso2022, Holz2021}.
+However, the relatively recent development and novelty of the assay have left a gap in widely accepted academic and industry standards for data analysis and interpretation \cite{Rowden2023}.
 
-        To address this gap, we introduce \textbf{quicR}, an open-source library, developed in R~\cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
-By consolidating key metrics and providing robust analytical tools, \textbf{quicR} aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC~\cite{Christenson2023} and Micro-QuIC~\cite{Lee2024}.\ \textbf{quicR} is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
+To address this gap, we introduce \textbf{quicR}, an open-source library, developed in R \cite{R2024}, dedicated to the cleaning, analysis, and visualization of RT-QuIC data.
+By consolidating key metrics and providing robust analytical tools, \textbf{quicR} aims to standardize the analysis pipeline and foster reproducibility within the field of quaking induced assays including related assays such as Nano-QuIC \cite{Christenson2023} and Micro-QuIC \cite{Lee2024}.
+\textbf{quicR} is designed with both researchers and diagnosticians in mind, providing a user-friendly interface that integrates seamlessly with existing R workflows.
 
-        While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics.
-These include:
+While universal diagnostic criteria for RT-QuIC have yet to be established, certain analytical metrics have emerged as valuable tools for interpreting assay results and kinetics. These include:
 
 \begin{enumerate}
-            \item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold (also known as lag time)~\cite{Orru2015}. 
-            \item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed~\cite{Gallups2022}.
-            \item Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities~\cite{Rowden2023}.
-            \item Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation~\cite{Henderson2015}.
+\item Time-to-threshold (TtT): The time required for the fluorescence signal to exceed a predefined threshold \cite{Orru2015}.
+\item Rate of amyloid formation (RAF): A measure of the kinetics of aggregate growth, which provides insight into the relative quantity of misfolded seed \cite{Gallups2022}.
+\item Maxpoint ratio (MPR): A ratio-based metric measuring peak normalized fluorescence intensities \cite{Rowden2023}.
+\item Maximum slope (MS): The steepest rate of fluorescence increase, reflecting the most rapid phase of aggregation \cite{Henderson2015}.
 \end{enumerate}
@@
 In addition to analytical tools, \textbf{quicR} provides flexible and customizable visualization capabilities.
-Leveraging the powerful ggplot2 library~\cite{ggplot2016}, \textbf{quicR} enables users to generate high-quality, publication-ready figures.
+Leveraging the powerful ggplot2 library \cite{ggplot2016}, \textbf{quicR} enables users to generate high-quality, publication-ready figures.
 These visualizations can be further customized using the intuitive `+' syntax of ggplot2, allowing for tailored presentations of RT-QuIC data.
@@
 \subsection{Software architecture}
-            \textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure~\ref{fig:workflow}).
+\textbf{quicR} was developed to address the growing need for efficient data conversion, analysis, and visualization of RT-QuIC data (Figure \ref{fig:workflow}).
 The overall architecture revolves around integration with the proprietary MARS software (BMG Labtech, Ortenberg, Germany) which exports raw data as Excel workbooks.
@@
 Orange nodes are functions which calculate some metric.
-Finally, yellow nodes represent data analysis endpoints.}\label{fig:workflow}
+Finally, yellow nodes represent data analysis endpoints.}
+\label{fig:workflow}
 \end{figure}
@@
 \subsubsection{Input of Sample IDs into Omega Control Software}
-                The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations.
-This file is uniquely formatted, and not easily reproduced manually.
+The Omega control software allows input of a TXT file containing sample IDs, dilution factors, and their well locations. This file is uniquely formatted, and not easily reproduced manually.
 
 \begin{enumerate}
-                    \item \textbf{BMG\_format()}: This function allows for input of a CSV file containing the plate layout (see Table~\ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
+\item \textbf{BMG\_format()}: This function allows for input of a CSV file containing the plate layout (see Table \ref{tbl:layout} for proper formatting), and exports the formatted TXT file.
 The file can then be imported into the Omega control software before running.
@@
 The top left corner is cell ``A1'' in the CSV file.
-The top numbered row and the left-most lettered column should never be altered.}\label{tbl:layout}
+The top numbered row and the left-most lettered column should never be altered.}
+\label{tbl:layout}
 \end{table}
@@
 Those tables include the ``Sample IDs'' and ``Dilutions'' tables (if dilutions were included in the MARS export).
-For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\ If there is no table, the user can simply add it manually.
+For much of the downstream analysis, it is crucial that the ``Sample IDs'' table was exported from MARS.\@ If there is no table, the user can simply add it manually.
 
@@
 \item \textbf{convert\_tables()}: accepts tables outputted from organize\_tables() and converts them to columns in a data frame.
-                    \item \textbf{get\_sample\_locations()}: extracts the well locations for each sample.
-Output of this function is used as an argument for visualizing a microplate-level view of real-time data.
+\item \textbf{get\_sample\_locations()}: extracts the well locations for each sample. Output of this function is used as an argument for visualizing a microplate-level view of real-time data.
 \end{enumerate}
@@
 \subsubsection{Retrieving and Manipulating Raw Data}
-                The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS.\ There are three functions dedicated to the retrieval and cleaning of raw data.
+The raw, real-time data is typically found on the second sheet of the Excel workbook exported from MARS. There are three functions dedicated to the retrieval and cleaning of raw data.
 
@@
 \subsubsection{Calculations}
-                Three analytical metrics have dedicated functions: TtT, MPR, and MS.\ RAF does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
+Three analytical metrics have dedicated functions: TtT, MPR, and MS.
+RAF does not have a designated function since it is simply the reciprocal of the time-to-threshold (1/TtT).
 However, it can be calculated using the calculate\_metrics() function if TtT is chosen as an optional parameter.
 Each function below accepts input from the transpose\_real() or the normalize\_RFU() functions.
-See Figure~\ref{fig:metrics} for an example of the output of these functions.
+See Figure \ref{fig:metrics} for an example of the output of these functions.
 
@@
 This threshold can be supplied by calculate\_threshold() or determined separately by the user.
-                    \item \textbf{calculate\_MPR()}: accepts raw or normalized data and returns the maximum value obtained during the run.
-If supplied with raw data, it will make a call to the normalize\_RFU() function.
+\item \textbf{calculate\_MPR()}: accepts raw or normalized data and returns the maximum value obtained during the run. If supplied with raw data, it will make a call to the normalize\_RFU() function.
 \item \textbf{calculate\_MS()}: computes the approximate derivative of the real-time data and returns the maximum value obtained during the run.
-                    \item \textbf{calculate\_metrics()}: makes a call to functions 2--4 above and generates a data frame with the sample-matched metrics.
-Also computes RAF if TtT is given as an argument.
+\item \textbf{calculate\_metrics()}: makes a call to functions 2--4 above and generates a data frame with the sample-matched metrics. Also computes RAF if TtT is given as an argument.
 \end{enumerate}
@@
 Time‐to‐threshold is determined as the time required to cross a given threshold (in this example, the threshold is set at 0.2).
-The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.}\label{fig:metrics}
+The blue curve represents the derivative of the raw data, and max slope is determined as the maximum of the derivative.}
+\label{fig:metrics}
 \end{figure}
@@
 \begin{enumerate}
-                    \item \texttt{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
+\item \textbf{plate\_view()}: accepts the output from the get\_real() function and get\_sample\_locations() function.
 Makes an 8$\times$12 or 16$\times$24 faceted plot depending on if the plate has 96 or 384 wells.
@@
 
-        \subsection{Comparable Methods}
-            To contextualize the functionality and performance of \textbf{quicR}, we compared it with existing RT-QuIC analysis approaches from the published R package, QuICSeedR\ \cite{Li2025}, and the unpublished rtquicR\ \cite{Slota2023}.
-While all three offer overlapping core functionalities, their design philosophies, input handling, and computational trade-offs differ substantially.
-
-            Benchmarking was performed using the rbenchmark library~\cite{rbenchmark} with 50 replications for each function.
-Comparisons are approximate, as equivalent functions were not necessarily found between the three packages.
-Results are summarized in Table~\ref{tbl:benchmark}.
-In general, QuICSeedR\ demonstrates the fastest execution times across most core functions.
-However, \textbf{quicR} addresses several practical limitations that the authors believe justify the slower performance in some areas.
-Notably, QuICSeedR requires an additional, manually formatted Excel file to input sample metadata, whereas \textbf{quicR} directly parses both raw and meta data embedded within a single MARS export file.
-This design reduces user overhead and minimizes the potential for transcription errors.
-
-            The rtquicR\ package introduces support for additional thresholding methods and normalization strategies, and uniquely includes features such as SD50 and area-under-the-curve calculations.
-However, it does not currently support 384-well plate layouts, automated metadata parsing, or input files with missing data, all of which are supported by \textbf{quicR}.
-Its functions also require pre-cleaned and pre-structured input data, placing more burden on the user to prepare their dataset prior to analysis.
-
-            \textbf{quicR} further distinguishes itself through its modular design: it allows users to calculate metrics such as MPR, MS, TtT, and RAF independently rather than as a bundled operation.
-While QuICSeedR includes built-in support for bulk analysis and diagnostic outputs, these workflows can be achieved in \textbf{quicR} using standard R idioms (e.g., the \texttt{apply} family of functions), and are planned for future releases.
-
-            Overall, \textbf{quicR} favors flexibility, reproducibility, and usability with raw instrument output at the expense of execution speed trade-offs that align with the package’s intended use in diagnostic pipelines.
-
-            \begin{table}[H]
-                \centering
-                \begin{tblr}{
-                    cells     = {font = \fontsize{11pt}{11pt}\selectfont},
-                    colspec   = {rccc}, 
-                    rows      = {rowsep = 1pt},
-                    row{1}    = {font=\bfseries},
-                    rowhead   = 1,
-                    width     = \textwidth
-                }
-                    \hline
-                    \SetCell[c=1]{c}Feature / Benchmark & \textbf{quicR} & \textbf{QuICSeedR} & \textbf{rtquicR} \\ 
-                    \hline
-                    Available on CRAN & Yes & Yes & No \\
-                    Number of input files required & 1 & 2 & 2 \\ 
-                    Number of threshold methods & 2 & 3 & 4 \\
-                    Number of normalization methods & 1 & 1 & 2 \\
-                    Automated metadata entry & Yes & No & No \\
-                    Automated sample locations & Yes & Yes & No \\
-                    Allows empty data & Yes & Yes & No \\
-                    Compatible with 384-well plates & Yes & Yes & No \\
-                    % Actively maintained & Yes & No \\
-                    Built-in bulk analysis support & No & Yes & Yes \\
-                    Diagnostic analysis functionality & No & Yes & No \\
-                    Incorporates dilution factors & Yes & No & Yes \\
-                    Converts time units & No & Yes & Yes \\
-                    Calculates metrics independently & Yes & No & Yes \\
-                    Calculates metrics in bulk & Yes & Yes & No \\
-                    Calcualates MPR & Yes & Yes & Yes \\
-                    Calculates MS & Yes & Yes & No \\
-                    Calculates TtT & Yes & Yes & Yes \\
-                    Calculates RAF & Yes & Yes & No \\
-                    Calculates area under the curve & No & No & Yes \\
-                    Calculates SD50 & No & No & Yes \\
-                    \hline
-                    Plate view plot execution time (s) & 0.082 & 0.062 & NA \\
-                    Metric plot execution time (s) & 0.009 & 0.005 & 0.007 \\
-                    Metric calculations (MPR, MS, etc.) (s) & 0.355 & 0.018 & NA\\
-                    MPR calculation (s) & 0.002 & NA & 0.028 \\
-                    TtT calculation (s) & 0.001 & NA & 0.131 \\
-                    Metadata parsing time (s) & 0.127 & 0.037 & NA \\
-                    Raw data parsing time (s) & 0.069 & 0.050 & 0.191 \\
-                    Bulk analysis (s/file) & 6.550 & 0.849 & 1.986 \\
-                    \hline
-                \end{tblr}
-                \caption{Comparison of core features and execution times between \textbf{quicR}, QuICSeedR, and rtquicR.
-While QuICSeedR demonstrated the fastest overall execution times, \textbf{quicR} offered enhanced metadata handling, metric flexibility, and support for unprocessed instrument output files.\ rtquicR introduces additional metrics such as SD50 and area under the curve but requires pre-structured input and lacks support for 384-well microplate formats and automated metadata parsing.
-All benchmarks were performed using the same dataset and machine (Windows 11, 16GB RAM) in 50 replicates.}\label{tbl:benchmark}
-            \end{table}
-
-        \subsection{Reproducibility}
-            To promote transparency and reproducibility, we provide a standardized benchmarking and data extraction script alongside the \textbf{quicR} package.
-This script processes raw RT-QuIC output files in MARS export format, computes key kinetic metrics (MPR, MS, TtT, RAF), and writes all intermediate and final results to CSV files.
-Users are instructed to run the script locally, generating three files (\texttt{<user>\_meta.csv}, \texttt{<user>\_data.csv}, and \texttt{<user>\_calcs.csv}) which were then compared across systems or submissions to ensure consistent performance.
-
-            To further guard against system-dependent variability, the script includes the following measures:
-
-            \begin{enumerate}
-                % \item Sorting of input and output data by sample ID to enforce deterministic row order;
-                \item Cross-platform user ID resolution to enable standardized filenames
-                \item Fixed random seed initialization to control for any stochastic components
-                \item Output of full session metadata via \texttt{sessionInfo()} to record package versions and platform details
-                \item UTF-8 encoding of all CSV files for consistent parsing across operating systems.
-            \end{enumerate}
-
-            This reproducibility framework ensures that benchmark results, as reported in Table~\ref{tbl:benchmark}, can be independently validated and extended.
-The script, along with example data, is included in the package repository and supplementary materials.
-
-        \subsection{Maintenance and Community Involvement}
-            The \textbf{quicR} package is developed with long-term maintainability and community engagement in mind.
-The source code is hosted on GitHub (\url{https://github.com/gagerowden/quicR}), where users can report issues, request features, and contribute improvements via pull requests.
-A comprehensive \textbf{CONTRIBUTING} file and issue templates are provided to streamline collaboration and lower the barrier for external contributions.
-In addition to continuous integration testing, we plan to tag releases with semantic versioning and maintain a changelog to track updates and improvements.
-Feedback from diagnostic users has already led to enhancements in metadata parsing and output plotting, and we anticipate continued improvements through engagement with the broader scientific community.
-We encourage users to share their use cases, raise issues, and help shape future development directions.
-
 \section{Illustrative examples}
@@
 The reaction was performed on a FLUOstar Omega plate reader (BMG Labtech, Ortenberg, Germany).
-The file was exported as an Excel workbook where the metadata appears on the first sheet and the raw data on the second sheet.
+The file was exported as an Excel workbook where the metadata appears on the first sheet and the raw data on the second.
 
 \subsection{Example Code}
-            \# Step 1: Install and load the package.\\
-            install.packages(``quicR'')\\
-            library(quicR)\\
-            \# Step 2: Identify the raw file.\\
-            file <- ``example.xlsx''\\
-            \# Step 3: Extract the raw data.\\
+\# Step 1: Identify the raw file.\\
+file <- "example.xlsx"\\
+\# Step 2: Extract the raw data.\\
 raw <- get\_real(file)[[1]]\\
-            \# Step 4: Normalize the data against the background.\\
+\# Step 3: Normalize the data against the background.\\
 normal <- normalize\_RFU(raw, transposed = FALSE)\\
-            \# Step 5: Extract the metadata.\\
+\# Step 4: Extract the metadata.\\
 meta <- organize\_tables(file) |> convert\_tables()\\
-            \# Step 6: Get sample locations.\\
+\# Step 5: Get sample locations.\\
 locations <- get\_sample\_locations(file)\\
-            \# Step 7: Create the analyzed data frame.\\
+\# Step 6: Create the analyzed data frame.\\
 analyzed <- calculate\_metrics(normal, meta)\\
-            \# Step 8: Plot the analyzed data frame.\\
+\# Step 7: Plot the analyzed data frame.\\
 plot\_metrics(analyzed)\\
-            \# Step 9: Plot the plate view.\\
+\# Step 8: Plot the plate view.\\
 plate\_view(raw, locations)\\
 
-            Once the file name is identified, get\_real() is used to extract the raw data.
+Once the file name is identified, the get\_real() function is used to extract the raw data.
 This data is imported as a data frame with each sample designated as an individual column and the first column designated as time.
-Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to normalize\_RFU()~\cite{Rowden2023}.
+Much of the downstream analysis works best with background-normalized data, so the raw data is then passed to the normalize\_RFU() function \cite{Rowden2023}.
 This function accepts an integer as an argument for the desired cycle to be selected for background measurement.
 
-            Next, the metadata is extracted using organize\_tables() and convert\_tables().
+Next, the metadata is extracted using the organize\_tables() and convert\_tables() functions.
 These take the metadata found on the first sheet of the Excel file and convert them into data frame columns.
@@
 Once the proper variables have been defined, they can be used as input in the visualization functions.
-The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as Figure~\ref{fig:boxplot}.
-Additionally, the raw data and sample locations are used to plot the plate view as in Figure~\ref{fig:plateview}.
+The analyzed data frame can be used as an argument in plot\_metrics() to generate a plot such as Figure \ref{fig:boxplot}.
+Additionally, the raw data and sample locations are used to plot the plate view as in Figure \ref{fig:plateview}.
 
@@
 \includegraphics[width=\textwidth]{images/boxplot.png}
-                \caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}\label{fig:boxplot}
+\caption{Boxplot of the four critical metrics calculated by the \textbf{quicR} package.}
+\label{fig:boxplot}
 \end{figure}
@@
 \includegraphics[width=\textwidth]{images/plate_view.png}
-                \caption{Plate view of RT-QuIC.\ Wells are identified with a sample ID and dilution factor separated by an optional delimiter (in this case, a whitespace).}\label{fig:plateview}
+\caption{Plate view of RT-QuIC. Wells are identified with a sample ID and dilution factor separated by an optional delimiter (in this case, a whitespace).}
+\label{fig:plateview}
 \end{figure}
@@
 \section{Impact}
-        Since its development in 2010~\cite{Wilham2010,Atarashi2011}, the utility of RT-QuIC has expanded to a host of neurodegenerative diseases caused by prions and other misfolded proteins~\cite{Orru2024,ALWAKIL202597,Wang2024}.
-The improved speed and accuracy of the assay has been a boon to human health~\cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts~\cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
+Since its development in 2010 \cite{Wilham2010,Atarashi2011}, the utility of RT-QuIC has expanded to a host of neurodegenerative diseases caused by prions and other misfolded proteins \cite{Orru2024,ALWAKIL202597,Wang2024}.
+The improved speed and accuracy of the assay has been a boon to human health \cite{Orru2015,green2019rt,race2019transmission,vascellari2022real} and animal management efforts \cite{huang2025chronic,cooper2019detection,piel2024validation,harpaz2024transmission}.
 Thus, it is imperative that standardized practices and analyses are adopted.
@@
 The \textbf{quicR} package represents a significant advancement in the standardization and reproducibility of RT-QuIC data analysis.
-By integrating key metrics such as TtT~\cite{Orru2015}, RAF~\cite{Gallups2022}, MPR~\cite{Rowden2023}, and MS~\cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
+By integrating key metrics such as TtT \cite{Orru2015}, RAF \cite{Gallups2022}, MPR \cite{Rowden2023}, and MS \cite{Henderson2015}, \textbf{quicR} addresses critical gaps in the field, providing researchers and diagnosticians with a robust toolkit for interpreting RT-QuIC data.
 
 One of the primary strengths of \textbf{quicR} lies in its streamlined workflow and user-centric design.
-The package leverages R’s powerful ecosystem and the tidyverse~\cite{tidyverse2019} to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users.
+The package leverages R’s powerful ecosystem and the tidyverse \cite{tidyverse2019} to create high-quality, customizable visualizations, ensuring accessibility for a wide range of users.
 Additionally, the incorporation of open-source principles allows the broader scientific community to contribute to its development, fostering innovation and adaptability.
@@
 
-        Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.\ \textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and diagnostic interpretations remains a challenge for the field~\cite{Rowden2023}.
+Another avenue for improvement lies in the standardization of RT-QuIC diagnostic criteria.
+\textbf{quicR} provides tools to calculate key metrics, but consensus on thresholds and diagnostic interpretations remains a challenge for the field \cite{Rowden2023}.
 Collaborative efforts among researchers and clinicians are necessary to define universal criteria, enabling \textbf{quicR} to fully realize its potential as a diagnostic tool.
@@
 \section*{Acknowledgements}
-        Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.\ We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
+Special thanks to Beni Altmann at The Comprehensive R Archive Network (CRAN) for help during the submission process to CRAN.
+We thank Tiffany Wolf and Marc Schwabenlander for their support through the Minnesota Center for Prion Research and Outreach.
 We thank Miranda Huang and Kristin Bondo for testing the code.

### 2025-09-04 R/get_real.R
Updated get_real to incorporate transposition and normalization.

@@ -3,14 +3,15 @@
 #' Accepts an Excel file or a dataframe of real-time RT-QuIC data.
 #'
 #' @param data Either an Excel file or a dataframe.
-#' @param ordered Logical, if true, will organize the columns by sample ID rather than by well.
+#' @param order_by_sample Logical, if true, will organize the columns by sample ID rather than by well.
+#' @param transpose_table Logical, if true, will transpose the table(s).
 #'
 #' @return A list of dataframes containing the formatted real-time data.
 #'
 #' @importFrom dplyr select
 #' @importFrom dplyr %>%
 #' @importFrom dplyr rename
-#' @importFrom readxl read_excel
+#' @importFrom readxl read_xlsx
 #' @importFrom janitor row_to_names
 #' @importFrom janitor clean_names
 #'
@@ -23,14 +24,14 @@
 #' get_real(file)
 #'
 #' @export
-get_real <- function(data, ordered = FALSE) {
+get_real <- function(data, order_by_sample = FALSE, transpose_table = TRUE) {
   check_format <- function(x) {
     if (is.character(x)) {
-      return(suppressMessages(read_excel(x, sheet = 2, col_names = FALSE)))
+      return(suppressMessages(read_xlsx(x, sheet = 2, col_names = FALSE)))
     } else if (is.data.frame(x)) {
       return(x)
     } else {
-      stop("Please enter either .xlsx string or dataframe. ")
+      stop("Please enter either .xlsx file path or data frame. ")
     }
   }
 
@@ -42,7 +43,7 @@ get_real <- function(data, ordered = FALSE) {
       clean_names() %>%
       rename("Time" = 1) %>%
       {
-        if (ordered) {
+        if (order_by_sample) {
           select(., "Time", order(colnames(.[colnames(.) != "Time"])))
         } else {
           .
@@ -70,5 +71,23 @@ get_real <- function(data, ordered = FALSE) {
     return(df_list)
   }
 
-  return(split_real_time(curate(check_format(data))))
+  transpose_real <- function(data) {
+    colnames(data) %>%
+      rbind(data) %>%
+      unname() %>%
+      t() %>%
+      as.data.frame() %>%
+      row_to_names(1) %>%
+      rename("Sample IDs" = "Time") %>%
+      mutate_at(-c(1), function(y) as.numeric(as.character(y)))
+  }
+
+  return(
+    data %>%
+      check_format() %>%
+      curate() %>%
[…]

### 2025-09-04 R/calculate_MPR.R
Vastly improved MPR and TtT calculation speeds.

@@ -3,33 +3,23 @@
 #' Maxpoint ratio is defined as the maximum relative fluorescence divided by the
 #' background fluorescence.
 #'
-#' @param data A dataframe containing the real-time fluorescence data.
-#' @param start_col Integer, the column at which the background fluorescence should be read.
-#' @param data_is_norm Logical, if the data has not been normalized, will make a call to normalize_RFU.
-#' @return A vector containing MPR values.
+#' @param data A data frame output from 'get_quic()'.
+#' @param col The column containing the normalized fluorescence data.
+#' @param .by Grouping factor. Should typically be by individual wells.
+#' @return A data frame containing well-matched MPR values.
 #'
-#' @importFrom dplyr select
-#' @importFrom dplyr %>%
+#' @importFrom dplyr summarize
 #'
 #' @examples
-#' # This test takes >5 sec
-#' \donttest{
 #' file <- system.file(
 #'   "extdata/input_files",
 #'   file = "test.xlsx",
 #'   package = "quicR"
 #' )
-#' df_ <- quicR::get_real(file)[[1]]
-#' print(calculate_MPR(df_))
-#' }
+#' get_quic(file) |>
+#'   calculate_MPR()
 #'
 #' @export
-calculate_MPR <- function(data, start_col = 3, data_is_norm = TRUE) {
-  data %>%
-    {
-      if (data_is_norm) . else quicR::normalize_RFU(.)
-    } %>%
-    select(start_col:ncol(.)) %>%
-    apply(1, max) %>%
-    return()
+calculate_MPR <- function(data, col="Norm", .by="Wells") {
+  summarize(data, MPR = max(!!sym(col)), .by=.by)
 }

### 2025-09-04 R/calculate_TtT.R

@@ -4,62 +4,45 @@
 #'
 #' @param data A dataframe containing real-time RT-QuIC data.
 #' @param threshold A numeric value defining the threshold.
-#' @param start_col The column containing the starting position of the real-time data.
+#' @param time Column containing your time values.
+#' @param values Column containing your fluorescence values.
+#' @param .by Grouping factor. Should typically be by individual wells.
 #'
 #' @return A vector containing the times to threshold
 #'
+#' @importFrom dplyr group_by
+#' @importFrom dplyr rename
+#' @importFrom dplyr mutate_at
+#' @importFrom dplyr summarize
+#' @importFrom dplyr select
+#' @importFrom purrr is_empty
+#'
 #' @examples
-#' # This test takes >5 sec
-#' \donttest{
 #' file <- system.file(
 #'   "extdata/input_files",
 #'   file = "test2.xlsx",
 #'   package = "quicR"
 #' )
-#' get_real(file)[[1]] |>
-#'   quicR::normalize_RFU() |>
+#' get_quic(file) |>
 #'   calculate_TtT(threshold = 2)
-#' }
 #'
 #' @export
-calculate_TtT <- function(data, threshold, start_col = 3) {
-  # Get numeric cycle times
-  cycles <- as.numeric(colnames(data)[start_col:ncol(data)])
-  cycle_interval <- diff(cycles[1:2])  # assumes uniform intervals
+calculate_TtT <- function(data, threshold, time="Time", values="Norm", .by="Wells") {
 
-  # Extract just the numeric matrix portion
-  readings <- as.matrix(data[, start_col:ncol(data)])
+  dt <- data$Time[2] - data$Time[1]
 
-  # Apply function across rows
-  TtT <- apply(
-    readings,
-    1,
-    function(row) {
-      # Find first index where threshold is crossed
-      cross_idx <- which(row >= threshold)[1]
-
-      if (!is.na(cross_idx)) {
-        if (cross_idx == 1) {
-          return(cycles[1])  # threshold met at first timepoint
-        }
-
-        # Linear interpolation
-        prev <- row[cross_idx - 1]
-        curr <- row[cross_idx]
-        slope <- curr - prev
-
-        if (slope == 0) return(cycles[cross_idx])  # avoid division by zero
-
-        delta_threshold <- threshold - prev
[…]

### 2025-09-05 .example_scripts/BMG_format.R
updated gitignore

@@ -1,17 +1,0 @@
-# This script takes an .csv file plate layout and formats it into a .txt file
-# that can be imported into the BMG control software.
-
-# See "formatted.txt" in the BMG formatting folder for the output example.
-# See "plate_layout.csv" in the BMG formatting folder for input file example.
-
-
-
-library(quicR)
-
-
-
-# Use plate_layout.csv in the Desktop.
-setwd("C:/Users/Priogen/Desktop")
-file <- "plate_layout.csv"
-
-BMG_format(file) |> writeLines("formatted.txt")

### 2025-09-05 .example_scripts/calculate_metrics.R

@@ -1,252 +1,0 @@
-library(ggpubr)
-library(openxlsx)
-library(agricolae)
-library(tidyverse)
-library(quicR)
-
-
-
-# Initialize the file and read in the data --------------------------------
-
-
-
-# For testing, use "test".
-# Request the user to input the file name for analysis.
-file <- ""
-while (file == "") {
-  file <- paste0(
-    readline(
-      "Please input the Excel file name without .xlsx extension: "
-    ),
-    ".xlsx"
-  )
-  if (!file.exists(file)) {
-    print(paste(file, "does not exist. Please enter a valid file name."))
-    file <- ""
-  }
-}
-
-# Ask the user for the threshold.
-threshold <- "Please enter the desired threshold for RAF calculation: " %>%
-  readline() %>%
-  as.integer()
-
-
-
-# Identify the raw real-time data -----------------------------------------
-
-
-
-# Get the real-time data from the BMG export file.
-df <- quicR::get_real(file, ordered = FALSE)
-
-# Ask the user which real-time data set they want to use.
-df_id <- ifelse(
-  length(df) > 1,
-  paste(
-    "There are",
-    length(df),
-    "real-time data sets. Please enter a number in that range: "
-  ) %>%
-    readline() %>%
-    as.integer(),
-  1
-)
-
-# Select the real-time data set that the user signified.
-df <- df[[df_id]]
-
-
-
-# Get the metadata of each sample -----------------------------------------
-
-
-
-# Export the tables in the first sheet of the file.
-dic <- file %>%
-  quicR::organize_tables() %>%
-  quicR::convert_tables()
-
-
-
-# Calculate the normalized real-time data ---------------------------------
-
-
-
-df_norm <- df %>%
-  transpose_real() %>%
-  normalize_RFU(transposed = TRUE)
-
-
-
-# Add dilution factors if applicable ---------------------------------------
-
-
-
-# Determine if there is a dilutions table.
-dilution_bool <- "Dilutions" %in% names(dic)
-
-
-
-# Calculate the relevant metrics ------------------------------------------
-
-
-
-# Define the number of hours that the rxn ran for.
[…]

### 2025-09-05 .example_scripts/plate_view_export.R

@@ -1,85 +1,0 @@
-# require(readxl)
-require(tidyverse)
-require(quicR)
-
-
-
-# Initialize parameters for downstream functions. -------------------------
-
-
-
-file <- ""
-while (file == "") {
-  file <- paste0(
-    readline("Please input .xlsx file name WITHOUT extension: "),
-    ".xlsx"
-  )
-  if (!(file.exists(file))) {
-    print("File does not exist. Please ensure file name was typed correctly")
-    file <- ""
-  }
-}
-
-plate <- 0
-while (plate == 0) {
-  plate <- as.integer(readline("Please enter 96 or 384 for plate type: "))
-  if (plate != 96 & plate != 384) {
-    plate <- 0
-  }
-}
-
-
-
-# Following block exports the plate view figure. --------------------------
-
-
-
-# Define the layout using the first sheet in the excel file.
-# The sheet should be formatted so that each ID in the "layout" table is unique.
-df_dic <- quicR::organize_tables(file, plate = plate)
-
-# Determine if there is a dilutions table.
-dilution_bool <- "Dilutions" %in% names(df_dic)
-
-# Read in the real-time data.
-# get_real will return a list of dataframes depending on how many real-time
-# measurements the user exported from MARS.
-df_ <- quicR::get_real(file, ordered = FALSE)
-
-df_id <- ifelse(
-  length(df_) > 1,
-  as.integer(
-    readline(
-      paste(
-        "There are",
-        length(df_),
-        "real-time data sets. Please enter a number in that range: "
-      )
-    )
-  ),
-  1
-)
-
-df_ <- df_[[df_id]] %>%
-  as.data.frame()
-
-sample_locations <- get_sample_locations(
-  file = file,
-  tab_name = "Sample IDs",
-  dilution_bool = dilution_bool,
-  dilution_fun = function(x) -log10(x),
-  sep = "\n",
-  plate = plate
-)
-
-
-
-# Run plate_view function which produces a plate view figure. -------------
-
-
-
-quicR::plate_view(df_, sample_locations, plate) +
-  ggtitle(str_split_i(file, "\\.", 1)) +
-  theme(plot.title = element_text(hjust = 0.5))
-
-ggsave("plate_view.png", width = 3600, height = 2400, units = "px")

### 2025-09-05 R/BMG_format.R

@@ -1,95 +1,0 @@
-#' Format Table for BMG Sample ID Import
-#'
-#' BMG_format accepts a plate layout .CSV file and formats the Sample IDs into
-#' a format which can be easily imported into the BMG control software.
-#'
-#' @param file A .CSV file containing the plate layout of Sample IDs.
-#' @param save_path The path to the directory that you want the file saved.
-#' @param save_name The name of the output file. Should have the ".txt" extension.
-#' @param write_file Logical. If true, function will write a .txt file; otherwise it will return a character vector.
-#'
-#' @return A text file containing information for import into the BMG control software.
-#'
-#' @importFrom utils read.csv
-#' @importFrom dplyr mutate
-#' @importFrom dplyr select
-#' @importFrom dplyr left_join
-#' @importFrom tidyr unite
-#' @importFrom stats na.omit
-#' @importFrom reshape2 melt
-#'
-#' @examples
-#' layout_file <- system.file(
-#'   "extdata/BMG_formatting",
-#'   file = "plate_layout.csv",
-#'   package = "quicR"
-#' )
-#' BMG_format(layout_file)
-#'
-#' @export
-BMG_format <- function(file, save_path = "", save_name = "formatted.txt", write_file = FALSE) {
-  df_ <- read.csv(file, header = F)
-  colnames(df_) <- c("col", df_[1, -1])
-  df_ <- df_[-1, ]
-
-  locations <- c()
-  samples <- c()
-  for (i in 1:(ncol(df_) - 1)) {
-    for (j in 1:nrow(df_)) {
-      locations <- rbind(locations, paste0(LETTERS[j], i))
-      samples <- rbind(samples, df_[j, (i + 1)])
-    }
-  }
-
-  locations <- locations |>
-    cbind(samples) |>
-    as.data.frame()
-
-  colnames(locations) <- c("Wells", "Samples")
-
-  dic <- df_ |>
-    melt(id.vars = 1) |>
-    unique() |>
-    mutate(Plate_ID = "X") |>
-    na.omit() |>
-    unite("Wells", c("col", "variable"), sep = "")
-
-  x <- 0
-  previous <- dic[["value"]][1]
-  current <- ""
-  for (i in 1:nrow(dic)) {
-    current <- dic[["value"]][i]
-    if (tolower(current) == "n") {
-      dic[i, "Plate_ID"] <- "N"
-    } else if (tolower(current) == "p") {
[…]

### 2025-09-05 R/add_reps.R

@@ -1,25 +1,0 @@
-#' Add replicates
-#'
-#' Adds replicate information to the sample IDs. Well IDs should be formatted
-#' like so: A4, B9, H11, J24
-#'
-#' @param df A dataframe containing two columns for well IDs and Sample IDs
-#' @param sep a character string to separate the terms.
-#' @return A dataframe with replicate numbers pasted to the Sample IDs
-#'
-#' @export
-add_reps <- function(df, sep = "_") {
-  if (ncol(df) > 2) {
-    stop("Dataframe should only have two columns with well IDs and Sample IDs.")
-  }
-  df[, "C"] <- NA
-  count_list <- list()
-  for (i in 1:nrow(df)) {
-    samp <- df[i, 2]
-    count_list <- append(count_list, samp)
-    df[i, 3] <- sum(count_list == samp)
-  }
-  df[, "B"] <- paste(df$B, df$C, sep = sep)
-  df <- df[, 1:2]
-  return(df)
-}

### 2025-09-05 R/calculate_MPR.R

@@ -1,25 +1,0 @@
-#' Calculate the Maxpoint Ratio
-#'
-#' Maxpoint ratio is defined as the maximum relative fluorescence divided by the
-#' background fluorescence.
-#'
-#' @param data A data frame output from 'get_quic()'.
-#' @param col The column containing the normalized fluorescence data.
-#' @param .by Grouping factor. Should typically be by individual wells.
-#' @return A data frame containing well-matched MPR values.
-#'
-#' @importFrom dplyr summarize
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' get_quic(file) |>
-#'   calculate_MPR()
-#'
-#' @export
-calculate_MPR <- function(data, col="Norm", .by="Wells") {
-  summarize(data, MPR = max(!!sym(col)), .by=.by)
-}

### 2025-09-05 R/calculate_MS.R

@@ -1,63 +1,0 @@
-#' Calculate Maximum Slope
-#'
-#' Uses a sliding window to calculate the slope of real-time reads.
-#'
-#' @param data A dataframe containing real-time reads. It is recommended to use a dataframe made from normalize_RFU.
-#' @param window Integer designating how wide you want the sliding window to be for calculating the moving average slope.
-#' @param data_is_norm Logical; if FALSE, will make a call to normalize_RFU.
-#'
-#' @return A dataframe containing the real-time slope values as change in RFU/sec.
-#'
-#' @importFrom slider slide_dbl
-#' @importFrom purrr map_dbl
-#' @importFrom dplyr mutate_all
-#' @importFrom dplyr mutate
-#' @importFrom dplyr relocate
-#' @importFrom dplyr %>%
-#' @importFrom dplyr select
-#'
-#' @examples
-#' # This test takes >5 sec
-#' \donttest{
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "rt_data.csv",
-#'   package = "quicR"
-#' )
-#' df_ <- read.csv(file, check.names = FALSE)
-#' calculate_MS(df_)
-#' }
-#'
-#' @export
-calculate_MS <- function(data, window = 3, data_is_norm = TRUE) {
-  curate <- function(x) {
-    x %>%
-      {if (data_is_norm) . else normalize_RFU(.)} %>%
-      t() %>%
-      as.data.frame() %>%
-      mutate_all(~ as.numeric(as.character(.))) %>%
-      mutate(Time = as.numeric(rownames(.))) %>%
-      suppressWarnings() %>%
-      na.omit() %>%
-      relocate("Time", .before = 1)
-  }
-
-  slope <- function(x) {
-    x %>%
-      select(-"Time") %>%
-      map_dbl(~ {
-        slide_dbl(
-          .x = seq_along(.x),
-          .f = function(idx) {
-            if (length(idx) < 2) return(NA)
-            diff(range(.x[idx])) / diff(range(x[["Time"]][idx]))
-          },
-          .before = window,
-          .complete = TRUE
-        ) %>%
-          max(na.rm = TRUE)
-      })
-  }
-
-  return(slope(curate(data)))
-}

### 2025-09-05 R/calculate_TtT.R

@@ -1,48 +1,0 @@
-#' Calculate Time to Threshold
-#'
-#' Calculates the time required to reach a defined threshold.
-#'
-#' @param data A dataframe containing real-time RT-QuIC data.
-#' @param threshold A numeric value defining the threshold.
-#' @param time Column containing your time values.
-#' @param values Column containing your fluorescence values.
-#' @param .by Grouping factor. Should typically be by individual wells.
-#'
-#' @return A vector containing the times to threshold
-#'
-#' @importFrom dplyr group_by
-#' @importFrom dplyr rename
-#' @importFrom dplyr mutate_at
-#' @importFrom dplyr summarize
-#' @importFrom dplyr select
-#' @importFrom purrr is_empty
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test2.xlsx",
-#'   package = "quicR"
-#' )
-#' get_quic(file) |>
-#'   calculate_TtT(threshold = 2)
-#'
-#' @export
-calculate_TtT <- function(data, threshold, time="Time", values="Norm", .by="Wells") {
-
-  dt <- data$Time[2] - data$Time[1]
-
-  data %>%
-    group_by(!!sym(.by)) %>%
-    rename("y" = !!sym(values), "x" = !!sym(time)) %>%
-    mutate_at(c("x", "y"), as.numeric) %>%
-    summarize(
-      "x2" = ifelse(!is_empty(x[y > 2]), min(x[y > 2]), max(x)),
-      "x1" = x2 - dt,
-      "y2" = y[x == x2],
-      "y1" = y[x == x1],
-      "ttt" = ifelse(
-        x2 == max(x), x2, x1 + (threshold - y1) * (x2 - x1) / (y2 - y1)
-      )
-    ) %>%
-    select(!!sym(.by), "ttt")
-}

### 2025-09-05 R/calculate_metrics.R

@@ -1,47 +1,0 @@
-#' Generate a dataframe with calculated metrics.
-#'
-#' Uses functions from the "calculate" family of quicR functions to generate an analyzed dataframe.
-#'
-#' @param data A dataframe containing the raw RT-QuIC data.
-#' @param meta A dataframe containing sample metadata. Should include at least the "Sample IDs" column.
-#' @param metrics An array containing the metrics which should be calculated.
-#' @param transpose Logical; should the raw data be transposed before performing the calculations?
-#' @param normalize Logical; should the raw data be normalized before performing the calculations?
-#' @param start_col Integer; column number denoting where the numeric data begins.
-#' @param MS_window Integer; width of the window applied in the calculation of max slope.
-#' @param threshold Float; the threshold applied to the calculation of time-to-threshold.
-#'
-#' @importFrom dplyr mutate
-#'
-#' @return A dataframe of calculated metrics.
-#'
-#' @export
-calculate_metrics <- function(
-    data,
-    meta,
-    metrics = c("MPR", "MS", "TtT", "RAF"),
-    transpose = FALSE,
-    normalize = FALSE,
-    start_col = 3L,
-    MS_window = 3L,
-    threshold = 2
-) {
-
-  if (transpose) data <- transpose_real(data)
-  if (normalize) data <- normalize_RFU(data)
-  if ("RAF" %in% metrics & !("TtT" %in% metrics)) {
-    stop("RAF can only be calculated using TtT.\nPlease include TtT in the metrics argument. ")
-  }
-
-  data.frame(
-    `Sample IDs` = if ("Sample IDs" %in% colnames(meta)) meta$`Sample IDs`,
-    check.names = FALSE
-  ) |>
-    mutate(
-      Dilutions = if ("Dilutions" %in% colnames(meta)) meta$Dilutions,
-      MPR = if ("MPR" %in% metrics) calculate_MPR(data, start_col),
-      MS = if ("MS" %in% metrics) calculate_MS(data, MS_window),
-      TtT = if ("TtT" %in% metrics) calculate_TtT(data, threshold),
-      RAF = if ("RAF" %in% metrics) 1 / .data$TtT
-    )
-}

### 2025-09-05 R/calculate_threshold.R

@@ -1,44 +1,0 @@
-#' Calculate a Threshold for Rate Determination
-#'
-#' Calculates a threshold for determining time-to-threshold and rate of amyloid formation.
-#'
-#' @param data A dataframe output from get_real.
-#' @param background_cycle Integer; the cycle used for background fluorescence.
-#' @param method Method for determining threshold; default is "stdev".
-#' @param multiplier For some methods, will add a multiplier for more conservative thresholds.
-#'
-#' @importFrom dplyr select
-#' @importFrom stats sd
-#'
-#' @return A float value.
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test2.xlsx",
-#'   package = "quicR"
-#' )
-#' threshold <- get_real(file)[[1]] |>
-#'   calculate_threshold(multiplier = 10)
-#'
-#' @export
-calculate_threshold <- function(data, background_cycle = 2, method = list("stdev", "none"), multiplier = 1) {
-
-  if (is.list(method)) method <- method[[which(method == "stdev")]]
-  if (method == "none") return(NA)
-
-  curate <- function() {
-    data |>
-      select(-"Time") |>
-      lapply(as.numeric) |>
-      as.data.frame()
-  }
-
-  if (method == "stdev") {
-    get_row <- function() curate()[background_cycle, ]
-    avg <- function() apply(get_row(), 1, mean, na.rm = TRUE)[[1]]
-    std <- function() apply(get_row(), 1, sd, na.rm = TRUE)[[1]] * multiplier
-    return(avg() + std())
-  }
-
-}

### 2025-09-05 R/convert_tables.R

@@ -1,40 +1,0 @@
-#' Convert tables into a single column in a dataframe.
-#'
-#' Accepts a table or matrix or a list of tables and matrices
-#' and converts them into dataframe columns.
-#'
-#' @param tab A table/matrix or a list of tables/matrices.
-#' @param na_omit Logical; if true, will remove rows with NA.
-#'
-#' @return A dataframe column.
-#'
-#' @importFrom tidyr gather
-#' @importFrom dplyr select
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' tabs <- organize_tables(file)
-#' convert_tables(tabs)
-#'
-#' @export
-convert_tables <- function(tab, na_omit = TRUE) {
-  if (!is.vector(tab)) stop("Input should be of type vector.")
-
-  df_ <- lapply(
-    seq_along(tab),
-    function(i) {
-      message(paste0(i, ": ", names(tab)[i]))
-      data.frame(as.vector(t(tab[[i]])), stringsAsFactors = FALSE)
-    }
-  )
-  df_ <- do.call(cbind, df_)
-  colnames(df_) <- names(tab)
-
-  if (na_omit) df_ <- na.omit(df_)
-
-  return(df_)
-}

### 2025-09-05 R/get_meta.R

@@ -1,43 +1,0 @@
-#' Retrieve the BMG metadata
-#'
-#' Takes the Excel file exported from MARS and compiles the metadata in the
-#' header.
-#'
-#' @param file The Excel file exported from MARS.
-#'
-#' @return A dataframe containing the Meta_ID and Meta_info
-#'
-#' @importFrom readxl read_excel
-#' @importFrom stats na.omit
-#' @importFrom tidyr separate_wider_delim
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' get_meta(file)
-#'
-#' @export
-get_meta <- function(file) {
-  if (is.character(file)) { # Read the Excel file into R.
-    data <- read_excel(file, sheet = 1, col_names = FALSE) %>%
-      suppressMessages()
-  } else if (is.data.frame(file)) {
-    data <- file
-  } else {
-    stop("Please enter either .xlsx string or dataframe. ")
-  }
-
-  data[1:which(is.na(data[[1]]))[1], 1] |>
-    as.data.frame() |>
-    na.omit() |>
-    separate_wider_delim(
-      1,
-      ": ",
-      names = c("Meta_ID", "Meta_info"),
-      too_few = "align_start",
-      too_many = "merge"
-    )
-}

### 2025-09-05 R/get_quic.R

@@ -1,60 +1,0 @@
-#' Get all time-series and metadata.
-#'
-#' Accepts an Excel file or a data frame of real-time RT-QuIC data.
-#'
-#' @param file An Excel file exported by BMG.
-#' @param transpose_table Logical, if true, will transpose the table(s). This should almost always be true.
-#' @param normalize Logical, if true, will normalize the fluorescent data against the values at a certain cycle defined by 'norm_point'.
-#' @param norm_point Integer, defines the cycle to use as background fluorescence.
-#' @param which_table Integer, defines which table in the Excel sheet contains the real-time data. Should usually be set to 1.
-#' @param .by Grouping factor. Should typically be by individual wells.
-#'
-#' @return A data frame containing all time-series data and sample/plate metadata.
-#'
-#' @importFrom dplyr mutate
-#' @importFrom dplyr mutate_at
-#' @importFrom dplyr group_by
-#' @importFrom tidyr pivot_longer
-#' @importFrom magrittr %>%
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' get_quic(file)
-#'
-#' @export
-get_quic <- function(file, transpose_table=TRUE, normalize=TRUE,
-                     norm_point=2, which_table=1, .by="Wells") {
-
-  meta <- organize_tables(file) %>%
-    convert_tables()
-
-  # normalize_real <- function(x) {
-  #   group_by(x, !!sym(.by)) %>%
-  #     mutate(Norm = RFU/RFU[norm_point]) %>%
-  #     ungroup()
-  # }
-
-  get_real(file, transpose_table=transpose_table)[[which_table]] %>%
-    mutate(
-      "Sample IDs" = meta[["Sample IDs"]],
-      "Wells" = meta[["Wells"]],
-      "Dilutions" = ifelse("Dilutions" %in% colnames(meta), meta[["Dilutions"]], NA),
-      .after = `Sample IDs`
-    ) %>%
-    # relocate(Wells, Dilutions, .after=`Sample IDs`) %>%
-    pivot_longer(4:ncol(.), names_to="Time", values_to="RFU") %>%
-    mutate_at(c("Time", "RFU"), as.numeric) %>%
-    {
-      if (normalize) {
-        group_by(., !!sym(.by)) %>%
-          mutate(Norm = RFU/RFU[norm_point]) %>%
-          ungroup()
-      } else {
-        .
-      }
-    }
-}

### 2025-09-05 R/get_real.R

@@ -1,93 +1,0 @@
-#' Get Real-Time RT-QuIC Fluorescence Data
-#'
-#' Accepts an Excel file or a dataframe of real-time RT-QuIC data.
-#'
-#' @param data Either an Excel file or a dataframe.
-#' @param order_by_sample Logical, if true, will organize the columns by sample ID rather than by well.
-#' @param transpose_table Logical, if true, will transpose the table(s).
-#'
-#' @return A list of dataframes containing the formatted real-time data.
-#'
-#' @importFrom dplyr select
-#' @importFrom dplyr %>%
-#' @importFrom dplyr rename
-#' @importFrom readxl read_xlsx
-#' @importFrom janitor row_to_names
-#' @importFrom janitor clean_names
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' get_real(file)
-#'
-#' @export
-get_real <- function(data, order_by_sample = FALSE, transpose_table = TRUE) {
-  check_format <- function(x) {
-    if (is.character(x)) {
-      return(suppressMessages(read_xlsx(x, sheet = 2, col_names = FALSE)))
-    } else if (is.data.frame(x)) {
-      return(x)
-    } else {
-      stop("Please enter either .xlsx file path or data frame. ")
-    }
-  }
-
-  curate <- function(x) {
-    x %>%
-      na.omit() %>%
-      select(-1) %>%
-      row_to_names(1) %>%
-      clean_names() %>%
-      rename("Time" = 1) %>%
-      {
-        if (order_by_sample) {
-          select(., "Time", order(colnames(.[colnames(.) != "Time"])))
-        } else {
-          .
-        }
-      } %>%
-      suppressWarnings()
-  }
-
-  split_real_time <- function(x) {
-    # Number of types of data (e.g. Raw, Normalized, or Derivative)
-    reads <- length(which(x[["Time"]] == 0))
-    if (reads == 1) {
-      return(list(x))
-    }
-
-    # Designate the integers used to calculate how the data will be cut
-    num_rows <- cycles <- length(unique(x[["Time"]]))
-
-    # Create separate data frames for different read types
-    df_list <- list()
-    for (i in 1:reads) {
-      df_list <- append(df_list, list(x[(1 + num_rows - cycles):num_rows, ]))
-      num_rows <- num_rows + cycles
-    }
[…]

### 2025-09-05 R/get_wells.R

@@ -1,33 +1,0 @@
-#' Get the Wells Used in the RT-QuIC Run.
-#'
-#' Returns the well IDs used in the plate.
-#'
-#' @param file Excel file exported from MARS
-#' @param sheet The sheet containing the well IDs in the Excel file.
-#'
-#' @return A vector containing well IDs.
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' get_wells(file)
-#'
-#' @export
-get_wells <- function(file, sheet = 2) {
-  {
-    if (is.character(file)) {
-      read_excel(file, sheet = sheet, col_names = FALSE) %>%
-        suppressMessages()
-    } else if (is.data.frame(file)) {
-      file
-    } else {
-      stop("Please enter either .xlsx string or dataframe. ")
-    }
-  } %>%
-    filter(.$`...1` == "Well") %>%
-    select(-(1:2)) %>%
-    as.character()
-}

### 2025-09-05 R/organize_tables.R

@@ -1,70 +1,0 @@
-#' Organize MARS Tables
-#'
-#' Extracts the tables from the microplate view sheet in the MARS Excel file
-#' and adds each table to a list.
-#'
-#' @param file An Excel file exported from MARS.
-#' @param plate Integer either 96 or 384 to denote microplate type.
-#'
-#' @return A list containing tibbles.
-#'
-#' @importFrom readxl cell_cols
-#' @importFrom readxl read_xlsx
-#'
-#' @examples
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test.xlsx",
-#'   package = "quicR"
-#' )
-#' organize_tables(file)
-#'
-#' @export
-organize_tables <- function(file, plate = 96) {
-
-  if (plate != 96 & plate != 384) {
-    stop("Please enter either 96 or 384 for the plate argument. ")
-  }
-  if (!is.character(file) & !is.data.frame(file)) {
-    stop("Please enter either an excel file string or a dataframe. ")
-  }
-
-  # Block allows input of an excel file string or a dataframe.
-  if (is.character(file)) {
-    # Read the Excel file into R.
-    data <- read_xlsx(
-      file,
-      sheet = 1,
-      col_names = FALSE,
-      if (plate == 96) range = cell_cols(2:13) else range = cell_cols(2:25)
-    ) |>
-      suppressMessages()
-  } else {
-    data <- ifelse(plate == 96, file[2:13], file[2:25])
-  }
-
-  # Create a vector with named tibbles for each table.
-  step <- ifelse(plate == 96, 11, 19)
-  df_dic <- list()
-  i <- 1
-
-  while (i < nrow(data)) {
-    name <- paste0(sub("^\\d+\\. ", "", data[[i, 1]]))
-    df_dic[[name]] <- data[(i + 2): (i + step - 2), ]
-    i <- i + step
-  }
-
-  df_dic$Wells <- (
-    expand.grid(
-      {if (plate == 96) LETTERS[1:8] else LETTERS[1:16]},
-      {if (plate == 96) 1:12 else 1:24}
-    ) %>%
-      unite(Wells, 1,2, sep="")
-  )[[1]] %>%
-    matrix(
-      nrow=ifelse(plate == 96, 8, 16),
-      ncol=ifelse(plate == 96, 12, 24)
-    )
-
-  return(df_dic)
-}

### 2025-09-05 R/plate_view.R

@@ -1,128 +1,0 @@
-#' Real-Time Plate View
-#'
-#' Converts the real-time data into a ggplot figure. The layout is either 8x12
-#' or 16x24 for 96- and 384-well plates, respectively.
-#'
-#' @param df Real-time dataframe
-#' @param meta Dataframe containing well IDs and Sample IDs to title each facet.
-#' @param plate Integer either 96 or 384 to denote microplate type.
-#'
-#' @return A ggplot object
-#'
-#' @import ggplot2
-#' @import dplyr
-#' @importFrom tidyr replace_na
-#' @importFrom tidyr separate
-#' @importFrom stringr str_length
-#' @importFrom reshape2 melt
-#'
-#' @examples
-#' # This test takes >5 sec
-#' \donttest{
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test2.xlsx",
-#'   package = "quicR"
-#' )
-#'
-#' # Get the real-time data.
-#' df_ <- get_real(file, ordered = FALSE)[[1]] |>
-#'   as.data.frame()
-#'
-#' sample_locations <- get_sample_locations(
-#'   file,
-#'   dilution_bool = TRUE,
-#'   dilution_fun = function(x) -log10(x)
-#' )
-#'
-#' plate_view(df_, sample_locations)
-#' }
-#'
-#' @export
-plate_view <- function(df, meta, plate = 96) {
-
-  if (plate != 96 & plate != 384) {
-    return("Invalid plate layout. Format should be either 96 or 384. ")
-  }
-
-  # Ensures that the input is a dataframe.
-  df <- data.frame(df)
-
-  colnames(df) <- c("Time", paste(meta[[1]], meta[[2]], sep = "."))
-
-  # Create a template of all possible columns
-  template_columns <- expand.grid(
-    if (plate == 96) {
-      Var1 <- LETTERS[1:8]
-    } else {
-      Var1 <- LETTERS[1:16]
-    },
-    if (plate == 96) {
-      Var2 <- sprintf("%02d", 1:12)
-    } else {
-      Var2 <- sprintf("%02d", 1:24)
-    }
-  )
-  template_columns <- sort(paste0(template_columns$Var1, template_columns$Var2))
-  rm(Var1, Var2)
-
-  # Add columns with NAs if they do not exist.
-  for (col in template_columns) {
-    if (!(col %in% meta[[1]])) {
-      df[col] <- NA
-    }
-  }
-
-  # Add a "Time" column. This is important for the melt function.
[…]

### 2025-09-05 R/plot_metrics.R

@@ -1,81 +1,0 @@
-#' Plot metrics generated from the "calculate" family of quicR functions.
-#'
-#' Generates a faceted figure of boxplots.
-#'
-#' @param data A dataframe containing the calculated metrics from the "calculate" family of quicR functions.
-#' @param sample_col The name of the column containing the sample IDs.
-#' @param fill The column containing the fill aesthetic. Usually the dilutions column.
-#' @param dilution_bool Logical; should dilution factors be included in the plot?
-#' @param nrow Integer; number of rows to output in the plot.
-#' @param ncol Integer; number of columns to output in the plot.
-#'
-#' @importFrom dplyr %>%
-#' @importFrom tidyr gather
-#' @import ggplot2
-#'
-#' @return A ggplot object
-#'
-#' @examples
-#' # This test takes >5 sec
-#' \donttest{
-#' file <- system.file(
-#'   "extdata/input_files",
-#'   file = "test4.xlsx",
-#'   package = "quicR"
-#' )
-#'
-#' data <- quicR::get_real(file)[[1]] |>
-#'   quicR::normalize_RFU()
-#'
-#' meta <- quicR::organize_tables(file) |>
-#'   quicR::convert_tables()
-#'
-#' calculate_metrics(data, meta) |>
-#'   plot_metrics()
-#' }
-#'
-#' @export
-plot_metrics <- function(data, sample_col = "Sample IDs", fill = "Dilutions", dilution_bool = TRUE, nrow = 2, ncol = 2) {
-
-  variables <- function() {
-    if (dilution_bool) {
-      (data %>% gather("variable", "value", -c(sample_col, fill)))$variable %>%
-        unique() %>%
-        length()
-    } else {
-      (data %>% gather("variable", "value", -c(sample_col)))$variable %>%
-        unique() %>%
-        length()
-    }
-  }
-
-  data %>%
-    {
-      if (dilution_bool) {
-        gather(., "variable", "value", -c(sample_col, fill))
-      } else {
-        gather(., "variable", "value", -c(sample_col))
-      }
-    } %>%
-    ggplot(
-      aes(!!sym(sample_col),
-        .data$value,
-        fill = if (dilution_bool) as.factor(!!sym(fill))
-      )
-    ) +
-    geom_boxplot(
-      position = position_dodge2(preserve = "single")
-    ) +
-    {if (variables() > 1) {
[…]

### 2025-09-05 R/quicR.R

@@ -1,10 +1,0 @@
-#'  @description
-#'  Data handling for real-time quaking induced conversion assays
-#'
-#'  See the README on \href{https://github.com/gage1145/quicR}{Github}
-#'
-#'  @keywords internal
-"_PACKAGE"
-
-## quiets concerns of R CMD check re: the .'s that appear in pipelines
-if (getRversion() >= "2.15.1") utils::globalVariables(c("."))

### 2025-09-05 R/separate_raw.R

@@ -1,119 +1,0 @@
-#' Separate Real-Time Data into separate dataframes.
-#'
-#' If multiple real-time reads were exported from MARS, separate_raw will parse
-#' them out and separate them. It will also export to an Excel file with each
-#' real-time data having its own sheet.
-#'
-#' @param file An Excel file exported from MARS.
-#' @param num_rows Number of rows in the header to ignore.
-#' @param export_name The name of the original file or an orignal name.
-#'
-#' @return An Excel file with separated raw real-time data.
-#'
-#' @export
-# Separates the raw run files in the .xlsx file.
-separate_raw <- function(file, num_rows, export_name) {
-  if (is.character(file)) { # Read the Excel file into R.
-    data <- read_excel(file, sheet = 2)
-  } else if (is.data.frame(file)) {
-    data <- file
-  } else {
-    stop("Please enter either .xlsx string or dataframe. ")
-  }
-
-  # Remove metadata.
-  tidy_data <- data[-(1:num_rows - 1), -1] |>
-    na.omit(tidy_data)
-
-
-  # Set the first row as column names.
-  col_names <- tidy_data[1, ]
-  tidy_data <- tidy_data[-1, ]
-  colnames(tidy_data) <- col_names
-
-  # Add leading "0" before single digits in column names.
-  colnames(tidy_data) <- gsub(" X(\\d)$", " X0\\1", colnames(tidy_data))
-
-  # Identify and handle duplicate column names.
-  dup_cols <- colnames(tidy_data)[duplicated(colnames(tidy_data))]
-  if (length(dup_cols) > 0) {
-    # Add suffix to duplicate column names
-    for (col in dup_cols) {
-      indices <- which(colnames(tidy_data) == col)
-      colnames(tidy_data)[indices] <- paste0(col, "_", indices)
-    }
-  }
-
-  # Rename the first column as "Time"
-  tidy_data <- tidy_data |>
-    rename("Time" = 1)
-
-  # Convert tidy_data to numeric.
-  tidy_data <- as.data.frame(sapply(tidy_data, as.numeric))
-
-  # Rearrange columns to group replicates of the same sample
-  tidy_data <- tidy_data |>
-    select("Time", order(colnames(tidy_data), decreasing = FALSE))
-
-  # Remove suffixes from column names
-  colnames(tidy_data) <- gsub("_\\d+$", "", colnames(tidy_data))
-
[…]

### 2025-09-05 inst/extdata/testing.R

@@ -1,23 +1,0 @@
-library(quicR)
-library(dplyr)
-library(tidyr)
-
-source("~/quicR/R/get_quic.R")
-source("~/quicR/R/organize_tables.R")
-source("~/quicR/R/convert_tables.R")
-source("~/quicR/R/get_real.R")
-source("~/quicR/R/calculate_MPR.R")
-source("~/quicR/R/calculate_TtT.R")
-
-
-
-file <- "input_files/test4.xlsx"
-real <- get_real(file)
-
-raw <- get_quic(file)
-
-analyzed <- raw %>%
-  group_by(`Sample IDs`, Dilutions, Wells) %>%
-  reframe() %>%
-  left_join(calculate_MPR(raw)) %>%
-  left_join(calculate_TtT(raw, 2))

### 2025-09-05 man/manuscript/plots.R

@@ -1,205 +1,0 @@
-library(tidyverse)
-library(quicR)
-library(slider)
-library(ggpubr)
-library(ggrepel)
-
-
-
-# Smoothed Functions ------------------------------------------------------
-
-
-
-S <- 5.13534
-a <- 314730
-b <- -1.61059
-E <- -1.43142
-c <- 78.01494
-d <- -0.304958
-
-raw_func <- function(x) {
-  ratio1 <- S/(1 + a * exp(b * x))
-  ratio2 <- E/(1 + c * exp(d * x))
-  return(ratio1 + ratio2)
-}
-
-deriv_func <- function(x) {
-  ratio1 <- -S * a * b * exp(b * x) / (a * exp(b * x) + 1)^2
-  ratio2 <- -E * c * d * exp(d * x) / (c * exp(d * x) + 1)^2
-  ratio1 + ratio2
-}
-
-df_ <- data.frame(x = seq(0, 48, 0.1)) %>%
-  mutate(raw = raw_func(x), der = deriv_func(x))
-
-threshold <- 0.2
-ttt <- min(df_[which(df_$raw > threshold), "x"])
-mpr <- max(df_$raw)
-mpr_time <- df_[which(df_$raw == max(df_$raw)), "x"]
-ms <- max(df_$der)
-ms_time <- df_[which(df_$der == max(df_$der)), "x"]
-
-ggplot(df_, aes(x)) +
-  geom_line(aes(y = raw), color = "darkred", linewidth = 1.2) +
-  geom_line(aes(y = der), color = "darkblue", linewidth = 1.2) +
-  geom_segment(
-    x = 0,
-    xend = mpr_time,
-    y = mpr,
-    yend = mpr,
-    color = "darkred",
-    linewidth = 1.2,
-    linetype = "dashed"
-  ) +
-  geom_segment(
-    x = mpr_time,
-    xend = mpr_time,
-    y = -0.15,
-    yend = mpr,
-    color = "darkred",
-    linewidth = 1.2,
-    linetype = "dashed"
-  ) +
-  geom_segment(
-    x = 0,
-    xend = ms_time,
-    y = ms,
-    yend = ms,
-    color = "darkblue",
-    linewidth = 1.2,
-    linetype = "dashed"
-  ) +
-  geom_segment(
-    x = ms_time,
-    xend = ms_time,
-    y = -0.15,
-    yend = ms,
-    color = "darkblue",
-    linewidth = 1.2,
[…]

### 2025-09-05 tests/testthat.R

@@ -1,12 +1,0 @@
-# This file is part of the standard setup for testthat.
-# It is recommended that you do not modify it.
-#
-# Where should you do additional test configuration?
-# Learn more about the roles of various files in:
-# * https://r-pkgs.org/testing-design.html#sec-tests-files-overview
-# * https://testthat.r-lib.org/articles/special-files.html
-
-library(testthat)
-library(quicR)
-
-test_check("quicR")

### 2025-09-05 tests/testthat/test_BMG_format.R

@@ -1,25 +1,0 @@
-library(testthat)
-library(quicR)
-
-
-# use_r("BMG_format")
-
-test_file <- "BMG_formatting/plate_layout.csv"
-ref_file <- "BMG_formatting/formatted.txt"
-
-test_that(
-  "BMG_format returns character string.",
-  {
-    expect_type(BMG_format(test_file), "character")
-  }
-)
-
-test_that(
-  "BMG_format output matches formatted file.",
-  {
-    expect_equal(
-      data.frame(V1 = BMG_format(test_file)),
-      read.delim(ref_file, header = FALSE)
-    )
-  }
-)

### 2025-09-05 tests/testthat/test_get_real.R

@@ -1,31 +1,0 @@
-library(testthat)
-library(quicR)
-
-
-
-
-
-for (file in c("input_files/test.xlsx", "input_files/test2.xlsx", "input_files/test3.xlsx")) {
-  data <- readxl::read_xlsx(file, sheet = 2)
-
-  test_that(
-    "get_real accepts Excel file as input?",
-    {
-      expect_type(get_real(file), "list")
-    }
-  )
-
-  test_that(
-    "get_real accepts dataframe as input?",
-    {
-      expect_type(get_real(data), "list")
-    }
-  )
-
-  test_that(
-    "get_real returns list of dataframes?",
-    {
-      expect_true(is.data.frame(get_real(data)[[1]]))
-    }
-  )
-}

### 2025-09-05 tests/testthat/test_organize_tables.R

@@ -1,38 +1,0 @@
-library(testthat)
-library(quicR)
-
-
-# use_r("organize_tables")
-
-for (i in c("test", "test_no_meta")) {
-  file <- paste0("input_files/", i, ".xlsx")
-  df_list <- organize_tables(file)
-
-  test_that(
-    "organize_tables returns list?",
-    {
-      expect_type(df_list, "list")
-    }
-  )
-
-  test_that(
-    "organize_tables returns list of tibbles?",
-    {
-      expect_true(
-        class(df_list[[1]])[1] == "tbl_df" &
-          class(df_list[[1]])[2] == "tbl" &
-          class(df_list[[1]])[3] == "data.frame"
-      )
-    }
-  )
-}
-
-test_that(
-  "organize_tables accepts 384 as plate arg?",
-  {
-    expect_type(
-      organize_tables("input_files/test384.xlsx", plate = 384), "list"
-    )
-  }
-)
-

### 2025-09-05 man/manuscript/softwareX_submission_v2.tex
Updated the cache with gitignore.

@@
         \begin{keyword}
-            Chronic Wasting Disease \sep{} Creutzfeldt-Jakob Disease \sep{} Nano-QuIC \sep{} RT-QuIC \sep{} prion diagnostics \sep{} Parkinson's Disease \sep{} seed amplification assay
+            Chronic Wasting Disease \sep{} Creutzfeldt-Jakob Disease \sep{} Parkinson's Disease \sep{} RT-QuIC
         \end{keyword}
@@
 
-    \linenumbers
+    \linenumbers{}
 
@@
             C6 & Software code languages, tools, and services used & R\\
-            C7 & Compilation requirements, operating environments \& dependencies & R (>=4.1.0)\\
+            C7 & Compilation requirements, operating environments \& dependencies & R ($\geq{4.1.0}$)\\
             C8 & If available Link to developer documentation/manual & \url{https://cran.r-project.org/web/packages/quicR/quicR.pdf}\\
@@
         \subsection{Reproducibility}
-            To evaluate the reproducibility of \textbf{quicR} across systems and users, we developed a standardized script that processes MARS output files and writes three key result CSV files: metadata, normalized fluorescence data, and calculated metrics as well as a plain-text file containing R session information (See Table \ref{tbl:comparisons}).
-This script and accompanying raw data files were distributed, and users were instructed to source the script in the project directory.
-The output files were compared between each user for inconsistencies.
+            To evaluate the reproducibility of \textbf{quicR} across systems and users, we developed a standardized script that processes MARS output files and writes three key result CSV files: metadata, normalized fluorescence data, and calculated metrics as well as a plain-text file containing R session information (See Table~\ref{tbl:comparisons}).
+This script and accompanying raw data files were distributed to eight users who were instructed to source the script in the project directory.
+The output files were compared programatically between each user for discrepencies.
 Numerical data were given a floating point tolerance of 1E\textsuperscript{-12}.
@@
                     6 & 4.4.3 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 26100) \\
+                    7 & 4.4.3 & 2.1.0 & x86\_64-apple-darwin20 & macOS Sequoia 15.5 \\
+                    8 & 4.5.0 & 2.1.0 & x86\_64-w64-mingw32/x64 & Windows 11 x64 (build 22621) \\
                     \hline

### 2025-09-05 .example_scripts/BMG_format.R

@@ -1,0 +1,17 @@
+# This script takes an .csv file plate layout and formats it into a .txt file
+# that can be imported into the BMG control software.
+
+# See "formatted.txt" in the BMG formatting folder for the output example.
+# See "plate_layout.csv" in the BMG formatting folder for input file example.
+
+
+
+library(quicR)
+
+
+
+# Use plate_layout.csv in the Desktop.
+setwd("C:/Users/Priogen/Desktop")
+file <- "plate_layout.csv"
+
+BMG_format(file) |> writeLines("formatted.txt")

### 2025-09-05 .example_scripts/calculate_metrics.R

@@ -1,0 +1,252 @@
+library(ggpubr)
+library(openxlsx)
+library(agricolae)
+library(tidyverse)
+library(quicR)
+
+
+
+# Initialize the file and read in the data --------------------------------
+
+
+
+# For testing, use "test".
+# Request the user to input the file name for analysis.
+file <- ""
+while (file == "") {
+  file <- paste0(
+    readline(
+      "Please input the Excel file name without .xlsx extension: "
+    ),
+    ".xlsx"
+  )
+  if (!file.exists(file)) {
+    print(paste(file, "does not exist. Please enter a valid file name."))
+    file <- ""
+  }
+}
+
+# Ask the user for the threshold.
+threshold <- "Please enter the desired threshold for RAF calculation: " %>%
+  readline() %>%
+  as.integer()
+
+
+
+# Identify the raw real-time data -----------------------------------------
+
+
+
+# Get the real-time data from the BMG export file.
+df <- quicR::get_real(file, ordered = FALSE)
+
+# Ask the user which real-time data set they want to use.
+df_id <- ifelse(
+  length(df) > 1,
+  paste(
+    "There are",
+    length(df),
+    "real-time data sets. Please enter a number in that range: "
+  ) %>%
+    readline() %>%
+    as.integer(),
+  1
+)
+
+# Select the real-time data set that the user signified.
+df <- df[[df_id]]
+
+
+
+# Get the metadata of each sample -----------------------------------------
+
+
+
+# Export the tables in the first sheet of the file.
+dic <- file %>%
+  quicR::organize_tables() %>%
+  quicR::convert_tables()
+
+
+
+# Calculate the normalized real-time data ---------------------------------
+
+
+
+df_norm <- df %>%
+  transpose_real() %>%
+  normalize_RFU(transposed = TRUE)
+
+
+
+# Add dilution factors if applicable ---------------------------------------
+
+
+
+# Determine if there is a dilutions table.
+dilution_bool <- "Dilutions" %in% names(dic)
+
+
+
+# Calculate the relevant metrics ------------------------------------------
+
+
+
+# Define the number of hours that the rxn ran for.
[…]

### 2025-09-05 .example_scripts/plate_view_export.R

@@ -1,0 +1,85 @@
+# require(readxl)
+require(tidyverse)
+require(quicR)
+
+
+
+# Initialize parameters for downstream functions. -------------------------
+
+
+
+file <- ""
+while (file == "") {
+  file <- paste0(
+    readline("Please input .xlsx file name WITHOUT extension: "),
+    ".xlsx"
+  )
+  if (!(file.exists(file))) {
+    print("File does not exist. Please ensure file name was typed correctly")
+    file <- ""
+  }
+}
+
+plate <- 0
+while (plate == 0) {
+  plate <- as.integer(readline("Please enter 96 or 384 for plate type: "))
+  if (plate != 96 & plate != 384) {
+    plate <- 0
+  }
+}
+
+
+
+# Following block exports the plate view figure. --------------------------
+
+
+
+# Define the layout using the first sheet in the excel file.
+# The sheet should be formatted so that each ID in the "layout" table is unique.
+df_dic <- quicR::organize_tables(file, plate = plate)
+
+# Determine if there is a dilutions table.
+dilution_bool <- "Dilutions" %in% names(df_dic)
+
+# Read in the real-time data.
+# get_real will return a list of dataframes depending on how many real-time
+# measurements the user exported from MARS.
+df_ <- quicR::get_real(file, ordered = FALSE)
+
+df_id <- ifelse(
+  length(df_) > 1,
+  as.integer(
+    readline(
+      paste(
+        "There are",
+        length(df_),
+        "real-time data sets. Please enter a number in that range: "
+      )
+    )
+  ),
+  1
+)
+
+df_ <- df_[[df_id]] %>%
+  as.data.frame()
+
+sample_locations <- get_sample_locations(
+  file = file,
+  tab_name = "Sample IDs",
+  dilution_bool = dilution_bool,
+  dilution_fun = function(x) -log10(x),
+  sep = "\n",
+  plate = plate
+)
+
+
+
+# Run plate_view function which produces a plate view figure. -------------
+
+
+
+quicR::plate_view(df_, sample_locations, plate) +
+  ggtitle(str_split_i(file, "\\.", 1)) +
+  theme(plot.title = element_text(hjust = 0.5))
+
+ggsave("plate_view.png", width = 3600, height = 2400, units = "px")

### 2025-09-05 R/convert_tables.R

@@ -1,0 +1,40 @@
+#' Convert tables into a single column in a dataframe.
+#'
+#' Accepts a table or matrix or a list of tables and matrices
+#' and converts them into dataframe columns.
+#'
+#' @param tab A table/matrix or a list of tables/matrices.
+#' @param na_omit Logical; if true, will remove rows with NA.
+#'
+#' @return A dataframe column.
+#'
+#' @importFrom tidyr gather
+#' @importFrom dplyr select
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' tabs <- organize_tables(file)
+#' convert_tables(tabs)
+#'
+#' @export
+convert_tables <- function(tab, na_omit = TRUE) {
+  if (!is.vector(tab)) stop("Input should be of type vector.")
+
+  df_ <- lapply(
+    seq_along(tab),
+    function(i) {
+      message(paste0(i, ": ", names(tab)[i]))
+      data.frame(as.vector(t(tab[[i]])), stringsAsFactors = FALSE)
+    }
+  )
+  df_ <- do.call(cbind, df_)
+  colnames(df_) <- names(tab)
+
+  if (na_omit) df_ <- na.omit(df_)
+
+  return(df_)
+}

### 2025-09-05 R/get_meta.R

@@ -1,0 +1,43 @@
+#' Retrieve the BMG metadata
+#'
+#' Takes the Excel file exported from MARS and compiles the metadata in the
+#' header.
+#'
+#' @param file The Excel file exported from MARS.
+#'
+#' @return A dataframe containing the Meta_ID and Meta_info
+#'
+#' @importFrom readxl read_excel
+#' @importFrom stats na.omit
+#' @importFrom tidyr separate_wider_delim
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_meta(file)
+#'
+#' @export
+get_meta <- function(file) {
+  if (is.character(file)) { # Read the Excel file into R.
+    data <- read_excel(file, sheet = 1, col_names = FALSE) %>%
+      suppressMessages()
+  } else if (is.data.frame(file)) {
+    data <- file
+  } else {
+    stop("Please enter either .xlsx string or dataframe. ")
+  }
+
+  data[1:which(is.na(data[[1]]))[1], 1] |>
+    as.data.frame() |>
+    na.omit() |>
+    separate_wider_delim(
+      1,
+      ": ",
+      names = c("Meta_ID", "Meta_info"),
+      too_few = "align_start",
+      too_many = "merge"
+    )
+}

### 2025-09-05 R/get_wells.R

@@ -1,0 +1,33 @@
+#' Get the Wells Used in the RT-QuIC Run.
+#'
+#' Returns the well IDs used in the plate.
+#'
+#' @param file Excel file exported from MARS
+#' @param sheet The sheet containing the well IDs in the Excel file.
+#'
+#' @return A vector containing well IDs.
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_wells(file)
+#'
+#' @export
+get_wells <- function(file, sheet = 2) {
+  {
+    if (is.character(file)) {
+      read_excel(file, sheet = sheet, col_names = FALSE) %>%
+        suppressMessages()
+    } else if (is.data.frame(file)) {
+      file
+    } else {
+      stop("Please enter either .xlsx string or dataframe. ")
+    }
+  } %>%
+    filter(.$`...1` == "Well") %>%
+    select(-(1:2)) %>%
+    as.character()
+}

### 2025-09-05 inst/extdata/testing.R

@@ -1,0 +1,33 @@
+# library(quicR)
+library(dplyr)
+library(tidyr)
+library(janitor)
+library(readxl)
+library(purrr)
+library(zoo)
+library(ggplot2)
+
+source("../../R/get_quic.R")
+source("../../R/organize_tables.R")
+source("../../R/convert_tables.R")
+source("../../R/get_real.R")
+source("../../R/calculate_MPR.R")
+source("../../R/calculate_TtT.R")
+source("../../R/calculate_MS.R")
+source("../../R/calculate_metrics.R")
+source("../../R/plate_view.R")
+source("../../R/plot_metrics.R")
+
+
+
+file <- "input_files/test4.xlsx"
+raw <- get_quic(file)
+
+analyzed <- calculate_metrics(raw, `Sample IDs`, Dilutions, Wells)
+
+plot_metrics(analyzed, "MPR", "MS", "TtT", "RAF", dilution_bool = F)
+
+
+
+# plate_view(raw)
+#

### 2025-09-05 man/manuscript/plots.R

@@ -1,0 +1,205 @@
+library(tidyverse)
+library(quicR)
+library(slider)
+library(ggpubr)
+library(ggrepel)
+
+
+
+# Smoothed Functions ------------------------------------------------------
+
+
+
+S <- 5.13534
+a <- 314730
+b <- -1.61059
+E <- -1.43142
+c <- 78.01494
+d <- -0.304958
+
+raw_func <- function(x) {
+  ratio1 <- S/(1 + a * exp(b * x))
+  ratio2 <- E/(1 + c * exp(d * x))
+  return(ratio1 + ratio2)
+}
+
+deriv_func <- function(x) {
+  ratio1 <- -S * a * b * exp(b * x) / (a * exp(b * x) + 1)^2
+  ratio2 <- -E * c * d * exp(d * x) / (c * exp(d * x) + 1)^2
+  ratio1 + ratio2
+}
+
+df_ <- data.frame(x = seq(0, 48, 0.1)) %>%
+  mutate(raw = raw_func(x), der = deriv_func(x))
+
+threshold <- 0.2
+ttt <- min(df_[which(df_$raw > threshold), "x"])
+mpr <- max(df_$raw)
+mpr_time <- df_[which(df_$raw == max(df_$raw)), "x"]
+ms <- max(df_$der)
+ms_time <- df_[which(df_$der == max(df_$der)), "x"]
+
+ggplot(df_, aes(x)) +
+  geom_line(aes(y = raw), color = "darkred", linewidth = 1.2) +
+  geom_line(aes(y = der), color = "darkblue", linewidth = 1.2) +
+  geom_segment(
+    x = 0,
+    xend = mpr_time,
+    y = mpr,
+    yend = mpr,
+    color = "darkred",
+    linewidth = 1.2,
+    linetype = "dashed"
+  ) +
+  geom_segment(
+    x = mpr_time,
+    xend = mpr_time,
+    y = -0.15,
+    yend = mpr,
+    color = "darkred",
+    linewidth = 1.2,
+    linetype = "dashed"
+  ) +
+  geom_segment(
+    x = 0,
+    xend = ms_time,
+    y = ms,
+    yend = ms,
+    color = "darkblue",
+    linewidth = 1.2,
+    linetype = "dashed"
+  ) +
+  geom_segment(
+    x = ms_time,
+    xend = ms_time,
+    y = -0.15,
+    yend = ms,
+    color = "darkblue",
+    linewidth = 1.2,
[…]

### 2025-09-05 R/calculate_metrics.R
Updated calculate_metrics for the new pipeline.

@@ -1,0 +1,35 @@
+#' Generate a dataframe with calculated metrics.
+#'
+#' Uses functions from the "calculate" family of quicR functions to generate an analyzed dataframe.
+#'
+#' @param data A dataframe containing the raw RT-QuIC data.
+#' @param ... A list of grouping factors.
+#' @param threshold Float; the threshold applied to the calculation of time-to-threshold.
+#'
+#' @importFrom dplyr mutate
+#' @importFrom dplyr group_by
+#' @importFrom dplyr left_join
+#' @importFrom dplyr reframe
+#'
+#' @return A dataframe of calculated metrics.
+#'
+#' #' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_quic(file) |>
+#'  calculate_metrics(`Sample IDs`, Dilutions, Wells)
+#'
+#' @export
+calculate_metrics <- function(data, ..., threshold = 2) {
+  data %>%
+    group_by(...) %>%
+    reframe() %>%
+    left_join(calculate_MPR(raw)) %>%
+    left_join(calculate_TtT(raw, threshold)) %>%
+    left_join(calculate_MS(raw)) %>%
+    mutate(RAF = 1/.data$TtT) %>%
+    suppressMessages()
+}

### 2025-09-05 R/calculate_MPR.R
Updated calculate_MPR for the new pipeline.

@@ -1,0 +1,25 @@
+#' Calculate the Maxpoint Ratio
+#'
+#' Maxpoint ratio is defined as the maximum relative fluorescence divided by the
+#' background fluorescence.
+#'
+#' @param data A data frame output from 'get_quic()'.
+#' @param col The column containing the normalized fluorescence data.
+#' @param .by Grouping factor. Should typically be by individual wells.
+#' @return A data frame containing well-matched MPR values.
+#'
+#' @importFrom dplyr summarize
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_quic(file) |>
+#'   calculate_MPR()
+#'
+#' @export
+calculate_MPR <- function(data, col="Norm", .by="Wells") {
+  summarize(data, MPR = max(!!sym(col)), .by=.by)
+}

### 2025-09-05 R/calculate_MS.R
Updated calculate_MS for the new pipeline.

@@ -1,0 +1,24 @@
+#' Calculate Maximum Slope
+#'
+#' Uses a sliding window to calculate the slope of real-time reads.
+#'
+#' @param data A dataframe containing real-time reads. It is recommended to use a dataframe made from normalize_RFU.
+#' @param col Character, defines the column containing the derivative curve.
+#' @param .by Grouping factor. Should typically be by individual wells.
+#'
+#' @return A dataframe containing the real-time slope values as change in RFU/sec.
+#'
+#' @importFrom slider slide_dbl
+#' @importFrom purrr map_dbl
+#' @importFrom dplyr mutate_all
+#' @importFrom dplyr mutate
+#' @importFrom dplyr relocate
+#' @importFrom dplyr %>%
+#' @importFrom dplyr select
+#'
+#' @export
+calculate_MS <- function(data, col="Deriv", .by="Wells") {
+  data %>%
+    group_by(!!sym(.by)) %>%
+    summarize(MS = max(!!sym(col), na.rm=TRUE))
+}

### 2025-09-05 R/calculate_threshold.R
Updated calculate_threshold for the new pipeline.

@@ -1,0 +1,46 @@
+#' Calculate a Threshold for Rate Determination
+#'
+#' Calculates a threshold for determining time-to-threshold and rate of amyloid formation.
+#'
+#' @param data A dataframe output from get_real.
+#' @param values Column containing fluorescent values.
+#' @param time Column containing time values.
+#' @param background_time Float; the time point used for background fluorescence.
+#' @param method Method for determining threshold; default is "stdev".
+#' @param multiplier For some methods, will add a multiplier for more conservative thresholds.
+#'
+#' @importFrom dplyr select
+#' @importFrom stats sd
+#'
+#' @return A float value.
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test2.xlsx",
+#'   package = "quicR"
+#' )
+#' threshold <- get_quic(file) |>
+#'   calculate_threshold(multiplier=10)
+#'
+#' @export
+calculate_threshold <- function(data, values="RFU", time="Time",
+                                background_time=0, method=list("stdev", "none"),
+                                multiplier=1) {
+
+  if (is.list(method)) method <- "stdev"
+  if (method == "none") return(NA)
+
+  if (method == "stdev") {
+    (
+      data %>%
+       filter(!!sym(time) == background_time) %>%
+       summarize(
+         avg = mean(!!sym(values)),
+         std = sd(!!sym(values)),
+         thr = .data$avg + .data$std * multiplier
+       )
+    )$thr
+  }
+
+}

### 2025-09-05 R/calculate_TtT.R
Updated calculate_TtT for the new pipeline.

@@ -1,0 +1,48 @@
+#' Calculate Time to Threshold
+#'
+#' Calculates the time required to reach a defined threshold.
+#'
+#' @param data A dataframe containing real-time RT-QuIC data.
+#' @param threshold A numeric value defining the threshold.
+#' @param time Column containing your time values.
+#' @param values Column containing your fluorescence values.
+#' @param .by Grouping factor. Should typically be by individual wells.
+#'
+#' @return A vector containing the times to threshold
+#'
+#' @importFrom dplyr group_by
+#' @importFrom dplyr rename
+#' @importFrom dplyr mutate_at
+#' @importFrom dplyr summarize
+#' @importFrom dplyr select
+#' @importFrom purrr is_empty
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test2.xlsx",
+#'   package = "quicR"
+#' )
+#' get_quic(file) |>
+#'   calculate_TtT(threshold = 2)
+#'
+#' @export
+calculate_TtT <- function(data, threshold, time="Time", values="Norm", .by="Wells") {
+
+  dt <- data$Time[2] - data$Time[1]
+
+  data %>%
+    group_by(!!sym(.by)) %>%
+    rename("y" = !!sym(values), "x" = !!sym(time)) %>%
+    mutate_at(c("x", "y"), as.numeric) %>%
+    summarize(
+      "x2" = ifelse(!is_empty(.data$x[.data$y > 2]), min(.data$x[.data$y > 2]), max(.data$x)),
+      "x1" = .data$x2 - dt,
+      "y2" = .data$y[.data$x == .data$x2],
+      "y1" = .data$y[.data$x == .data$x1],
+      "TtT" = ifelse(
+        .data$x2 == max(.data$x), .data$x2, .data$x1 + (threshold - .data$y1) * (.data$x2 - .data$x1) / (.data$y2 - .data$y1)
+      )
+    ) %>%
+    select(!!sym(.by), "TtT")
+}

### 2025-09-05 R/get_quic.R
Updated get_quic

@@ -1,0 +1,54 @@
+#' Get all time-series and metadata.
+#'
+#' Accepts an Excel file or a data frame of real-time RT-QuIC data.
+#'
+#' @param file An Excel file exported by BMG.
+#' @param transpose_table Logical, if true, will transpose the table(s). This should almost always be true.
+#' @param norm_point Integer, defines the cycle to use as background fluorescence.
+#' @param which_table Integer, defines which table in the Excel sheet contains the real-time data. Should usually be set to 1.
+#' @param window_size Integer, defines the window size for estimating the derivative.
+#' @param .by Grouping factor. Should typically be by individual wells.
+#'
+#' @return A data frame containing all time-series data and sample/plate metadata.
+#'
+#' @importFrom dplyr mutate
+#' @importFrom dplyr mutate_at
+#' @importFrom dplyr group_by
+#' @importFrom dplyr lag
+#' @importFrom dplyr lead
+#' @importFrom tidyr pivot_longer
+#' @importFrom magrittr %>%
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_quic(file)
+#'
+#' @export
+get_quic <- function(file, transpose_table=TRUE, norm_point=2, which_table=1,
+                     window_size=2, .by="Wells") {
+
+  sheets <- lapply(1:2, function(x) suppressMessages(read_xlsx(file, sheet=x)))
+
+  meta <- organize_tables(sheets[[1]]) %>%
+    convert_tables()
+
+  get_real(sheets[[2]], transpose_table=transpose_table)[[which_table]] %>%
+    mutate(
+      "Sample IDs" = meta[["Sample IDs"]],
+      "Wells" = meta[["Wells"]],
+      "Dilutions" = ifelse("Dilutions" %in% colnames(meta), meta[["Dilutions"]], NA),
+      .after = "Sample IDs"
+    ) %>%
+    pivot_longer(4:ncol(.), names_to="Time", values_to="RFU") %>%
+    mutate_at(c("Time", "RFU"), as.numeric) %>%
+    group_by(., !!sym(.by)) %>%
+      mutate(
+        Norm = .data$RFU/.data$RFU[norm_point],
+        Deriv = (lead(.data$Norm, window_size) - lag(.data$Norm, window_size)) / (lead(.data$Time, window_size) - lag(.data$Time, window_size))
+      ) %>%
+      ungroup()
+}

### 2025-09-05 R/get_real.R
Updated the rest of the files.

@@ -1,0 +1,93 @@
+#' Get Real-Time RT-QuIC Fluorescence Data
+#'
+#' Accepts an Excel file or a dataframe of real-time RT-QuIC data.
+#'
+#' @param data Either an Excel file or a dataframe.
+#' @param order_by_sample Logical, if true, will organize the columns by sample ID rather than by well.
+#' @param transpose_table Logical, if true, will transpose the table(s).
+#'
+#' @return A list of dataframes containing the formatted real-time data.
+#'
+#' @importFrom dplyr select
+#' @importFrom dplyr %>%
+#' @importFrom dplyr rename
+#' @importFrom readxl read_xlsx
+#' @importFrom janitor row_to_names
+#' @importFrom janitor clean_names
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' get_real(file)
+#'
+#' @export
+get_real <- function(data, order_by_sample = FALSE, transpose_table = TRUE) {
+  check_format <- function(x) {
+    if (is.character(x)) {
+      return(suppressMessages(read_xlsx(x, sheet = 2, col_names = FALSE)))
+    } else if (is.data.frame(x)) {
+      return(x)
+    } else {
+      stop("Please enter either .xlsx file path or data frame. ")
+    }
+  }
+
+  curate <- function(x) {
+    x %>%
+      na.omit() %>%
+      select(-1) %>%
+      row_to_names(1) %>%
+      clean_names() %>%
+      rename("Time" = 1) %>%
+      {
+        if (order_by_sample) {
+          select(., "Time", order(colnames(.[colnames(.) != "Time"])))
+        } else {
+          .
+        }
+      } %>%
+      suppressWarnings()
+  }
+
+  split_real_time <- function(x) {
+    # Number of types of data (e.g. Raw, Normalized, or Derivative)
+    reads <- length(which(x[["Time"]] == 0))
+    if (reads == 1) {
+      return(list(x))
+    }
+
+    # Designate the integers used to calculate how the data will be cut
+    num_rows <- cycles <- length(unique(x[["Time"]]))
+
+    # Create separate data frames for different read types
+    df_list <- list()
+    for (i in 1:reads) {
+      df_list <- append(df_list, list(x[(1 + num_rows - cycles):num_rows, ]))
+      num_rows <- num_rows + cycles
+    }
[…]

### 2025-09-05 R/normalize_RFU.R

@@ -1,0 +1,32 @@
+#' Normalize Fluorescence
+#'
+#' Normalizes the real-time RT-QuIC data against the background fluorescence of
+#' a defined cycle. All cycles are divided by the fluorescent value of the
+#' defined cycle.
+#'
+#' @param data A dataframe generated from get_real.
+#' @param bg_cycle The cycle used for background fluorescence
+#' @param transposed Logical, TRUE if cycle values are shown as column names.
+#'
+#' @return A dataframe containing real-time normalized fluorescence values.
+#'
+#' @export
+normalize_RFU <- function(data, bg_cycle = 4, transposed = FALSE) {
+
+  curate <- function(x) {
+    colnames(x) %>%
+      rbind(x) %>%
+      unname() %>%
+      t() %>%
+      as.data.frame() %>%
+      row_to_names(1) %>%
+      rename("Sample IDs" = "Time") %>%
+      mutate_at(-c(1), function(y) as.numeric(as.character(y)))
+  }
+
+  normalize <- function(x) {
+    cbind(x[1], sweep(x[-1], 1, x[[bg_cycle + 1]], FUN = "/"))
+  }
+
+  if (transposed) normalize(data) else normalize(curate(data))
+}

### 2025-09-05 R/organize_tables.R

@@ -1,0 +1,81 @@
+#' Organize MARS Tables
+#'
+#' Extracts the tables from the microplate view sheet in the MARS Excel file
+#' and adds each table to a list.
+#'
+#' @param file An Excel file exported from MARS.
+#' @param plate Integer either 96 or 384 to denote microplate type.
+#'
+#' @return A list containing tibbles.
+#'
+#' @importFrom readxl cell_cols
+#' @importFrom readxl read_xlsx
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test.xlsx",
+#'   package = "quicR"
+#' )
+#' organize_tables(file)
+#'
+#' @export
+organize_tables <- function(file, plate = 96) {
+
+  if (plate != 96 & plate != 384) {
+    stop("Please enter either 96 or 384 for the plate argument. ")
+  }
+  if (!is.character(file) & !is.data.frame(file)) {
+    stop("Please enter either an excel file string or a dataframe. ")
+  }
+
+  # Block allows input of an excel file string or a dataframe.
+  if (is.character(file)) {
+    # Read the Excel file into R.
+    data <- read_xlsx(
+      file,
+      sheet = 1,
+      col_names = FALSE,
+      if (plate == 96) range = cell_cols(2:13) else range = cell_cols(2:25)
+    ) |>
+      suppressMessages()
+  } else {
+    if (plate == 96) data <- file[2:13] else data <- file[2:25]
+    # data <- ifelse(plate == 96, file[2:13], file[2:25])
+  }
+
+  # Remove leading NA rows.
+  for (i in 1:nrow(data)) {
+    if (!is.na(data[i,1])) {
+      if (i != 1){
+        data <- data[-(1:i-1),]
+        break
+      } else {break}
+    }
+  }
+
+  # Create a vector with named tibbles for each table.
+  step <- ifelse(plate == 96, 11, 19)
+  df_dic <- list()
+  i <- 1
+
+  while (i < nrow(data)) {
+    name <- paste0(sub("^\\d+\\. ", "", data[[i, 1]]))
+    df_dic[[name]] <- data[(i + 2): (i + step - 2), ]
+    i <- i + step
+  }
+
+  df_dic$Wells <- (
+    expand.grid(
+      {if (plate == 96) LETTERS[1:8] else LETTERS[1:16]},
[…]

### 2025-09-05 R/plate_view.R

@@ -1,0 +1,69 @@
+#' Real-Time Plate View
+#'
+#' Converts the real-time data into a ggplot figure. The layout is either 8x12
+#' or 16x24 for 96- and 384-well plates, respectively.
+#'
+#' @param data Real-time dataframe
+#' @param plate Integer either 96 or 384 to denote microplate type.
+#'
+#' @return A ggplot object
+#'
+#' @import ggplot2
+#' @import dplyr
+#' @importFrom tidyr replace_na
+#' @importFrom tidyr separate
+#' @importFrom stringr str_length
+#' @importFrom reshape2 melt
+#'
+#' @examples
+#' file <- system.file(
+#'   "extdata/input_files",
+#'   file = "test2.xlsx",
+#'   package = "quicR"
+#' )
+#'
+#' # Get the real-time data.
+#' df_ <- get_quic(file)
+#'
+#' plate_view(df_)
+#'
+#' @export
+plate_view <- function(data, plate = 96) {
+
+  if (plate != 96 & plate != 384) {
+    return("Invalid plate layout. Format should be either 96 or 384. ")
+  }
+
+  unique_cols <- data %>%
+    select(1:2) %>%
+    unique()
+
+  # Create the labeller function for the facet plot.
+  id_labeller <- function(variable, value) {
+    i <- unique_cols["Sample IDs"][unique_cols["Wells"] == value]
+    ifelse(is.na(i), " ", i)
+  }
+
+  data %>%
+    ggplot(aes(.data$Time)) +
+    geom_line(aes(y=.data$Norm), color="black") +
+    geom_line(aes(y=.data$Deriv), color="blue") +
+    facet_wrap(
+      vars(.data$Wells),
+      nrow = ifelse(plate == 96, 8, 16),
+      ncol = ifelse(plate == 96, 12, 24),
+      labeller = id_labeller
+    ) +
+    labs(
+      y = "RFU",
+      x = "Time (h)"
+    ) +
+    theme_classic() +
+    theme(
+      panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5),
+      strip.background = element_blank(),
+      axis.text.x = element_blank(),
+      axis.text.y = element_blank()
+    ) %>%
+    suppressWarnings()
+}

### 2025-09-05 R/plot_metrics.R

@@ -1,0 +1,42 @@
+#' Plot metrics generated from the "calculate" family of quicR functions.
+#'
+#' Generates a faceted figure of boxplots.
+#'
+#' @param data A dataframe containing the calculated metrics from the "calculate" family of quicR functions.
+#' @param ... A list of faceting columns.
+#' @param sample_col The name of the column containing the sample IDs.
+#' @param fill The column containing the fill aesthetic. Usually the dilutions column.
+#' @param dilution_bool Logical; should dilution factors be included in the plot?
+#' @param nrow Integer; number of rows to output in the plot.
+#' @param ncol Integer; number of columns to output in the plot.
+#'
+#' @importFrom magrittr %>%
+#' @importFrom tidyr pivot_longer
+#' @import ggplot2
+#'
+#' @return A ggplot object
+#'
+#' @export
+plot_metrics <- function(data, ..., sample_col = "Sample IDs", fill = "Dilutions", dilution_bool = TRUE, nrow = 2, ncol = 2) {
+
+  data %>%
+    pivot_longer(c(...)) %>%
+    ggplot(
+      aes(!!sym(sample_col), .data$value,
+        fill = if (dilution_bool) as.factor(!!sym(fill))
+      )
+    ) +
+    geom_boxplot(position = position_dodge2(preserve = "single")) +
+    {if (length(c(...)) > 1) {
+      facet_wrap(~.data$name, scales = "free_y", nrow = nrow, ncol = ncol)
+    }} +
+    {if (dilution_bool) {
+      labs(fill = fill)
+    }} +
+    theme(
+      legend.position = "bottom",
+      strip.text = element_text(face = "bold"),
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
+      axis.title = if(length(c(...)) > 1) element_blank() else element_text()
+    )
+}

### 2025-09-05 R/transpose_real.R

@@ -1,0 +1,28 @@
+#' Transpose Real-Time Data
+#'
+#' Transposes the real-time data table exported by the BMG software. Accepts
+#' output from the function, "get_real".
+#'
+#' @param data A dataframe generated from get_real.
+#'
+#' @return A transposed dataframe containing real-time normalized fluorescence values.
+#'
+#' @importFrom dplyr rename
+#' @importFrom dplyr mutate_at
+#' @importFrom dplyr %>%
+#' @importFrom janitor row_to_names
+#'
+#' @export
+
+# Still in the works
+transpose_real <- function(data) {
+  .Deprecated("get_real", "quicR", "This function has been integrated into the `get_real` function as a logical argument.")
+  colnames(data) %>%
+    rbind(data) %>%
+    unname() %>%
+    t() %>%
+    as.data.frame() %>%
+    row_to_names(1) %>%
+    rename("Sample IDs" = "Time") %>%
+    mutate_at(-c(1), function(y) as.numeric(as.character(y)))
+}
